### 2021-07-06 paper1.tex
Add mathUI template

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{onecolceurws}

\title{The One Column Style for CEUR-WS}

\author{
Mary Y. Writter \\ Publishing Dept.\\
                Paper City, PUB 11011 \\ mqw@pubdept.eu
\and
John X. Ceur \\ Science Dept.\\
                Online City, CEUR 99099 \\ jqq@ceur-ws.org
\and
Yvonne Onderzoeker \\ Research Dept.\\
                Science City, Sci 88088 \\ yvo@science.rdept.net
}

\institution{}

\begin{document}
\maketitle

\begin{abstract}
The Abstract paragraph should be indented $1.25$ inch on both
the left and right-hand margins. Abstract must be centered, bold, and
in point size 12. Two line spaces precede the Abstract. The Abstract
must be limited to one paragraphos.
\end{abstract}
\vskip 32pt

\section{General Formatting Instructions}

The format is in one column. The left margin is .9 inches (5.5 picas). Use 10 point type,
with a vertical spacing of 11 points. Times Roman is the preferred
typeface throughout.

Paper title is 16 point, Caps/lowercase, bold, centered. Subsequent
pages should start at 1 inch (6 picas) from the top of the page.

Authors names are centered, initial caps; co-authors names, if used, are
flush left and flush right.

Paragraphs are indented by 1 pica with no space between paragraphs.

\section{First Level Heading}

First level headings are all flush left, initial caps, bold and in point
size 12. One line space before the first level heading and $1/2$ line
space after the first level heading.

\subsection{Second Level Heading}

Second level headings must be flush left, initial caps, bold and in point
size 10. One line space before the second level heading and $1/2$ line
space after the second level heading.

\subsubsection{Third Level Heading}

Third level headings must be flush left, initial caps and bold.
One line space before the third level heading and $1/2$ line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps and roman type.
One line space before the fourth level heading and $1/2$ line
space after the fourth level heading.

\subsection{Citations In Text}

Citations within the text should indicate the author's last name and
year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
should follow the style that you are used to using, as long as the
citation style is consistent.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{This is a sample footnote} in
the text. Place the footnotes at the bottom of the page they appear on.
Precede the footnote with a vertical rule of 2 inches (12 picas).

\subsubsection{Figures}

All artwork must be centered, neat, clean and legible. Do not use pencil
or hand-drawn artwork. Figure number and caption always appear after the
the figure. Place one line space before the figure, one line space
before the figure caption and one line space after the figure caption.
The figure caption is initial caps and each figure is numbered
consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page to avoid
splitting the figure and figure caption.

Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
The source of the figure is in file {\tt fig1.eps}.

\begin{figure}[ht]
\begin{center}
\includegraphics[height=4cm]{fig1}
\caption{Sample EPS figure }
\label{fig1}
\end{center}
\end{figure}

Below is another figure using LaTeX commands.

\begin{figure}[ht]
\begin{center}
\setlength{\unitlength}{1pt}
\footnotesize
\begin{picture}(160,80)
        \put(0,0){\framebox(160,80)[]{}}
        \put(10,35){\framebox(80,40){}}
        \put(100,20){\framebox(40,20){}}
        \put(70,10){\framebox(20,10){}}
        \put(20,5){\framebox(10,5){}}
\end{picture}
\caption{Sample Figure Caption}
\end{center}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean and legible. Do not use pencil
or hand-drawn tables. Table number and title always appear before the
table.

One line space before the table title, one line space after the table
title and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[ht]
\begin{center}
\caption{Sample Table}

\bigskip

\begin{tabular}{|l|l|r|}
\hline
A & B & 1\\ \hline
C & D & 2\\
E & F & 3\\ \hline
\end{tabular}
\end{center}
\end{table}

\subsubsection{Handling References}

Use a first level heading for the references. References follow the
acknowledgements.

\subsubsection{Acknowledgements}

Use a third level heading for the acknowledgements. All acknowledgements
go at the end of the paper.

%\bibliographystyle{alpha} 
%\bibliography{samplebib}
%inline the .bbl file directly for mailing to authors.

\begin{thebibliography}{Com79}

\bibitem[Com79]{Comer-btree}
D.~Comer.
\newblock The ubiquitous b-tree.
\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.

\bibitem[Knu73]{Knuth-vol3}
D.~E. Knuth.
\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
  Searching}.
\newblock Addison-Wesley, 1973.

\end{thebibliography}

\end{document}

### 2021-07-06 paper1.tex
Structure of the paper

@@
 
-\title{The One Column Style for CEUR-WS}
+\title{Sophize Markdown and Communication Interface }
 
 \author{
-Mary Y. Writter \\ Publishing Dept.\\
-                Paper City, PUB 11011 \\ mqw@pubdept.eu
-\and
-John X. Ceur \\ Science Dept.\\
-                Online City, CEUR 99099 \\ jqq@ceur-ws.org
-\and
-Yvonne Onderzoeker \\ Research Dept.\\
-                Science City, Sci 88088 \\ yvo@science.rdept.net
+Abhishek Chugh \\ Sophize Foundation\\
+                Bengaluru, India \\ abc@sophize.org
 }
@@
 \begin{abstract}
-The Abstract paragraph should be indented $1.25$ inch on both
-the left and right-hand margins. Abstract must be centered, bold, and
-in point size 12. Two line spaces precede the Abstract. The Abstract
-must be limited to one paragraphos.
+Providing mathematicians to see connections of Mathematical objects (definitions, propositions, proofs) within and across multiple document has the potential to vastly accelerate mathematical research.
+We extend the markdown language and to demonstrate a new interactive way of representing such deeply connected mathematical knowledge on the web.
+We also utilize this new language to create a novel communication system that is specially built to allow a large number of collaborators to collaboratively solve mathematical problems.
 \end{abstract}
@@
 
-\section{General Formatting Instructions}
+\section{Introduction}
 
-The format is in one column. The left margin is .9 inches (5.5 picas). Use 10 point type,
-with a vertical spacing of 11 points. Times Roman is the preferred
-typeface throughout.
+Sophize is a novel Mathematics library and discussion platform.
+Mathematical proofs are developed from multiple POV (foundations, verification standards) and a single proof spans across a large number of documents - theorems to axioms.
+Our primary mission is to make it easy for mathematicians to allow mathematicians to find, discuss and discover such proofs.
+To achieve this mission, we are working on three goals:
 
-Paper title is 16 point, Caps/lowercase, bold, centered. Subsequent
-pages should start at 1 inch (6 picas) from the top of the page.
+formalize the largely unexplored network of information embedded in the connections of mathematical objects as envisioned by the GDML committee.
+Using the network of information to combine proofs based on each user’s chosen foundations and verification standards.
+Create a platform that is tailored for communication of mathematical ideas which utilizes and augments the network of information.
 
-Authors names are centered, initial caps; co-authors names, if used, are
-flush left and flush right.
+To achieve the above goals, we believe it is necessary to create a new format that is as extremely convenient for a casual web conversation of mathematical ideas and is powerful enough to embed mathematical entities (definitions, theorems, proofs etc.) from a wide variety of sources.
+The markdown language has the simplicity, extensibility and wide acceptance on the web that we are looking for.
+Sophize markdown extends the markdown format to meet our requirements.
 
-Paragraphs are indented by 1 pica with no space between paragraphs.
+The communication interface on the Sophize is designed to help mathematicians easily make sense of the discussion even when a post receives a large number of comments from many collaborators.
+We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to come with the design of our interface.
+Conveniently, the leaders have publically analysed these projects and suggested technical improvements suitable for such collaborations.
+In fact, a large portion of the interface is derived directly from the list of features desired and posted on their respective blogs by Prof Timothy Gowers and Prof Terence Tao.
+We believe that these features will not only aid large scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
 
-\section{First Level Heading}
+\section{Preliminaries}
 
-First level headings are all flush left, initial caps, bold and in point
-size 12. One line space before the first level heading and $1/2$ line
-space after the first level heading.
+Describe def, prop, arg, resourcepointer.
 
-\subsection{Second Level Heading}
+\subsection{Sophize Markdown}
 
-Second level headings must be flush left, initial caps, bold and in point
-size 10. One line space before the second level heading and $1/2$ line
-space after the second level heading.
+What is markdown, out of box features
 
-\subsubsection{Third Level Heading}
+\subsubsection{Latex extension}
 
@@
 
-\paragraph{Fourth Level Heading}
+\subsubsection{Link extension}
 
@@
 
-\subsection{Citations In Text}
+\paragraph{Link Types}
+Overlay, NO LINK,
 
-Citations within the text should indicate the author's last name and
-year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
-should follow the style that you are used to using, as long as the
-citation style is consistent.
+\paragraph{Status indicators}
 
-\subsubsection{Footnotes}
+\paragraph{Resource Expansion}
+
+\subsubsection{Formal Language Support}
 
@@
 
-\subsubsection{Figures}
+\subsubsection{Renderer}
+\paragraph{ Indicators }
+\paragraph{ Resource Overlay }
+\paragraph{ Proof views }
 
-All artwork must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn artwork. Figure number and caption always appear after the
-the figure. Place one line space before the figure, one line space
-before the figure caption and one line space after the figure caption.
-The figure caption is initial caps and each figure is numbered
-consecutively.
+\section{Sophize Collaboration Interface}
+Guiding principles/motivations?
+\subsection{Hierarchical Page Organization}
 
-Make sure that the figure caption does not get separated from the
-figure. Leave extra white space at the bottom of the page to avoid
-splitting the figure and figure caption.
+\subsection{Using existing math content}
 
-Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
-The source of the figure is in file {\tt fig1.eps}.
+\subsection{Referencing Comments}
 
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[height=4cm]{fig1}
-\caption{Sample EPS figure }
-\label{fig1}
-\end{center}
-\end{figure}
+\subsection{Moderation Tools}
 
-Below is another figure using LaTeX commands.
+\subsection{Hierarchical organization of comments}
 
-\begin{figure}[ht]
-\begin{center}
-\setlength{\unitlength}{1pt}
-\footnotesize
-\begin{picture}(160,80)
-        \put(0,0){\framebox(160,80)[]{}}
-        \put(10,35){\framebox(80,40){}}
-        \put(100,20){\framebox(40,20){}}
-        \put(70,10){\framebox(20,10){}}
-        \put(20,5){\framebox(10,5){}}
-\end{picture}
-\caption{Sample Figure Caption}
-\end{center}
-\end{figure}
+\subsection{Comment Summaries}
 
-\subsubsection{Tables}
+\subsection{Live Latex Preview}
 
-All tables must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn tables. Table number and title always appear before the
-table.
-
-One line space before the table title, one line space after the table
-title and one line space after the table. The table title must be
-initial caps and each table numbered consecutively.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Sample Table}
-
-\bigskip
-
-\begin{tabular}{|l|l|r|}
-\hline
-A & B & 1\\ \hline
-C & D & 2\\
-E & F & 3\\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Handling References}
-
-Use a first level heading for the references. References follow the
-acknowledgements.
-
-\subsubsection{Acknowledgements}
-
-Use a third level heading for the acknowledgements. All acknowledgements
-go at the end of the paper.
+\subsubsection*{Acknowledgements}
 

### 2021-07-07 paper1.tex
Sections 1 and 2

@@
 \author{
-Abhishek Chugh \\ Sophize Foundation\\
-                Bengaluru, India \\ abc@sophize.org
+Abhishek Chugh
 }
 
-\institution{}
+\institution{ Sophize Foundation\\
+                Bengaluru, India \\ abc@sophize.org }
 
@@
 \begin{abstract}
-Providing mathematicians to see connections of Mathematical objects (definitions, propositions, proofs) within and across multiple document has the potential to vastly accelerate mathematical research.
+We want to provide mathematicians the ability to deeply explore the concepts embedded across the math literature effortlessly.
 We extend the markdown language and to demonstrate a new interactive way of representing such deeply connected mathematical knowledge on the web.
@@
 Sophize is a novel Mathematics library and discussion platform.
-Mathematical proofs are developed from multiple POV (foundations, verification standards) and a single proof spans across a large number of documents - theorems to axioms.
-Our primary mission is to make it easy for mathematicians to allow mathematicians to find, discuss and discover such proofs.
-To achieve this mission, we are working on three goals:
+Our primary mission is to help our users find existing and discover new proofs of mathematical statements and utilize this knowledge for their work.
+All mathematical proofs can be seen as directed acyclic graphs of logical arguments that span across a large number of documents and databases.
+These proofs arise from a variety of different foundations such as ZFC, intuitionistic logic, type theory, and many others.
+The arguments used in any proof are considered valid based on standards - most academic mathematics is peer-reviewed, some mathematic proofs can be found in community curated sources such as Wikipedia.
+Proofs can also be algorithmically generated, and at the highest level of verification is when they are represented in a formal language.
+Thus, to aggregate proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces that are needed for such an organization.
+In this article, we focus on these user interfaces that help users to effortless navigate and understand existing proofs and discover new ones.
+Our work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
+The GDML committee comprising of multiple leaders in the math community recognized this network is largely unexplored and formalizing it will accelerate math research.
 
-formalize the largely unexplored network of information embedded in the connections of mathematical objects as envisioned by the GDML committee.
-Using the network of information to combine proofs based on each user’s chosen foundations and verification standards.
-Create a platform that is tailored for communication of mathematical ideas which utilizes and augments the network of information.
-
-To achieve the above goals, we believe it is necessary to create a new format that is as extremely convenient for a casual web conversation of mathematical ideas and is powerful enough to embed mathematical entities (definitions, theorems, proofs etc.) from a wide variety of sources.
-The markdown language has the simplicity, extensibility and wide acceptance on the web that we are looking for.
-Sophize markdown extends the markdown format to meet our requirements.
-
-The communication interface on the Sophize is designed to help mathematicians easily make sense of the discussion even when a post receives a large number of comments from many collaborators.
+In this paper, we first discuss the creation of a language, which is an extension of Markdown language.
+It is convenient enough to be used for a casual discussion of mathematical ideas over the web and is powerful enough to embed mathematical entities such as definitions, theorems, proofs from a wide variety of sources, including formal languages.
+Secondly, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
+The design focuses on making it easy for the participants to understand the current progress even when a large number of comments have been posted by many collaborators.
 We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to come with the design of our interface.
@@
 In fact, a large portion of the interface is derived directly from the list of features desired and posted on their respective blogs by Prof Timothy Gowers and Prof Terence Tao.
-We believe that these features will not only aid large scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
+We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
 
@@
 
-Describe def, prop, arg, resourcepointer.
+Before we describe the Sophize markdown language, it would be necessary to briefly describe how we model mathematical entities\footnote{This datamodel is published in JSON schema and language such as Typescript, Python at https://github.com/Sophize}.
+Here we describe parts of some of the concepts relevant for this paper.
 
-\subsection{Sophize Markdown}
+\subsection*{Resource}
+A resource is an abstract concept inherited by all other top-level concepts like terms, propositions and arguments.
+It contains fields such as search tags and citations, and a unique identifier used to refer to this concept called a resource pointer.
+
+A resource pointer consists of two parts first a namespace-like identifier which indicated the source of the data and a resource-id that that indicates the what kind of resource it is and its specific address.
+
+For example, the definition (\textbf{T}erm) of cone extracted from wikipedia may have the resource pointer \emph{wiki/T\_cone} and Pythagoras's theorem (\textbf{P}roposition) represented in the metamath project may have the resource pointer \emph{metamath/P\_pythagoras}.
+
+\subsection*{Term}
+A term is a clearly defined entity that can be used to make up a valid proposition.
+It can be a mathematical object, operator, symbol, entity, data structure, algorithm or even a person.
+Meaningless symbols in formal theories also categorized as terms.
+
+\subsection*{Proposition}
+A proposition is grammatically valid statement that can be either true or false. Axioms, theorems, conjectures, hypothesis, lemmas, corollaries, converses are all classified as propositions.
+
+\subsection*{Argument}
+An argument is set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
+In addition, most arguments have a supporting text that explains how the conclusion follows from the premises.
+
+\section{Sophize Markdown}
 
@@
 
-\subsubsection{Latex extension}
+\subsection{Latex extension}
 
@@
 
-\subsubsection{Link extension}
+\subsection{Link extension}
 
@@
 
-\paragraph{Link Types}
+\subsubsection{Link Types}
 Overlay, NO LINK,
 
-\paragraph{Status indicators}
+\subsubsection{Status indicators}
 
-\paragraph{Resource Expansion}
+\subsubsection{Resource Expansion}
 
-\subsubsection{Formal Language Support}
+\subsection{Formal Language Support}
 
@@
 
-\subsubsection{Renderer}
-\paragraph{ Indicators }
-\paragraph{ Resource Overlay }
-\paragraph{ Proof views }
+\subsection{Renderer}
+\subsubsection{ Indicators }
+\subsubsection{ Resource Overlay }
+\subsubsection{ Proof views }
 

### 2021-07-08 paper1.tex
More sections

@@
 \usepackage{onecolceurws}
+\usepackage{csquotes}
 
@@
 All mathematical proofs can be seen as directed acyclic graphs of logical arguments that span across a large number of documents and databases.
-These proofs arise from a variety of different foundations such as ZFC, intuitionistic logic, type theory, and many others.
+These proofs arise from a variety of foundations such as ZFC, intuitionistic logic, type theory, and many others.
 The arguments used in any proof are considered valid based on standards - most academic mathematics is peer-reviewed, some mathematic proofs can be found in community curated sources such as Wikipedia.
-Proofs can also be algorithmically generated, and at the highest level of verification is when they are represented in a formal language.
-Thus, to aggregate proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces that are needed for such an organization.
-In this article, we focus on these user interfaces that help users to effortless navigate and understand existing proofs and discover new ones.
+Proofs can also be algorithmically generated, and at the highest level of verification, they are represented in a formal language.
+Thus, to aggregate proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces needed for such an organization.
+This article focuses on these user interfaces that help users effortlessly navigate and understand existing proofs and discover new ones.
 Our work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
-The GDML committee comprising of multiple leaders in the math community recognized this network is largely unexplored and formalizing it will accelerate math research.
+The GDML committee comprising of multiple leaders in the math community recognized this network is largely unexplored, and formalizing it will accelerate math research.
 
-In this paper, we first discuss the creation of a language, which is an extension of Markdown language.
-It is convenient enough to be used for a casual discussion of mathematical ideas over the web and is powerful enough to embed mathematical entities such as definitions, theorems, proofs from a wide variety of sources, including formal languages.
+In this paper, we first discuss the details of a Sophize Markdown, which is an extension of Markdown language.
+It is convenient enough to be used for a casual discussion of mathematical ideas over the web.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, proofs from a wide variety of sources, including formal languages.
 Secondly, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
-The design focuses on making it easy for the participants to understand the current progress even when a large number of comments have been posted by many collaborators.
-We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to come with the design of our interface.
+The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments.
+We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to come up with our interface design.
 Conveniently, the leaders have publically analysed these projects and suggested technical improvements suitable for such collaborations.
@@
 \subsection*{Resource}
-A resource is an abstract concept inherited by all other top-level concepts like terms, propositions and arguments.
-It contains fields such as search tags and citations, and a unique identifier used to refer to this concept called a resource pointer.
+A resource is an abstract concept inherited by all other top-level concepts like terms, propositions and arguments. It contains fields such as search tags and citations, and a URI.
 
-A resource pointer consists of two parts first a namespace-like identifier which indicated the source of the data and a resource-id that that indicates the what kind of resource it is and its specific address.
+A uri consists of two parts: a namespace-like identifier called dataset-id which indicates the source of the data and a resource-id that that indicates the what kind of resource it is and its specific address.
+The dataset-id may be omitted and if it can be inferred from the surrounding context.
 
-For example, the definition (\textbf{T}erm) of cone extracted from wikipedia may have the resource pointer \emph{wiki/T\_cone} and Pythagoras's theorem (\textbf{P}roposition) represented in the metamath project may have the resource pointer \emph{metamath/P\_pythagoras}.
+For example, Pythagoras's theorem (\textbf{P}roposition) represented in the metamath project may have the uri \emph{metamath/\textbf{P}\_pythagoras} and the definition (\textbf{T}erm) of cone extracted from wikipedia may have the uri \emph{wiki/\textbf{T}\_cone}.
+When used inside another resource in the 'wiki' dataset, cone's definition can be pointed simply by \emph{T\_cone}.
 
@@
 In addition, most arguments have a supporting text that explains how the conclusion follows from the premises.
+A proof can thus be seen as directed graph of arguments and propositions.
 
 \section{Sophize Markdown}
+Markdown is a lightweight markup language for creating formatted text using a plain-text editor.
+Markdown is very widely adopted on the web and it makes quite simple to add lists, headers, bold/italic fonts, images and more.
+One can choose from a number of slightly varying markdown specifications.
+We start with the widely supported CommonMark specification and create extensions that are needed for our requirements.
+The extensions are implemented using the `markdown-it' JavaScript parser.
+The parser for Sophize markdown produces an AST tree.
+A separate renderer module utilizes the AST tree to create the appropriate HTML or Single Page Application (SPA) libraries that can be used in frameworks like Angular, React or Vue.
 
-What is markdown, out of box features
+\subsection{Parser Extension: Tex Math}
+While there are multiple applications that extend markdown to support TeX, there is no clear standard specification on the syntax.
+However, Pandoc is the most widely tool for converting LaTeX to markdown and its specification is well documented and tested.
+Thus, we use their math specification for our extension:
 
-\subsection{Latex extension}
+\blockquote{Anything between two \$ characters will be treated as TeX math.
+The opening \$ must have a non-space character immediately to its right, while the closing \$ must have a non-space character immediately to its left, and must not be followed immediately by a digit.
+Thus, \$20,000 and \$30,000 won’t parse as math.
+If for some reason you need to enclose text in literal \$ characters, backslash-escape them and they won’t be treated as math delimiters.
 
-Third level headings must be flush left, initial caps and bold.
-One line space before the third level heading and $1/2$ line
-space after the third level heading.
+For display math, use \$\$ delimiters.
+(In this case, the delimiters may be separated from the formula by whitespace.
+However, there can be no blank lines between the opening and closing \$\$ delimiters.)}
 
-\subsection{Link extension}
+\subsection{Parser Extension: Resource Links}
+This extensions allows embedding easily embed links to resources such as terms, propositions, and arguments. Links can be added using the URI and the following formats are supported:
 
-Fourth level headings must be flush left, initial caps and roman type.
-One line space before the fourth level heading and $1/2$ line
-space after the fourth level heading.
+\begin{itemize}
+	\item \#URI[ $\vert$ OPTIONS]
 
-\subsubsection{Link Types}
+	Examples: \#wiki/T\_cone, \#planetmath/P\_covering\_lemma$\vert$NO\_LINK$\vert$LC
+	\item \#(URI, [\textquotesingle LINK\_TEXT\textquotesingle][ $\vert$ OPTIONS])
+
+	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_greens\_lemma, EXPAND)
+\end{itemize}
+
+\subsubsection{Options}
+The different resource link options provide multiple ways to embed a resource in the markdown.
+These are required to make it convenient for the content creators to provide a rich experience for their readers.
+
 Overlay, NO LINK,
-
-\subsubsection{Status indicators}
 
@@
 \subsection{Formal Language Support}
-
-Indicate footnotes with a number\footnote{This is a sample footnote} in
-the text. Place the footnotes at the bottom of the page they appear on.
-Precede the footnote with a vertical rule of 2 inches (12 picas).
+In case of formal languages, definitions of terms, statements of propositions and even argument supporting text may be parse-able by an external parser.
+In such a case, we can convert the externally parsed output into regular markdown where each term is automatically linked to the appropriate resource.
+This provides for a very pleasant interface, where the user types in the native language and the final output automatically highlights all parts of a term.
+Currently, this is demonstrated on the Sophize Markdown with the metamath language.
 
 \subsection{Renderer}
+
 \subsubsection{ Indicators }

### 2021-07-09 paper1.tex
First draft complete

--- 2021-07-06 paper1.tex
@@
 \usepackage{onecolceurws}
+\usepackage{csquotes}
+\usepackage{hyperref}
 
-\title{Sophize Markdown and Communication Interface }
+\title{Sophize Markdown and Collaboration Interface }
 
 \author{
-Abhishek Chugh \\ Sophize Foundation\\
-                Bengaluru, India \\ abc@sophize.org
+Abhishek Chugh
 }
 
-\institution{}
+\institution{ Sophize Foundation\\
+                Bengaluru, India \\ abc@sophize.org }
 
@@
 \begin{abstract}
-Providing mathematicians to see connections of Mathematical objects (definitions, propositions, proofs) within and across multiple document has the potential to vastly accelerate mathematical research.
-We extend the markdown language and to demonstrate a new interactive way of representing such deeply connected mathematical knowledge on the web.
-We also utilize this new language to create a novel communication system that is specially built to allow a large number of collaborators to collaboratively solve mathematical problems.
+We extend the markdown language to represent the connections of mathematical objects that exist across various sources of knowledge.
+Using the new language, we demonstrate an interactive interface that helps its users effortlessly explore mathematics content on the web.
+We also utilize this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
+
 \end{abstract}
+
 \vskip 32pt
@@
 Sophize is a novel Mathematics library and discussion platform.
-Mathematical proofs are developed from multiple POV (foundations, verification standards) and a single proof spans across a large number of documents - theorems to axioms.
-Our primary mission is to make it easy for mathematicians to allow mathematicians to find, discuss and discover such proofs.
-To achieve this mission, we are working on three goals:
+Our primary mission is to help our users find existing and discover new proofs of mathematical statements and utilize this knowledge for their work.
+All mathematical proofs can be seen as directed acyclic graphs of logical arguments that span across a large number of documents and databases.
+These proofs arise from a variety of foundations such as ZFC, intuitionistic logic and type theory.
+The arguments used in any proof are considered valid based on varying criteria - most academic mathematics is peer-reviewed, some mathematic proofs can be found in community curated sources such as Wikipedia.
+Proofs can also be algorithmically generated, and at the highest level of verification, they are represented and verified using as formal system.
+Thus, aggregating proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces needed for such an organization.
+This article focuses on these user interfaces that help to navigate and understand existing proofs and discover new ones.
+Our work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
+The committee on planning a global library of the mathematical sciences recognized this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research\cite{sciences2014developing}.
+This introductory video gives an overview of our how structured knowledge can help: \url{https://youtu.be/Wb1JbW9Otek}.
 
-formalize the largely unexplored network of information embedded in the connections of mathematical objects as envisioned by the GDML committee.
-Using the network of information to combine proofs based on each user’s chosen foundations and verification standards.
-Create a platform that is tailored for communication of mathematical ideas which utilizes and augments the network of information.
-
-To achieve the above goals, we believe it is necessary to create a new format that is as extremely convenient for a casual web conversation of mathematical ideas and is powerful enough to embed mathematical entities (definitions, theorems, proofs etc.) from a wide variety of sources.
-The markdown language has the simplicity, extensibility and wide acceptance on the web that we are looking for.
-Sophize markdown extends the markdown format to meet our requirements.
-
-The communication interface on the Sophize is designed to help mathematicians easily make sense of the discussion even when a post receives a large number of comments from many collaborators.
-We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to come with the design of our interface.
-Conveniently, the leaders have publically analysed these projects and suggested technical improvements suitable for such collaborations.
-In fact, a large portion of the interface is derived directly from the list of features desired and posted on their respective blogs by Prof Timothy Gowers and Prof Terence Tao.
-We believe that these features will not only aid large scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
+In this paper, we first discuss the details of Sophize Markdown, an extension of Markdown language.
+It is convenient enough to be used for a casual discussion of mathematical ideas over the web.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, proofs from a wide variety of sources, including formal languages.
+Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
+The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments.
+We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to develop our interface design.
+Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
+In fact, a large portion of the interface is designed specifically overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}.
+We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
 
@@
 
-Describe def, prop, arg, resourcepointer.
+Before we describe the Sophize markdown language, it would be necessary to briefly describe how we model mathematical entities.
+The data model is published in JSON schema\cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
+We describe relevant parts of the concepts used here.
 
-\subsection{Sophize Markdown}
+\subsection*{Resource}
 
-What is markdown, out of box features
+A resource is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments. Each resource has a URI and contains fields such as search tags and citations.
 
-\subsubsection{Latex extension}
+A URI consists of two parts: a namespace-like identifier called dataset-id, which indicates the data source, and a resource-id that indicates what kind of resource it is along with its unique name in the data source.
+The dataset-id may be omitted if it can be inferred from the surrounding context.
 
-Third level headings must be flush left, initial caps and bold.
-One line space before the third level heading and $1/2$ line
-space after the third level heading.
+For example, Pythagoras's theorem (\textbf{P}roposition) represented in the Metamath project may have the uri \emph{metamath/\textbf{P}\_pythagoras} and the definition of cone (\textbf{T}erm) extracted from wikipedia may have the uri \emph{wiki/\textbf{T}\_cone}.
+When used inside another resource in the 'wiki' dataset, cone's definition can be referred simply by \emph{T\_cone}.
 
-\subsubsection{Link extension}
+\subsection*{Term}
 
-Fourth level headings must be flush left, initial caps and roman type.
-One line space before the fourth level heading and $1/2$ line
-space after the fourth level heading.
+A term is a clearly defined entity that can be used to make up a valid proposition.
+It can be a mathematical object, operator, symbol, entity, data structure, algorithm, or even a person.
+`Meaningless' primitives in formal theories are also categorized as terms.
 
-\paragraph{Link Types}
-Overlay, NO LINK,
+\subsection*{Proposition}
 
-\paragraph{Status indicators}
+A proposition is a grammatically valid statement that can be either true or false. Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, converses are all classified as propositions.
 
-\paragraph{Resource Expansion}
+\subsection*{Argument}
 
-\subsubsection{Formal Language Support}
+An argument is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
+In addition, most arguments have a supporting text that explains how the conclusion follows from the premises.
+A proof is seen as a directed graph of arguments and propositions.
 
-Indicate footnotes with a number\footnote{This is a sample footnote} in
-the text. Place the footnotes at the bottom of the page they appear on.
-Precede the footnote with a vertical rule of 2 inches (12 picas).
+\section{Sophize Markdown}
 
-\subsubsection{Renderer}
-\paragraph{ Indicators }
-\paragraph{ Resource Overlay }
-\paragraph{ Proof views }
+Markdown is a lightweight markup language for creating formatted text using a plain-text editor.
+Markdown is very widely adopted on the web, and it makes it quite simple to add lists, headers, bold/italic fonts, images, and more.
+One can choose from several slightly varying markdown specifications.
+We start with the widely supported CommonMark specification and create extensions that are needed for our requirements.
+The extensions are implemented using the `markdown-it' \cite{markdown_it} JavaScript parser.
+The parser for Sophize markdown produces an AST tree.
+A separate renderer module utilizes the AST tree to create the appropriate HTML or Single Page Application (SPA) libraries.
+Many of the features described here are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}
+
+\subsection{Parser Extension: Tex Math}
+
+While multiple applications extend markdown to support TeX, there is no standardized syntax specification.
+However, Pandoc is the most widely tool for converting LaTeX to markdown, and its specification is well documented and tested.
+Thus, we use their specification for our extension\cite{pandoc}:
+
+\blockquote{Anything between two \$ characters will be treated as TeX math.
+The opening \$ must have a non-space character immediately to its right, while the closing \$ must have a non-space character immediately to its left, and must not be followed immediately by a digit.
+Thus, \$20,000 and \$30,000 won’t parse as math.
+If for some reason you need to enclose text in literal \$ characters, backslash-escape them and they won’t be treated as math delimiters.
+
+For display math, use \$\$ delimiters.
+(In this case, the delimiters may be separated from the formula by whitespace.
+However, there can be no blank lines between the opening and closing \$\$ delimiters.)}
+
+\subsection{Parser Extension: Resource Links}
+
+This extension allows embedding easily embed links to resources such as terms, propositions, and arguments. Links can be added using the URI, and the following formats are supported:
+
+\begin{itemize}
+
+	\item \#URI[ $\vert$ OPTIONS]
+
+	Examples: \#wiki/T\_cone, \#planetmath/P\_covering\_lemma$\vert$NO\_LINK$\vert$LC
+
+	\item \#(URI, [\textquotesingle LINK\_TEXT\textquotesingle][ $\vert$ OPTIONS])
+
+	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_greens\_lemma, EXPAND)
+
+\end{itemize}
+
+\subsubsection{Options}
+
+The different resource link options provide different ways to embed a resource in the markdown.
+These are required to make it convenient for the content creators to provide a rich experience for their readers.
+The following are most commonly used:
+
+\paragraph{NAME (default)}
+
+Fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the terms.
+
+\paragraph{EXPAND}
+
+Instead of creating a link, expands the resource in place.
+For terms and propositions, the definition and the statement are added in place, respectively.
+For arguments, the premises, conclusion, and the argument text is added in place.
+
+\paragraph{OVERLAY\_LINK (default)}
+
+In the case of an overlay link, clicking on the link opens up a modal dialog to show a resource summary instead of navigating to another URL.
+
+\paragraph{NAV\_LINK}
+
+Clicking the link causes the browser to navigate to the web page indicated by the resource's URI.
+
+\paragraph{LOWER\_CASE or LC}
+
+Lower cases the link text. This becomes quite useful when adding a link in the middle of a sentence where adding the name in its default case would be grammatically incorrect.
+
+\paragraph{SHOW\_TVI (default)}
+
+For propositions only. Adds a truth value icon indicating whether or not there is a proof available for the proposition. Clicking on the icon brings up the proof as a graph of arguments.
+
+\paragraph{HIDE\_TVI}
+
+The truth value icon is hidden.
+
+\subsection{Formal Language Support}
+
+In formal languages, definitions of terms, statements of propositions, and supporting argument text may be parseable by an external parser.
+We can convert the externally parsed output into markdown in such a case, where each term is automatically linked to the appropriate resource.
+This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to deeply explore all concepts than make up the input statement.
+Currently, this is demonstrated in the Sophize Markdown with the Metamath language.
 
 \section{Sophize Collaboration Interface}
-Guiding principles/motivations?
+
+Sophize collaboration interface is designed to allow multiple researchers to simultaneously discuss multiple approaches to solve the problem of interest.
+In open online collaborations, a lot of different ideas and approaches get introduced rapidly.
+Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that dissuades even the experts and the highly motivated.
+This work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects.
+We believe that the interface can aid all collaborations types - with few or many participants.
+We demonstrate the various features of this interface by incorporating actual data from a polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
+
+\subsubsection*{Requirements}
+
+In open online collaborations, a lot of different ideas and approaches get introduced rapidly.
+Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task.
+This is perhaps the primary impediment that dissuades even the experts and the highly motivated from participating.
+
+To solve this problem, we need to organize the ideas that get tossed rapidly and summarize the progress.
+A reader should be able to quickly grasp the current progress, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.
+
+Some of the other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog (lightly edited):
+
+\begin{itemize}
+
+  \item LaTeX support
+
+  \item Group moderation
+
+  \item Comment editing and preview
+
+  \item Comment numbering and/or threading
+
+  \item Wiki-like features, i.e., group-editable, publicly-viewable documents with version control
+
+  \item Some way to view all recent comments or developments in a project
+
+  \item Easy registration process
+
+  \item Easy commenting process (i.e., no technical knowledge required)
+
+  \item Permanent URLs for posts and comments (for link-back purposes)
+
+\end{itemize}
+
+WE note that Sophize provides all the above features except that it doesn't let users look at the versions of documents. We summarize innovative features of the platform below:
+
 \subsection{Hierarchical Page Organization}
 
-\subsection{Using existing math content}
+As noted by Prof Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
+The "proof discovery tree," as Gower calls it, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
+The leaves of the tree would thus be sub-problems that get solved without division into sub-problems.
 
-\subsection{Referencing Comments}
+Sophize brings the 'Proof-discovery tree' to life by organizing the project using neatly organized wiki-like pages.
+Pages have a parent-child relationship allowing them to be organized like a tree.
+Discussion comments can be posted on any page, and moderators can re-arrange them the way they think is best for the project.
+Moderators are also encouraged to add an overview on each page that would quickly inform readers of the significant ideas that they should know before they start contributing.
+
+\subsection{Comment Summaries}
+
+Even after the hierarchical division of comments, some pages can still have a large number of comments, which would be difficult to follow.
+To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far.
+For example, they can club together multiple comment chains that were dead ends so that each reader doesn't waste their time.
+Or they could summarize a sub-proof that was arrived at after dozens of comments for future readers.
+
+\subsection{Sophize Markdown benefits}
+
+Project collaborators get all the benefits of Sophize Markdown, such as easy linking of existing math content, latex support, and live preview of pages and comments being written or edited.
+
+Comments in Sophize are numbered serially (starting with 1 for each collaboration),
+
+each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment).
+
+Comments in different projects can be references by providing the URI (\#URI/COMMENT\_NUMBER).
 
@@
 
-\subsection{Hierarchical organization of comments}
-
-\subsection{Comment Summaries}
-
-\subsection{Live Latex Preview}
+Sophize gives moderators usual moderation tools like spam removal and fine-grained access control to manage participants.
+In addition, we add a new feature where certain comments can be marked hidden.
+Often, threads of dozens of comments can be just noise in such discussions because they were based on confused concepts or mistaken assumptions.
+Such comments should not be marked as spam.
+By marking such threads as 'hidden,' moderators can ensure that these are not shown by default.
+But any user can choose to see them if needed.
 
@@
 
-%\bibliographystyle{alpha} 
-%\bibliography{samplebib}
+...
+
+\bibliographystyle{alpha}
+
+\bibliography{mybib}
+
 %inline the .bbl file directly for mailing to authors.
 
-\begin{thebibliography}{Com79}
+%\begin{thebibliography}{Com79}
 
-\bibitem[Com79]{Comer-btree}
-D.~Comer.
-\newblock The ubiquitous b-tree.
-\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
+%\bibitem[Com79]{Comer-btree}
+%D.~Comer.
+%\newblock The ubiquitous b-tree.
+%\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
 
-\bibitem[Knu73]{Knuth-vol3}
-D.~E. Knuth.
-\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
-  Searching}.
-\newblock Addison-Wesley, 1973.
+%\bibitem[Com79]{Comer-btree}
+%D.~Comer. \newblock The ubiquitous b-tree. \newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
 
-\end{thebibliography}
+%\bibitem[Knu73]{Knuth-vol3}
+%D.~E. Knuth. \newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and Searching}. \newblock Addison-Wesley, 1973.
+%\end{thebibliography}
 

### 2021-07-09 paper1.tex
Fix some issues

@@
 
-Fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the terms.
+Fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.
 
@@
 
-In open online collaborations, a lot of different ideas and approaches get introduced rapidly.
-Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task.
-This is perhaps the primary impediment that dissuades even the experts and the highly motivated from participating.
-
+Helping users make sense of the conversation and allowing them to get up to speed with existing conversation as quickly as possible is perhaps the most important requirement for managing online collaborations.
 To solve this problem, we need to organize the ideas that get tossed rapidly and summarize the progress.
@@
 
-Some of the other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog (lightly edited):
+Some of the other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):
 
@@
 
-WE note that Sophize provides all the above features except that it doesn't let users look at the versions of documents. We summarize innovative features of the platform below:
+We note that Sophize provides all the above features except that it doesn't yet allow users to look at the previous versions of documents. We summarize innovative features of the platform below:
 
@@
 As noted by Prof Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
-The "proof discovery tree," as Gower calls it, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
+The `proof discovery tree', as Gowers calls it \cite{gowers_weblog_2009}, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
 The leaves of the tree would thus be sub-problems that get solved without division into sub-problems.
 
-Sophize brings the 'Proof-discovery tree' to life by organizing the project using neatly organized wiki-like pages.
+Sophize brings the `Proof-discovery tree' to life by organizing the project using neatly organized wiki-like pages.
 Pages have a parent-child relationship allowing them to be organized like a tree.
 Discussion comments can be posted on any page, and moderators can re-arrange them the way they think is best for the project.
-Moderators are also encouraged to add an overview on each page that would quickly inform readers of the significant ideas that they should know before they start contributing.
+Moderators are also encouraged to add an overview on each page that would quickly inform readers of the significant ideas that they should be familiar with before they start contributing.
 
@@
 For example, they can club together multiple comment chains that were dead ends so that each reader doesn't waste their time.
-Or they could summarize a sub-proof that was arrived at after dozens of comments for future readers.
+Or to save time of future readers, they could summarize a sub-proof that was arrived at after dozens of comments.
 
@@
 
-Comments in Sophize are numbered serially (starting with 1 for each collaboration),
-
-each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment).
-
+Comments in Sophize are numbered serially (starting with 1 for each collaboration), each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment).
 Comments in different projects can be references by providing the URI (\#URI/COMMENT\_NUMBER).
@@
 
-Sophize gives moderators usual moderation tools like spam removal and fine-grained access control to manage participants.
+Sophize gives moderators usual tools like spam removal and fine-grained access control to manage participants.
 In addition, we add a new feature where certain comments can be marked hidden.
-Often, threads of dozens of comments can be just noise in such discussions because they were based on confused concepts or mistaken assumptions.
+Often, threads of dozens of comments can be just noise because they were based on confused concepts or mistaken assumptions.
 Such comments should not be marked as spam.
-By marking such threads as 'hidden,' moderators can ensure that these are not shown by default.
-But any user can choose to see them if needed.
+By marking such threads as `hidden', moderators can ensure that these are not shown by default.
+But any user can choose to see them if they wish to.
 

### 2021-07-10 paper1.tex
Minor fixes

@@
 These proofs arise from a variety of foundations such as ZFC, intuitionistic logic and type theory.
-The arguments used in any proof are considered valid based on varying criteria - most academic mathematics is peer-reviewed, some mathematic proofs can be found in community curated sources such as Wikipedia.
-Proofs can also be algorithmically generated, and at the highest level of verification, they are represented and verified using as formal system.
+The arguments used in any proof are considered valid based on varying criteria - most academic mathematics is peer-reviewed, some mathematical proofs can be found in community curated sources such as Wikipedia.
+Proofs can also be algorithmically generated, and at the highest level of verification, they are represented and verified using a formal system.
 Thus, aggregating proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces needed for such an organization.
@@
 The committee on planning a global library of the mathematical sciences recognized this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research\cite{sciences2014developing}.
-This introductory video gives an overview of our how structured knowledge can help: \url{https://youtu.be/Wb1JbW9Otek}.
+This introductory video gives an overview of how structured knowledge can help: \url{https://youtu.be/Wb1JbW9Otek}.
 
@@
 It is convenient enough to be used for a casual discussion of mathematical ideas over the web.
-It is also powerful enough to embed mathematical entities such as definitions, theorems, proofs from a wide variety of sources, including formal languages.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from a wide variety of sources, including formal languages.
 Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
@@
 Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
-In fact, a large portion of the interface is designed specifically overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}.
+In fact, a large portion of the interface is designed specifically to overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}.
 We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
@@
 For example, Pythagoras's theorem (\textbf{P}roposition) represented in the Metamath project may have the uri \emph{metamath/\textbf{P}\_pythagoras} and the definition of cone (\textbf{T}erm) extracted from wikipedia may have the uri \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the 'wiki' dataset, cone's definition can be referred simply by \emph{T\_cone}.
+When used inside another resource in the 'wiki' dataset, cone's definition can be referred to simply by \emph{T\_cone}.
 
@@
 While multiple applications extend markdown to support TeX, there is no standardized syntax specification.
-However, Pandoc is the most widely tool for converting LaTeX to markdown, and its specification is well documented and tested.
+However, Pandoc is the most widely used tool for converting LaTeX to markdown, and its specification is well documented and tested.
 Thus, we use their specification for our extension\cite{pandoc}:
@@
 
-This extension allows embedding easily embed links to resources such as terms, propositions, and arguments. Links can be added using the URI, and the following formats are supported:
+This extension allows easily adding links to resources such as terms, propositions, and arguments. Links can be added using the URI, and the following formats are supported:
 
@@
 
-Instead of creating a link, expands the resource in place.
+Instead of creating a link, this option expands the resource in place.
 For terms and propositions, the definition and the statement are added in place, respectively.
@@
 This work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects.
-We believe that the interface can aid all collaborations types - with few or many participants.
+We believe that the interface can aid many collaboration types - with few or many participants.
 We demonstrate the various features of this interface by incorporating actual data from a polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
@@
 Pages have a parent-child relationship allowing them to be organized like a tree.
-Discussion comments can be posted on any page, and moderators can re-arrange them the way they think is best for the project.
+Discussion comments can be posted on any page, and moderators can rearrange them the way they think is best for the project.
 Moderators are also encouraged to add an overview on each page that would quickly inform readers of the significant ideas that they should be familiar with before they start contributing.
@@
 To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far.
-For example, they can club together multiple comment chains that were dead ends so that each reader doesn't waste their time.
-Or to save time of future readers, they could summarize a sub-proof that was arrived at after dozens of comments.
+For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste their time.
+Or to save time for future readers, they could summarize a sub-proof that was arrived at after dozens of comments.
 

### 2021-07-11 paper1.tex
Add 'sources' section

@@
 Sophize gives moderators usual tools like spam removal and fine-grained access control to manage participants.
-In addition, we add a new feature where certain comments can be marked hidden.
+We also add a new feature where certain comments can be marked hidden.
 Often, threads of dozens of comments can be just noise because they were based on confused concepts or mistaken assumptions.
@@
 But any user can choose to see them if they wish to.
+
+\subsubsection*{Sources}
+Sophize markdown parser and its Angular renderer source code is available with MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
+The NPM packages for these projects are named `sophize-md-parser' and `ngx-sophize-md-renderer'.
 

### 2021-07-11 paper1.tex
More improvements

@@
 The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments.
-We studied the nature of collaboration on Polymath projects - massively collaborative online mathematical projects to develop our interface design.
+We studied the nature of collaboration on Polymath projects\cite{polymath_blog} - massively collaborative online mathematical projects to develop our interface design.
 Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
@@
 
-\subsection{Parser Extension: Tex Math}
-
-While multiple applications extend markdown to support TeX, there is no standardized syntax specification.
-However, Pandoc is the most widely used tool for converting LaTeX to markdown, and its specification is well documented and tested.
-Thus, we use their specification for our extension\cite{pandoc}:
-
-\blockquote{Anything between two \$ characters will be treated as TeX math.
-The opening \$ must have a non-space character immediately to its right, while the closing \$ must have a non-space character immediately to its left, and must not be followed immediately by a digit.
-Thus, \$20,000 and \$30,000 won’t parse as math.
-If for some reason you need to enclose text in literal \$ characters, backslash-escape them and they won’t be treated as math delimiters.
-
-For display math, use \$\$ delimiters.
-(In this case, the delimiters may be separated from the formula by whitespace.
-However, there can be no blank lines between the opening and closing \$\$ delimiters.)}
-
-\subsection{Parser Extension: Resource Links}
+\subsection{Embedding structured data}
 
@@
 The different resource link options provide different ways to embed a resource in the markdown.
-These are required to make it convenient for the content creators to provide a rich experience for their readers.
+These are required to make it convenient for the content creators to provide a rich experience to their readers.
 The following are most commonly used:
@@
 
-For propositions only. Adds a truth value icon indicating whether or not there is a proof available for the proposition. Clicking on the icon brings up the proof as a graph of arguments.
-
-\paragraph{HIDE\_TVI}
-
-The truth value icon is hidden.
+For propositions only.
+Adds a truth value icon indicating whether or not there is a proof available for the proposition.
+Clicking on the icon brings up the proof as a graph of arguments.
+The HIDE\_TVI option makes sure that the truth value icon is always hidden.
 
@@
 
+\subsection{\LaTeX\space Support}
+
+While multiple applications extend markdown to support TeX, there is no standardized syntax specification.
+However, Pandoc is the most widely used tool for converting LaTeX to markdown, and its specification is well documented and tested.
+Thus, we use their specification for our extension\cite{pandoc}:
+
+\blockquote{Anything between two \$ characters will be treated as TeX math.
+The opening \$ must have a non-space character immediately to its right, while the closing \$ must have a non-space character immediately to its left, and must not be followed immediately by a digit.
+Thus, \$20,000 and \$30,000 won’t parse as math.
+If for some reason you need to enclose text in literal \$ characters, backslash-escape them and they won’t be treated as math delimiters.
+
+For display math, use \$\$ delimiters.
+(In this case, the delimiters may be separated from the formula by whitespace.
+However, there can be no blank lines between the opening and closing \$\$ delimiters.)}
+
 \section{Sophize Collaboration Interface}
 
-Sophize collaboration interface is designed to allow multiple researchers to simultaneously discuss multiple approaches to solve the problem of interest.
-In open online collaborations, a lot of different ideas and approaches get introduced rapidly.
+Sophize communication interface is designed to allow multiple researchers to collaboratively solve a problem.
+In such open online collaborations, a lot of different ideas and approaches get introduced rapidly.
 Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that dissuades even the experts and the highly motivated.
-This work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects.
+We believe that we have created a novel interface that can significantly mitigate this problem.
+The work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects\cite{polymath_blog}.
 We believe that the interface can aid many collaboration types - with few or many participants.
@@
 Helping users make sense of the conversation and allowing them to get up to speed with existing conversation as quickly as possible is perhaps the most important requirement for managing online collaborations.
-To solve this problem, we need to organize the ideas that get tossed rapidly and summarize the progress.
+To solve this problem, we need to organize the ideas in an intuitive way  and summarize the progress.
 A reader should be able to quickly grasp the current progress, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.
 
-Some of the other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):
+Other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):
 
@@
 To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far.
+Comment summaries get embedded in the comment tree as a parent for comments they summarise.
 For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste their time.
@@
 Comments in Sophize are numbered serially (starting with 1 for each collaboration), each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment).
-Comments in different projects can be references by providing the URI (\#URI/COMMENT\_NUMBER).
+Comments in an external project can be referenced by providing the project's URI (\#URI/COMMENT\_NUMBER).
 
-\subsection{Moderation Tools}
+Also, we make it extremely easy to extract terms, propositions and proofs from comments. These resources not only help in better understanding of the project, it also helps build Sophize's library.
 
-Sophize gives moderators usual tools like spam removal and fine-grained access control to manage participants.
+\subsection{Reducing noise}
+
+Sophize gives project moderators usual tools like spam removal and fine-grained access control to manage participants.
 We also add a new feature where certain comments can be marked hidden.
@@
 By marking such threads as `hidden', moderators can ensure that these are not shown by default.
-But any user can choose to see them if they wish to.
+But any user can see them if they wish to.
 

### 2021-07-12 paper1.tex
Suggestions from Patrick

@@
 \usepackage{hyperref}
+\usepackage{framed}
+\usepackage{mdframed}
+\usepackage{upquote}
+\usepackage{lmodern}
+\usepackage[normalem]{ulem}
 
@@
 \begin{abstract}
-We extend the markdown language to represent the connections of mathematical objects that exist across various sources of knowledge.
-Using the new language, we demonstrate an interactive interface that helps its users effortlessly explore mathematics content on the web.
-We also utilize this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
+We have extended the Markdown language to represent the connections between mathematical objects that exist across various sources of knowledge.
+Using the new language, we demonstrated an interactive interface that helps its users explore mathematics content on the web.
+We also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
+This contribution sketches the basic ideas and provides links to some demos of the new functionality.
 
@@
 
-Sophize is a novel Mathematics library and discussion platform.
-Our primary mission is to help our users find existing and discover new proofs of mathematical statements and utilize this knowledge for their work.
-All mathematical proofs can be seen as directed acyclic graphs of logical arguments that span across a large number of documents and databases.
-These proofs arise from a variety of foundations such as ZFC, intuitionistic logic and type theory.
-The arguments used in any proof are considered valid based on varying criteria - most academic mathematics is peer-reviewed, some mathematical proofs can be found in community curated sources such as Wikipedia.
+Sophize is a novel mathematics library and discussion platform.
+Our primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
+Mathematical proofs can be seen as directed acyclic graphs of logical arguments that can extend across a large number of documents and databases.
+These proofs are carried out based on a variety of foundations such as ZFC, intuitionistic logic and type theory.
+The arguments used in any proof are considered valid  or not based on criteria that can vary.
+Most academic mathematics is peer-reviewed and published, but some mathematical proofs can be found in community curated sources such as Wikipedia.
 Proofs can also be algorithmically generated, and at the highest level of verification, they are represented and verified using a formal system.
-Thus, aggregating proofs from such a wide variety of sources that utilize a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces needed for such an organization.
-This article focuses on these user interfaces that help to navigate and understand existing proofs and discover new ones.
+Thus, aggregating proofs from such a wide variety of sources that use a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces.
+This article focuses on these user interfaces that help users to navigate and understand existing proofs and discover new ones.
 Our work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
-The committee on planning a global library of the mathematical sciences recognized this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research\cite{sciences2014developing}.
+The committee on planning a global library of the mathematical sciences recognized that this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research\cite{sciences2014developing}.
 This introductory video gives an overview of how structured knowledge can help: \url{https://youtu.be/Wb1JbW9Otek}.
 
-In this paper, we first discuss the details of Sophize Markdown, an extension of Markdown language.
+In this paper, we first discuss the details of Sophize Markdown, an extension of the Markdown language.
 It is convenient enough to be used for a casual discussion of mathematical ideas over the web.
@@
 Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
-The design focuses on making it easy for the participants to understand the current progress even when many collaborators have posted a large number of comments.
-We studied the nature of collaboration on Polymath projects\cite{polymath_blog} - massively collaborative online mathematical projects to develop our interface design.
+The design focuses on making it easy for the participants to understand current progress even when many collaborators have posted a large number of comments.
+We studied the nature of collaboration on Polymath projects\cite{polymath_blog}, which are massively collaborative online mathematical projects, to develop our interface design.
 Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
-In fact, a large portion of the interface is designed specifically to overcome the issues noted by Prof Timothy Gowers \cite{gowers_weblog_2009} and Prof Terence Tao\cite{whats_new_2009}.
-We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like AiM.
+In fact, a large portion of the interface is designed specifically to overcome the issues noted by Timothy Gowers \cite{gowers_weblog_2009} and Terence Tao\cite{whats_new_2009}.
+We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like those organized by AiM.
 
@@
 
-Before we describe the Sophize markdown language, it would be necessary to briefly describe how we model mathematical entities.
+Before we describe the Sophize Markdown language, it will be necessary to briefly describe how we model mathematical entities.
 The data model is published in JSON schema\cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
@@
 
-A URI consists of two parts: a namespace-like identifier called dataset-id, which indicates the data source, and a resource-id that indicates what kind of resource it is along with its unique name in the data source.
+A URI consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that indicates what kind of resource it is along with its unique name in the data source.
 The dataset-id may be omitted if it can be inferred from the surrounding context.
 
-For example, Pythagoras's theorem (\textbf{P}roposition) represented in the Metamath project may have the uri \emph{metamath/\textbf{P}\_pythagoras} and the definition of cone (\textbf{T}erm) extracted from wikipedia may have the uri \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the 'wiki' dataset, cone's definition can be referred to simply by \emph{T\_cone}.
+For example, Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
+When used inside another resource in the 'wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
 
@@
 
-A proposition is a grammatically valid statement that can be either true or false. Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, converses are all classified as propositions.
+A proposition is a grammatically valid statement that can be either true or false. Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.
 
@@
 An argument is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
-In addition, most arguments have a supporting text that explains how the conclusion follows from the premises.
+In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
 A proof is seen as a directed graph of arguments and propositions.
@@
 Markdown is a lightweight markup language for creating formatted text using a plain-text editor.
-Markdown is very widely adopted on the web, and it makes it quite simple to add lists, headers, bold/italic fonts, images, and more.
-One can choose from several slightly varying markdown specifications.
-We start with the widely supported CommonMark specification and create extensions that are needed for our requirements.
+Markdown is very widely adopted on the web, and it makes it quite simple to add lists, headers, bold or italic fonts, images, and more.
+One can choose from several slightly varying Markdown specifications.
+We start with the widely supported CommonMark specification and create extensions that we need.
 The extensions are implemented using the `markdown-it' \cite{markdown_it} JavaScript parser.
-The parser for Sophize markdown produces an AST tree.
+The parser for Sophize Markdown produces an abstract syntax tree (AST).
 A separate renderer module utilizes the AST tree to create the appropriate HTML or Single Page Application (SPA) libraries.
@@
 
-This extension allows easily adding links to resources such as terms, propositions, and arguments. Links can be added using the URI, and the following formats are supported:
+This extension allows easily adding links to resources such as terms, propositions, and arguments. Links can be added using the resource's URI, and the following formats are supported:
 
@@
 
-\subsubsection{Options}
+There are multiple resource link options to embed a resource in the Markdown.
+These are required to make it convenient for the content creators to provide a rich experience to their readers.
+Some of the commonly used one are summarized below.
 
-The different resource link options provide different ways to embed a resource in the markdown.
-These are required to make it convenient for the content creators to provide a rich experience to their readers.
-The following are most commonly used:
+\subsubsection{Link Text Options}
 
@@
 
-\paragraph{EXPAND}
+\paragraph{CUSTOM\_TEXT}
+Link text is supplied by the user.
 
-Instead of creating a link, this option expands the resource in place.
-For terms and propositions, the definition and the statement are added in place, respectively.
-For arguments, the premises, conclusion, and the argument text is added in place.
+\paragraph{LOWER\_CASE or UPPER\_CASE}
+
+Lower cases the link text. This becomes quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.
+
+\paragraph{Example}
+As noted earlier, dataset-id of URIs can often be available from the context. We assume that to be the case to make the examples easier to read.
+The following Markdown code shows the various link text options:
+
+\begin{verbatim}
+#P_cosine_law|UC is a generalization of the #P_pythagorean for all kinds of
+#(T_triangle, 'triangles').
+\end{verbatim}
+
+\paragraph{The above code is rendered as:}
+\begin{mdframed}
+\dashuline{Law of cosines} is a generalization of the \dashuline{Pythagorean theorem} for all kinds of \dashuline{triangles}.
+\end{mdframed}
+
+\subsubsection{Link Type Options}
 
@@
 
-\paragraph{LOWER\_CASE or LC}
+\paragraph{NO\_LINK}
 
-Lower cases the link text. This becomes quite useful when adding a link in the middle of a sentence where adding the name in its default case would be grammatically incorrect.
+This is not a link but clicking or hovering on it brings up a text on the web browser indicating the URI.
 
-\paragraph{SHOW\_TVI (default)}
+\paragraph{Example}
+The following Markdown code has all three link types:
+\begin{verbatim}
+#T_matrix_multiplication|NO_LINK|UC is a #(T_commutative_property, 
+'non-commutative'|NAV_LINK) #T_binary_operation.
+\end{verbatim}
 
-For propositions only.
-Adds a truth value icon indicating whether or not there is a proof available for the proposition.
+\paragraph{The above code is rendered as:}
+\begin{mdframed}
+Matrix multiplication is a \underline{non-commutative} \dashuline{binary operation.}
+\end{mdframed}
+The first `link' shows `\#wiki/T\_matrix\_multiplication' on mouse-hover. The second link navigates the page to a different URL. Clicking on the third link shows a modal dialog box like so:
+
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=5cm]{modal}}
+\caption{Modal dialog box for the term binary operation. These boxes can also have content that uses all three types of links. }
+\label{fig1}
+\end{center}
+\end{figure}
+
+\subsubsection{Resource Expansion}
+
+Instead of creating a link, this option expands the resource in place.
+For terms and propositions, the definition and the statement are added in place, respectively.
+For arguments, the premises, conclusion, and the argument text is added in place.
+Another option `ARG\_TEXT\_ONLY' can be used for to dislay only the argument text.
+
+\paragraph{Example}
+The following is a sample article where we uses re-use concepts and theorems already extracted from multiple sources (say, Wikipedia and the Oxford dictionary):
+
+\begin{verbatim}
+# Conic section
+
+A conic section (or simply conic) is a curve obtained as the intersection of the
+#(wiki/T_conical_surface, 'surface') of a #wiki/T_cone with a #wiki/T_plane. There are
+three types of conic sections.
+
+## Ellipse
+#oxford/T_ellipse|EXPAND #wiki/P_ellipse_area|EXPAND
+
+## Parabola
+#oxford/T_parabola|EXPAND The area of a parabola is unbounded.
+
+## Hyperbola  
+#oxford/T_hyperbola|EXPAND The area of a hyperbola is unbounded.
+
+\end{verbatim}
+
+\paragraph{The above code is rendered as:}
+\begin{mdframed}
+\section*{Conic Section}
+A conic section (or simply conic) is a curve obtained as the intersection of the \dashuline{surface} of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
+
+\subsection*{Ellipse}
+An ellipse is a regular \dashuline{oval} shape, traced by a point moving in a plane so that the sum of its distances from two other points (the foci) is constant, or resulting when a cone is cut by an oblique plane which does not intersect the base.
+The area $A_{ellipse}$ enclosed by an ellipse is $$A_{ellipse} = \pi a b$$where $a$ and $b$ are the lengths of the \dashuline{semi-major} and \dashuline{semi-minor} axes, respectively.
+
+\subsection*{Parabola}
+A parabola is a \dashuline{symmetrical} open plane curve formed by the intersection of a cone with a plane parallel to its side. The area of a parabola is unbounded.
+
+\subsection*{Hyperbola}
+A Hyperbola symmetrical open curve formed by the intersection of a circular cone with a plane at a smaller angle with its axis than the side of the cone. The area of a hyperbola is unbounded.
+
+\end{mdframed}
+
+\subsubsection{Status Indicators}
+
+For propositions, a Truth Value Icon indicating whether or not there is a proof is added next to the link.
 Clicking on the icon brings up the proof as a graph of arguments.
-The HIDE\_TVI option makes sure that the truth value icon is always hidden.
+Similarly, an icon is added next to an argument which indicates whether the argument is valid or not.
+These options can be turned on or off depending on the user input and the context.
+Further details require details of the Sophize knowledge organization scheme which is not our focus here.
 
@@
 In formal languages, definitions of terms, statements of propositions, and supporting argument text may be parseable by an external parser.
-We can convert the externally parsed output into markdown in such a case, where each term is automatically linked to the appropriate resource.
-This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to deeply explore all concepts than make up the input statement.
-Currently, this is demonstrated in the Sophize Markdown with the Metamath language.
+We can convert the externally parsed output into Markdown in such a case, where each term is automatically linked to the appropriate resource.
+This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to explore all concepts than make up the input statement in depth.
+Currently, this is demonstrated in the use of Sophize Markdown with the Metamath language.
 
@@
 
-While multiple applications extend markdown to support TeX, there is no standardized syntax specification.
-However, Pandoc is the most widely used tool for converting LaTeX to markdown, and its specification is well documented and tested.
+While multiple applications extend Markdown to support TeX, there is no standardized syntax specification.
+However, Pandoc is the most widely used tool for converting \LaTeX\space to Markdown, and its specification is well documented and tested.
 Thus, we use their specification for our extension\cite{pandoc}:
@@
 
+The following example summarizes the specification:
+\begin{quote}
+\begin{verbatim} 
+Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of 
+happiness is that fetched $1.3 million recently. While it may not fetch many \$s, I 
+like the field equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
+\end{verbatim}
+\end{quote}
+
+The above Markdown code is rendered as:
+\begin{mdframed}
+Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of happiness is
+what fetched \$1.3 million recently. While it may not fetch many \$s, I like the field
+equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
+\end{mdframed}
+
 \section{Sophize Collaboration Interface}
 
-Sophize communication interface is designed to allow multiple researchers to collaboratively solve a problem.
+Sophize's communication interface is designed to allow multiple researchers to collaboratively solve a problem.
 In such open online collaborations, a lot of different ideas and approaches get introduced rapidly.
-Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that dissuades even the experts and the highly motivated.
+Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that can dissuade even the experts and the highly motivated.
 We believe that we have created a novel interface that can significantly mitigate this problem.
-The work is primarily influenced by recommendations made by Professor Timothy Gowers and Professor Terence Tao after organizing a few polymath projects\cite{polymath_blog}.
+The work is primarily influenced by recommendations made by Timothy Gowers and Terence Tao after organizing several Polymath projects\cite{polymath_blog}.
 We believe that the interface can aid many collaboration types - with few or many participants.
-We demonstrate the various features of this interface by incorporating actual data from a polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
+We demonstrate the various features of this interface by incorporating actual data from a Polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
 
@@
 
-Helping users make sense of the conversation and allowing them to get up to speed with existing conversation as quickly as possible is perhaps the most important requirement for managing online collaborations.
-To solve this problem, we need to organize the ideas in an intuitive way  and summarize the progress.
-A reader should be able to quickly grasp the current progress, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.
+Helping users make sense of the conversation and allowing them to get up to speed with existing progress as quickly as possible is perhaps the most important requirement for managing online collaborations.
+To solve this problem, we need to organize the ideas in an intuitive way and to summarize the progress.
+A reader should be able to quickly grasp the current state, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.
 
-Other technical requirements were discussed by some project participants and summarized by Prof. Tao on his blog\cite{whats_new_2009} (lightly edited):
+Other technical requirements were discussed by some project participants and summarized by Tao on his blog\cite{whats_new_2009} (lightly edited):
 
@@
 
-  \item LaTeX support
+  \item \LaTeX\space support
 
@@
 
-As noted by Prof Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
+As noted by Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
 The `proof discovery tree', as Gowers calls it \cite{gowers_weblog_2009}, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
@@
 Discussion comments can be posted on any page, and moderators can rearrange them the way they think is best for the project.
-Moderators are also encouraged to add an overview on each page that would quickly inform readers of the significant ideas that they should be familiar with before they start contributing.
+Moderators are also encouraged to add an overview on each page that quickly informs readers of the significant ideas that they should be familiar with before they start contributing.
 
@@
 
-Even after the hierarchical division of comments, some pages can still have a large number of comments, which would be difficult to follow.
+Even after the hierarchical division of comments, some pages can still have a large number of comments, which make them difficult to follow.
 To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far.
 Comment summaries get embedded in the comment tree as a parent for comments they summarise.
-For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste their time.
-Or to save time for future readers, they could summarize a sub-proof that was arrived at after dozens of comments.
+For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste time on them.
+Or they could summarize a sub-proof that was arrived at after dozens of comments.
 
@@
 
-Project collaborators get all the benefits of Sophize Markdown, such as easy linking of existing math content, latex support, and live preview of pages and comments being written or edited.
+Project collaborators get all the benefits of Sophize Markdown, such as easy linking of existing math content, \LaTeX\space support, and live preview of pages and comments being written or edited.
 
@@
 
-Sophize gives project moderators usual tools like spam removal and fine-grained access control to manage participants.
+Sophize gives project moderators the usual tools like spam removal and fine-grained access control to manage participants.
 We also add a new feature where certain comments can be marked hidden.
@@
 By marking such threads as `hidden', moderators can ensure that these are not shown by default.
-But any user can see them if they wish to.
+But any user can view them if they wish to.
 
 \subsubsection*{Sources}
-Sophize markdown parser and its Angular renderer source code is available with MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
+The Sophize Markdown parser and its Angular renderer source code are available under an MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
 The NPM packages for these projects are named `sophize-md-parser' and `ngx-sophize-md-renderer'.
@@
 \subsubsection*{Acknowledgements}
-
-...
+This publication resulted (in part) from research supported by the International Mathematical Union.
+We would like to thank Patrick Ion for encouraging us to publish our work and also for their help in organizing the content of the paper.
 

### 2021-07-12 paper1.tex
Cleanup
Reduce spaces, remove unnecessary code

@@
 
-\author{
-Abhishek Chugh
-}
+\author{ Abhishek Chugh }
 
-\institution{ Sophize Foundation\\
-                Bengaluru, India \\ abc@sophize.org }
+\institution{ Sophize Foundation\\ Bengaluru, India \\ abc@sophize.org }
 
@@
 
-## Hyperbola  
-#oxford/T_hyperbola|EXPAND The area of a hyperbola is unbounded.
+...
 
@@
 
-\subsection*{Hyperbola}
-A Hyperbola symmetrical open curve formed by the intersection of a circular cone with a plane at a smaller angle with its axis than the side of the cone. The area of a hyperbola is unbounded.
+...
 
@@
 
-The above Markdown code is rendered as:
+Assuming the terms and propositions are referenced are available, the above Markdown code is rendered as:
 \begin{mdframed}
@@
 
-%inline the .bbl file directly for mailing to authors.
-
-%\begin{thebibliography}{Com79}
-
-%\bibitem[Com79]{Comer-btree}
-%D.~Comer.
-%\newblock The ubiquitous b-tree.
-%\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
-
-%\bibitem[Com79]{Comer-btree}
-%D.~Comer. \newblock The ubiquitous b-tree. \newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
-
-%\bibitem[Knu73]{Knuth-vol3}
-%D.~E. Knuth. \newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and Searching}. \newblock Addison-Wesley, 1973.
-%\end{thebibliography}
-
 \end{document}

### 2021-07-14 paper1.tex
Screenshts, intro and conclusion

@@
 \begin{abstract}
+Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
 We have extended the Markdown language to represent the connections between mathematical objects that exist across various sources of knowledge.
@@
 
+\subsubsection*{Background: The Sophize Platform}
+
 Sophize is a novel mathematics library and discussion platform.
-Our primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-Mathematical proofs can be seen as directed acyclic graphs of logical arguments that can extend across a large number of documents and databases.
-These proofs are carried out based on a variety of foundations such as ZFC, intuitionistic logic and type theory.
+The platform has been developed by the author over the course of last two years at \url{https://sophize.org}.
+Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
+We combine knowledge from multiple resources and have currently accumulated, thousands of definitions, theorems and proofs from a wide variety of sources including some published research, PlanetMath, Wikipedia, and the Metamath formal system.
+
+\subsubsection*{Proofs in Sophize}
+
+Mathematical proofs are based on a variety of foundations such as ZFC, intuitionistic logic and type theory.
 The arguments used in any proof are considered valid  or not based on criteria that can vary.
@@
 Proofs can also be algorithmically generated, and at the highest level of verification, they are represented and verified using a formal system.
-Thus, aggregating proofs from such a wide variety of sources that use a wide variety of foundations and verification criteria is a challenging problem that requires novel knowledge organization techniques and user interfaces.
-This article focuses on these user interfaces that help users to navigate and understand existing proofs and discover new ones.
-Our work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
-The committee on planning a global library of the mathematical sciences recognized that this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research\cite{sciences2014developing}.
-This introductory video gives an overview of how structured knowledge can help: \url{https://youtu.be/Wb1JbW9Otek}.
 
-In this paper, we first discuss the details of Sophize Markdown, an extension of the Markdown language.
-It is convenient enough to be used for a casual discussion of mathematical ideas over the web.
+Sophize organizes mathematical knowledge as a dense graph of propositions and logical arguments that is built by combining knowledge from a number of documents and other data sources.
+We use this graph and combine it with the set of foundations and verifications chosen by each user to create proofs tailored to their needs.
+This introductory video gives an overview of how a mathemtician would browse such proofs can help: \url{https://youtu.be/Wb1JbW9Otek}.
+
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=14cm]{proof_tree}}
+\caption{Proof shown as a graph of arguments and propositions on the Sophize platform.}
+\label{proof_tree}
+\end{center}
+\end{figure}
+
+This work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
+The committee on planning a global library of the mathematical sciences recognized that this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research \cite{sciences2014developing}.
+
+Hence, we required novel knowledge organization techniques that can connect mathematical entities from in such wide range of formal and informal knowledge sources.
+Thus, one of main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
+
+\subsubsection*{Mathematics collaborations}
+
+As a discussion platform, Sophize is focused on creating an interface that helps mathematicians discuss mathematics and collaboratively discover new proofs.
+The existing web platforms and technologies while useful, are of course not tailored for academic mathematical discussions.
+It becomes very challenging to organize discussions and participants struggle to keep up with the rapidly evolving ideas.
+In our current environment where in-person collaboration opportunities have drastically reduced this can prove to be quite beneficial.
+
+\subsubsection*{Contribution}
+
+In this paper, we present the features of Sophize Markdown, an extension of the Markdown language.
+It is convenient enough to be used for casual discussions of mathematical ideas over the web.
 It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from a wide variety of sources, including formal languages.
-Then, we elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
-The design focuses on making it easy for the participants to understand current progress even when many collaborators have posted a large number of comments.
-We studied the nature of collaboration on Polymath projects\cite{polymath_blog}, which are massively collaborative online mathematical projects, to develop our interface design.
-Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
-In fact, a large portion of the interface is designed specifically to overcome the issues noted by Timothy Gowers \cite{gowers_weblog_2009} and Terence Tao\cite{whats_new_2009}.
-We believe that these features will not only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like those organized by AiM.
+It thus plays an integral role in the two problems that we have mentioned above.
+
+We then elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
+The design focuses on making the collaboration more productive and enjoyable by building the right set of technical tools that aid in effective organization and summarization of existing progress.
+
+Section 3 presents Sophize markdown as a lightweight interface for represeting math content and Section 4 discusses its collaboration facilities. Section 5 concludes the paper.
+
+\subsection*{Acknowledgements}
+This publication resulted (in part) from research supported by the International Mathematical Union.
+We would like to thank Patrick Ion and Michael Kohlhase for helping us in organizing our ideas and structuring the content of the paper.
 
@@
 
+\subsection{Sophize's Datamodel}
 Before we describe the Sophize Markdown language, it will be necessary to briefly describe how we model mathematical entities.
-The data model is published in JSON schema\cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
+The data model is published in JSON schema \cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
 We describe relevant parts of the concepts used here.
 
-\subsection*{Resource}
+\subsubsection*{Resource}
 
-A resource is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments. Each resource has a URI and contains fields such as search tags and citations.
+A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+Each resource has a URI and contains fields such as search tags and citations.
 
@@
 For example, Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the 'wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
 
-\subsection*{Term}
+\subsubsection*{Term}
 
-A term is a clearly defined entity that can be used to make up a valid proposition.
+A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
 It can be a mathematical object, operator, symbol, entity, data structure, algorithm, or even a person.
@@
 
-\subsection*{Proposition}
+\subsubsection*{Proposition}
 
-A proposition is a grammatically valid statement that can be either true or false. Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.
+A \textbf{proposition} is a grammatically valid statement that can be either true or false.
+Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.
 
-\subsection*{Argument}
+\subsubsection*{Argument}
 
-An argument is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
+An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
 In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
 A proof is seen as a directed graph of arguments and propositions.
+
+\subsection{Polymath Projects}
+In order to better understand the nature of online collaborations, we studied the nature of collaboration on Polymath projects \cite{polymath_blog}, which are massively collaborative online mathematical projects.
+Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
+In fact, a large portion of the interface is designed specifically to overcome the issues noted by Timothy Gowers \cite{gowers_weblog_2009} and Terence Tao \cite{whats_new_2009}.
 
@@
 
-\paragraph{NAME (default)}
+\paragraph{\textbf{NAME} (default): This option fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.}
 
-Fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.
+\paragraph{\textbf{LOWER\_CASE (LC) or UPPER\_CASE (UC)}: These options become quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.}
 
-\paragraph{CUSTOM\_TEXT}
-Link text is supplied by the user.
+\paragraph{\textbf{Custom text}: A link can also explicitly specify the link text by enclosing it in single quotes.}
 
-\paragraph{LOWER\_CASE or UPPER\_CASE}
-
-Lower cases the link text. This becomes quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.
-
-\paragraph{Example}
-As noted earlier, dataset-id of URIs can often be available from the context. We assume that to be the case to make the examples easier to read.
-The following Markdown code shows the various link text options:
+The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and are thus not specified in the URIs.
 
@@
 
-\paragraph{OVERLAY\_LINK (default)}
+\paragraph{\textbf{OVERLAY\_LINK} (default): By default, clicking on links opens up a modal dialog with the resource's summary.}
 
-In the case of an overlay link, clicking on the link opens up a modal dialog to show a resource summary instead of navigating to another URL.
+\paragraph{\textbf{NAV\_LINK}: We can create a hyperlink to the resource's URL using the using NAV\_LINK option.}
 
-\paragraph{NAV\_LINK}
+\paragraph{\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element that whose hover text is the URI of the resource.}
 
-Clicking the link causes the browser to navigate to the web page indicated by the resource's URI.
-
-\paragraph{NO\_LINK}
-
-This is not a link but clicking or hovering on it brings up a text on the web browser indicating the URI.
-
-\paragraph{Example}
-The following Markdown code has all three link types:
+For example, the following Markdown code has all three link types:
 \begin{verbatim}
@@
 \end{mdframed}
-The first `link' shows `\#wiki/T\_matrix\_multiplication' on mouse-hover. The second link navigates the page to a different URL. Clicking on the third link shows a modal dialog box like so:
+The first element shows `\#wiki/T\_matrix\_multiplication' on mouse-hover. The second link navigates the page to a different URL. Clicking on the third link pops up a modal dialog box like so:
 
@@
 \caption{Modal dialog box for the term binary operation. These boxes can also have content that uses all three types of links. }
-\label{fig1}
+\label{modal}
 \end{center}
@@
 For arguments, the premises, conclusion, and the argument text is added in place.
-Another option `ARG\_TEXT\_ONLY' can be used for to dislay only the argument text.
+Another option `ARG\_TEXT\_ONLY' can be used for to display only the argument text.
 
-\paragraph{Example}
 The following is a sample article where we uses re-use concepts and theorems already extracted from multiple sources (say, Wikipedia and the Oxford dictionary):
@@
 For propositions, a Truth Value Icon indicating whether or not there is a proof is added next to the link.
-Clicking on the icon brings up the proof as a graph of arguments.
+Clicking on the icon brings up the proof graph as shown in figure \ref{proof_tree}.
 Similarly, an icon is added next to an argument which indicates whether the argument is valid or not.
-These options can be turned on or off depending on the user input and the context.
+These options can be turned on or off depending on the input and the context.
 Further details require details of the Sophize knowledge organization scheme which is not our focus here.
@@
 
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=3cm]{formal}}
+\caption{The prime number theorem written in Metamath language and rendered as Markdown in real time.}
+\label{formal}
+\end{center}
+\end{figure}
+
 \subsection{\LaTeX\space Support}
@@
 However, Pandoc is the most widely used tool for converting \LaTeX\space to Markdown, and its specification is well documented and tested.
-Thus, we use their specification for our extension\cite{pandoc}:
+Thus, we use their specification for our extension \cite{pandoc}:
 
@@
 happiness is that fetched $1.3 million recently. While it may not fetch many \$s, I 
-like the field equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
+like the field equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
 \end{verbatim}
@@
 what fetched \$1.3 million recently. While it may not fetch many \$s, I like the field
-equations more $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
+equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
 \end{mdframed}
 
-\section{Sophize Collaboration Interface}
+\section{Sophize Collaboration}
 
@@
 We believe that we have created a novel interface that can significantly mitigate this problem.
-The work is primarily influenced by recommendations made by Timothy Gowers and Terence Tao after organizing several Polymath projects\cite{polymath_blog}.
+The work is primarily influenced by recommendations made by Timothy Gowers and Terence Tao after organizing several Polymath projects \cite{polymath_blog}.
 We believe that the interface can aid many collaboration types - with few or many participants.
 We demonstrate the various features of this interface by incorporating actual data from a Polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
+
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=14cm]{collab}}
+\caption{Some elements of the Sophize Collaboration Interface.}
+\label{collab}
+\end{center}
+\end{figure}
 
@@
 
-Other technical requirements were discussed by some project participants and summarized by Tao on his blog\cite{whats_new_2009} (lightly edited):
+Other technical requirements were discussed by some project participants and summarized by Tao on his blog \cite{whats_new_2009} (lightly edited):
 
@@
 By marking such threads as `hidden', moderators can ensure that these are not shown by default.
-But any user can view them if they wish to.
+But any user can view them when required.
 
-\subsubsection*{Sources}
+\section{Conclusion and Future Work}
+
+We have presented Sophize Markdown, a lightweight language for representing mathematical knowledge on the web.
+Using this language, we can easily embed mathematical entities like definitions, theorems and proofs, making it very convenient to search and browse the content.
+While there are other ways to represent semantic knowledge such as content MathML and OpenMath, their scope is somewhat limited to specifying meaning of mathematical formula.
+The sTeX system \cite{Kohlhase2008} is perhaps most similar to Sophize Markdown but it needs creation of \LaTeX\space documents and use of \LaTeX ML systems.
+This makes it quite challenging to use in real-time web workflows that the Sophize platform.
+
+We utilized the Sophize Markdown language to create an innovative mathematics communication interface.
+It specially designed to aid online mathematics collaborations and can help actualize their vast latent potential.
+We believe that it can only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like those organized by AiM.
+
+In the future, we want to make a substantial portion of math literature embedded with structured data available at a much greater scale.
+Thus, we will improve Sophize Markdown's support for \LaTeX\space features like equation numbering, tables, and references.
+In addition, we are developing an online tool to easily extract content like definitions, theorems, proofs from math literature by automating some of the tedious tasks.
+This process will be aided by the supervised learning techniques \cite{ginev2019scientific} for classification scientific statements.
+
+\subsection*{Sources}
 The Sophize Markdown parser and its Angular renderer source code are available under an MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
 The NPM packages for these projects are named `sophize-md-parser' and `ngx-sophize-md-renderer'.
-
-\subsubsection*{Acknowledgements}
-This publication resulted (in part) from research supported by the International Mathematical Union.
-We would like to thank Patrick Ion for encouraging us to publish our work and also for their help in organizing the content of the paper.
 

### 2021-07-14 paper1.tex
Changes before the final read

@@
 We have extended the Markdown language to represent the connections between mathematical objects that exist across various sources of knowledge.
-Using the new language, we demonstrated an interactive interface that helps its users explore mathematics content on the web.
+Using the new language, we demonstrated an interactive interface that helps users explore mathematics content on the web.
 We also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
@@
 Sophize is a novel mathematics library and discussion platform.
-The platform has been developed by the author over the course of last two years at \url{https://sophize.org}.
+The author has developed the platform over the course of the last two years at \url{https://sophize.org}.
 Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-We combine knowledge from multiple resources and have currently accumulated, thousands of definitions, theorems and proofs from a wide variety of sources including some published research, PlanetMath, Wikipedia, and the Metamath formal system.
+We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
 
@@
 
-Mathematical proofs are based on a variety of foundations such as ZFC, intuitionistic logic and type theory.
+Mathematical proofs are based on a variety of foundations such as ZFC, intuitionistic logic, and type theory.
 The arguments used in any proof are considered valid or not based on criteria that can vary.
@@
 
-Sophize organizes mathematical knowledge as a dense graph of propositions and logical arguments that is built by combining knowledge from a number of documents and other data sources.
+Sophize combines such an expansive range of proofs into a dense graph of propositions and logical arguments that aggregates knowledge from a several documents and other data sources.
 We use this graph and combine it with the set of foundations and verifications chosen by each user to create proofs tailored to their needs.
-This introductory video gives an overview of how a mathemtician would browse such proofs can help: \url{https://youtu.be/Wb1JbW9Otek}.
+This introductory video gives an overview of the platform's offerings: \url{https://youtu.be/Wb1JbW9Otek}.
 
@@
 \begin{center}
-\fbox{\includegraphics[height=14cm]{proof_tree}}
-\caption{Proof shown as a graph of arguments and propositions on the Sophize platform.}
+\fbox{\includegraphics[height=12cm]{proof_tree}}
+\caption{A proof displayed as a graph (tree) of arguments and propositions on the Sophize platform.}
 \label{proof_tree}
@@
 
-Hence, we required novel knowledge organization techniques that can connect mathematical entities from in such wide range of formal and informal knowledge sources.
-Thus, one of main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
+Hence, we required novel knowledge organization techniques to connect mathematical entities from such a wide range of formal and informal knowledge sources.
+And thus, one of the main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
+This is the primary problem that this work addresses.
 
@@
 
-As a discussion platform, Sophize is focused on creating an interface that helps mathematicians discuss mathematics and collaboratively discover new proofs.
-The existing web platforms and technologies while useful, are of course not tailored for academic mathematical discussions.
-It becomes very challenging to organize discussions and participants struggle to keep up with the rapidly evolving ideas.
-In our current environment where in-person collaboration opportunities have drastically reduced this can prove to be quite beneficial.
+As a discussion platform, Sophize focuses on creating an interface that helps mathematicians discuss mathematics and collaboratively discover new proofs.
+The existing web platforms and technologies, while useful, are, of course, not tailored for academic mathematical discussions.
+It becomes very challenging to organize discussions, and participants struggle to keep up with the rapidly evolving ideas.
+In our current environment, where in-person collaboration opportunities have drastically reduced, aiding mathematicians to work together online can prove to be quite beneficial.
 
@@
 It is convenient enough to be used for casual discussions of mathematical ideas over the web.
-It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from a wide variety of sources, including formal languages.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from various sources, including formal systems.
 It thus plays an integral role in the two problems that we have mentioned above.
@@
 
-Section 3 presents Sophize markdown as a lightweight interface for represeting math content and Section 4 discusses its collaboration facilities. Section 5 concludes the paper.
+Section 3 presents Sophize markdown as a lightweight interface for representing math content, and Section 4 discusses its collaboration facilities. Finally, Section 5 concludes the paper.
 
@@
 \subsection{Sophize's Datamodel}
-Before we describe the Sophize Markdown language, it will be necessary to briefly describe how we model mathematical entities.
+Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
 The data model is published in JSON schema \cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
@@
 
-A URI consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that indicates what kind of resource it is along with its unique name in the data source.
+A URI consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
 The dataset-id may be omitted if it can be inferred from the surrounding context.
 
-For example, Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
+For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
 When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
@@
 A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
-It can be a mathematical object, operator, symbol, entity, data structure, algorithm, or even a person.
+It can be a mathematical object, operator, symbol, data structure, algorithm, or even a person.
 `Meaningless' primitives in formal theories are also categorized as terms.
@@
 \subsection{Polymath Projects}
-In order to better understand the nature of online collaborations, we studied the nature of collaboration on Polymath projects \cite{polymath_blog}, which are massively collaborative online mathematical projects.
-Conveniently, the leaders have publically analyzed these projects and suggested technical improvements suitable for such collaborations.
+In order to better understand the nature of online collaborations, we studied the Polymath projects \cite{polymath_blog}, which are massively collaborative online mathematical projects.
+Conveniently, the project leaders publically analyzed these projects and suggested technical improvements suitable for such collaborations.
 In fact, a large portion of the interface is designed specifically to overcome the issues noted by Timothy Gowers \cite{gowers_weblog_2009} and Terence Tao \cite{whats_new_2009}.
@@
 One can choose from several slightly varying Markdown specifications.
-We start with the widely supported CommonMark specification and create extensions that we need.
+We start with the widely supported CommonMark specification and create extensions for the features that we need.
 The extensions are implemented using the `markdown-it' \cite{markdown_it} JavaScript parser.
@@
 A separate renderer module utilizes the AST tree to create the appropriate HTML or Single Page Application (SPA) libraries.
-Many of the features described here are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}
+Many of the features of Sophize Markdown are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}
 
@@
 
-This extension allows easily adding links to resources such as terms, propositions, and arguments. Links can be added using the resource's URI, and the following formats are supported:
+With Sophize Markdown we can easily embed resources such as terms, propositions, and arguments. Links can be added using the resource's URI, and the following formats are supported:
 
@@
 
-	\item \#URI[ $\vert$ OPTIONS]
+	\item \#URI[ $\vert$ OPTIONS ]
 
@@
 
-	\item \#(URI, [\textquotesingle LINK\_TEXT\textquotesingle][ $\vert$ OPTIONS])
+	\item \#(URI, \textquotesingle Custom\ Text\textquotesingle [ $\vert$ OPTIONS ])
 
-	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_greens\_lemma, EXPAND)
+	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_green\_tao\_theorem, 'Green–Tao Theorem'$\vert$NAV\_LINK)
 
@@
 These are required to make it convenient for the content creators to provide a rich experience to their readers.
-Some of the commonly used one are summarized below.
+Some of the commonly used options are summarized below.
 
@@
 \begin{verbatim}
-#T_matrix_multiplication|NO_LINK|UC is a #(T_commutative_property, 
+#T_matrix_multiplication|NO_LINK is a #(T_commutative_property, 
 'non-commutative'|NAV_LINK) #T_binary_operation.
@@
 For terms and propositions, the definition and the statement are added in place, respectively.
-For arguments, the premises, conclusion, and the argument text is added in place.
-Another option `ARG\_TEXT\_ONLY' can be used for to display only the argument text.
+For arguments, its premises, conclusion, and the argument text is added.
 
@@
 #oxford/T_parabola|EXPAND The area of a parabola is unbounded.
-
 ...
-
 \end{verbatim}
@@
 These options can be turned on or off depending on the input and the context.
-Further details require details of the Sophize knowledge organization scheme which is not our focus here.
+Further details require an in-depth understanding of the Sophize knowledge organization scheme which is not our focus here.
 
@@
 We can convert the externally parsed output into Markdown in such a case, where each term is automatically linked to the appropriate resource.
-This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to explore all concepts than make up the input statement in depth.
+This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to explore all concepts that make up the input statement in depth.
 Currently, this is demonstrated in the use of Sophize Markdown with the Metamath language.
@@
 
-Assuming the terms and propositions are referenced are available, the above Markdown code is rendered as:
+The above Markdown code is rendered as:
 \begin{mdframed}
@@
 As noted by Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
-The `proof discovery tree', as Gowers calls it \cite{gowers_weblog_2009}, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
+The `proof discovery tree', as described by Gowers \cite{gowers_weblog_2009}, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
 The leaves of the tree would thus be sub-problems that get solved without division into sub-problems.
@@
 We have presented Sophize Markdown, a lightweight language for representing mathematical knowledge on the web.
-Using this language, we can easily embed mathematical entities like definitions, theorems and proofs, making it very convenient to search and browse the content.
-While there are other ways to represent semantic knowledge such as content MathML and OpenMath, their scope is somewhat limited to specifying meaning of mathematical formula.
+Using this language, we can easily embed mathematical entities like definitions, theorems, and proofs, making it very convenient to find and browse relevant content.
+Sophize Markdown plays a central role in organizing proofs from various data sources on the Sophize platform.
+While there are other ways to represent semantic knowledge, such as content MathML and OpenMath, their scope is somewhat limited to specifying the meaning of the mathematical formula.
 The sTeX system \cite{Kohlhase2008} is perhaps most similar to Sophize Markdown but it needs creation of \LaTeX\space documents and use of \LaTeX ML systems.
-This makes it quite challenging to use in real-time web workflows that the Sophize platform.
+This makes its use in real-time web workflows impractical.
 
 We utilized the Sophize Markdown language to create an innovative mathematics communication interface.
-It specially designed to aid online mathematics collaborations and can help actualize their vast latent potential.
-We believe that it can only aid large-scale collaborations like Polymath but will also be useful for private collaborations and workshops like those organized by AiM.
+It is specially designed to aid online mathematics collaborations and can help actualize their vast latent potential.
+We believe that it can not only aid large-scale collaborations like the Polymath projects but will also be useful for private collaborations and workshops like those organized by AiM.
 
@@
 In addition, we are developing an online tool to easily extract content like definitions, theorems, proofs from math literature by automating some of the tedious tasks.
-This process will be aided by the supervised learning techniques \cite{ginev2019scientific} for classification scientific statements.
+This process will be aided by the recent supervised learning techniques \cite{ginev2019scientific} that classify scientific statements in literature.
 

### 2021-07-14 sophize_md.tex
Submitted version

--- 2021-07-14 paper1.tex
@@
 This publication resulted (in part) from research supported by the International Mathematical Union.
-We would like to thank Patrick Ion and Michael Kohlhase for helping us in organizing our ideas and structuring the content of the paper.
+The author would like to thank Patrick Ion and Michael Kohlhase for help in organizing our ideas and structuring the content of the paper.
 
@@
 
-The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and are thus not specified in the URIs.
+The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and thus not specified in the URIs.
 
@@
 
-\paragraph{\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element that whose hover text is the URI of the resource.}
+\paragraph{\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element whose hover text is the URI of the resource.}
 
@@
 
-The following is a sample article where we uses re-use concepts and theorems already extracted from multiple sources (say, Wikipedia and the Oxford dictionary):
+The following is a sample article where we re-use concepts and theorems already extracted from multiple sources (say, Wikipedia and the Oxford dictionary):
 
@@
 We can convert the externally parsed output into Markdown in such a case, where each term is automatically linked to the appropriate resource.
-This provides a delightful interface, where the user types in the native language, and the final output automatically allows users to explore all concepts that make up the input statement in depth.
+This provides a convenient interface, where the user types in the native language, and the final output automatically allows users to explore all concepts that make up the input statement in depth.
 Currently, this is demonstrated in the use of Sophize Markdown with the Metamath language.
@@
 Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of 
-happiness is that fetched $1.3 million recently. While it may not fetch many \$s, I 
+happiness is what fetched $1.3 million recently. While it may not fetch many \$s, I 
 like the field equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$

### 2021-07-25 sophize_md.tex
Update based on reviewer comments

@@
 We have extended the Markdown language to represent the connections between mathematical objects that exist across various sources of knowledge.
-Using the new language, we demonstrated an interactive interface that helps users explore mathematics content on the web.
+Using the new language, we showcase an interactive interface that helps users explore mathematics content on the web.
 We also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
@@
 
-Sophize combines such an expansive range of proofs into a dense graph of propositions and logical arguments that aggregates knowledge from a several documents and other data sources.
+Sophize combines such an expansive range of proofs into a dense graph of propositions and logical arguments that aggregates knowledge from several documents and other data sources.
 We use this graph and combine it with the set of foundations and verifications chosen by each user to create proofs tailored to their needs.
@@
 It becomes very challenging to organize discussions, and participants struggle to keep up with the rapidly evolving ideas.
-In our current environment, where in-person collaboration opportunities have drastically reduced, aiding mathematicians to work together online can prove to be quite beneficial.
+In our current environment, where in-person collaboration opportunities have drastically reduced due to the ongoing COVID-19 pandemic, aiding mathematicians to work together online can prove to be quite beneficial.
 
@@
 
-Section 3 presents Sophize markdown as a lightweight interface for representing math content, and Section 4 discusses its collaboration facilities. Finally, Section 5 concludes the paper.
+Section 3 presents Sophize Markdown as a lightweight interface for representing math content, and Section 4 discusses its collaboration facilities. Finally, Section 5 concludes the paper.
 
@@
 
-\subsection{Sophize's Datamodel}
-Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
+\subsection{Sophize's Data Model}
+\paragraph{Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
 The data model is published in JSON schema \cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
-We describe relevant parts of the concepts used here.
+We describe relevant parts of the concepts used here.}
 
-\subsubsection*{Resource}
+\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+Each resource has a URI and contains fields such as search tags and citations.}
 
-A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
-Each resource has a URI and contains fields such as search tags and citations.
-
-A URI consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
+A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
 The dataset-id may be omitted if it can be inferred from the surrounding context.
@@
 
-\subsubsection*{Term}
+\paragraph{A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
+It can be a mathematical object, operator, symbol, data structure, algorithm, or even a person.
+`Meaningless' primitives in formal theories are also categorized as terms.}
 
-A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
-It can be a mathematical object, operator, symbol, data structure, algorithm, or even a person.
-`Meaningless' primitives in formal theories are also categorized as terms.
+\paragraph{A \textbf{proposition} is a grammatically valid statement that can be either true or false.
+Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.}
 
-\subsubsection*{Proposition}
-
-A \textbf{proposition} is a grammatically valid statement that can be either true or false.
-Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.
-
-\subsubsection*{Argument}
-
-An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
+\paragraph{An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
 In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
-A proof is seen as a directed graph of arguments and propositions.
+A proof is seen as a directed graph of arguments and propositions.}
 
@@
 For propositions, a Truth Value Icon indicating whether or not there is a proof is added next to the link.
-Clicking on the icon brings up the proof graph as shown in figure \ref{proof_tree}.
+Clicking on the icon brings up the proof graph as shown in Figure \ref{proof_tree}.
 Similarly, an icon is added next to an argument which indicates whether the argument is valid or not.

### 2021-10-06 math_library/sophize_math.tex
Initial commit

--- 2021-07-25 sophize_md.tex
@@
 
+\graphicspath {{../res}}
+
 \institution{ Sophize Foundation\\ Bengaluru, India \\ abc@sophize.org }
@@
 Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
-We have extended the Markdown language to represent the connections between mathematical objects that exist across various sources of knowledge.
-Using the new language, we showcase an interactive interface that helps users explore mathematics content on the web.
-We also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
-This contribution sketches the basic ideas and provides links to some demos of the new functionality.
+We present a Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
+With this knowledge organization scheme at its core, we have engineered that platform to aggregate knowledge from sources.
+The platform meaningfully combines knowledge from published research, encyclopedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
+To make this happen, two developments were necessary.
+First, we developed an open plugin architecture that allows proofs from computer programs to be generated as required.
+Second, we extended the Markdown language to represent the connections between between mathematical objects found across various sources of knowledge.
+In addition, we also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
 
@@
 
-\section{Preliminaries}
+\section{Sophize's Knowledge Organization Scheme}
 

### 2021-10-17 math_library/sophize_math.tex
changes

@@
 We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+
+- The goal is rational truth. Three dimensions are consistency, correspondence and values.
+
+- In its current iteration, Sophize can modekl vast mnajority (almost all)  of mathematics.
 
@@
 \section{Sophize's Knowledge Organization Scheme}
+For math logical consistency is the sole criteria for truth..
+Thus, as a math library, Sophize models mathematical knowledge using logical arguments.
 
-\subsection{Sophize's Data Model}
-\paragraph{Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
-The data model is published in JSON schema \cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
-We describe relevant parts of the concepts used here.}
-
-\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
-Each resource has a URI and contains fields such as search tags and citations.}
-
-A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
-The dataset-id may be omitted if it can be inferred from the surrounding context.
-
-For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+The various concepts used for orgnizing knowledge logically are described below.
+These concepts have been modelled in JSON schema \cite{sophize_datamodel} and published for popular programming language such as Java (MVN), Javascript (npm) and Python (PyPI).
 
@@
 
-\subsection{Polymath Projects}
-In order to better understand the nature of online collaborations, we studied the Polymath projects \cite{polymath_blog}, which are massively collaborative online mathematical projects.
-Conveniently, the project leaders publically analyzed these projects and suggested technical improvements suitable for such collaborations.
-In fact, a large portion of the interface is designed specifically to overcome the issues noted by Timothy Gowers \cite{gowers_weblog_2009} and Terence Tao \cite{whats_new_2009}.
+\paragraph{While modelling the concepts an abstract concept for ease of implementation.
+A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+Each resource has a URI and contains fields such as search tags and citations.}
+
+A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
+The dataset-id may be omitted if it can be inferred from the surrounding context.
+
+For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
+When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+
+The same URI scheme will be used in this paper to refer to various terms, propositions, arguments, etc.
+
+There are a couple more concepts that we will describe at later in the paper.
+
+\subsection{Belief sets}
+
+In Sophize, a proposition is claimed to be true if it is concluded by a valid argument and the premises of the argument are also true.
+
+Of course this means that we need to start with some propositions that are assumed to be true.
+Traditionally, these are mathematical axioms and are considered to true because they are self-evident.
+However, there is no criteria to define if a propositions if self-evidently true.
+In mathematical inquiry, theorems are proven/disproven in one or more multiple theories, each with its own set of axioms.
+Each theory may have its theoretical advantages and practical uses and there are no criteria to choose one theory over another when trying to assert a proposition's truth/falsity.
+
+Thus, Sophize allows any set of propositions to be considered true without evidence.
+Such a set of propositions is called a belief set.
+Thus, the truth-value of a proposition is only defined within a belief set - it doesn't have any concept of universal truth.
+
+The same argument may be utilized by multiple belief sets to compute truth values.
+
+Computing of truth values in a belief set is thus a simple recursive graph algorithm. Sophize computes truth values for all its belief sets.
+
+\subsection{Validity of arguments}
+Validity of an argument is, in principle, objectively verifiable. A formally defined logistic systems have a mechanical procedure to verify validity arguments.
+
+However, mathematics only utilizes a tiny portion formally verifiable arguments. Most mathematics is verifies via peer review, some with curated by experts.
+
+\subsection{Tracking Inconsistency}
+If a propositions and its negation is proved within a belief set is inconsistent.
+As proved by the principle of explosion, any propositions can be proved from such a contradiction.
+Thus making the claim of truth of any proposition practically worthless.
+
+Thus it is important to track and report contradictions in a belief set.
+Thus Sophize has a semantic notion of negation of a proposition.
+The premises or conclusion of an argument can be negation of propositions.
+
+When a proposition and its negation are proven, the system reports such contradictions for every belief set.
 

### 2021-10-21 math_library/sophize_math.tex
Update sophize_math.tex

@@
 \usepackage[normalem]{ulem}
+
+\newcommand\todo[1]{\textcolor{red}{TODO: #1}}
 
@@
 
-\section{Introduction}
+\section{Introduction [FROM CICM]}
 
@@
 
-- The goal is rational truth. Three dimensions are consistency, correspondence and values.
+\todo{- The goal is rational truth. Three dimensions are consistency, correspondence and values.}
 
-- In its current iteration, Sophize can modekl vast mnajority (almost all)  of mathematics.
+\todo{- In its current iteration, Sophize can model vast majority (almost all)  of mathematics.}
 
@@
 And thus, one of the main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
-This is the primary problem that this work addresses.
-
-\subsubsection*{Mathematics collaborations}
-
-As a discussion platform, Sophize focuses on creating an interface that helps mathematicians discuss mathematics and collaboratively discover new proofs.
-The existing web platforms and technologies, while useful, are, of course, not tailored for academic mathematical discussions.
-It becomes very challenging to organize discussions, and participants struggle to keep up with the rapidly evolving ideas.
-In our current environment, where in-person collaboration opportunities have drastically reduced due to the ongoing COVID-19 pandemic, aiding mathematicians to work together online can prove to be quite beneficial.
+\todo{Explain and summarize the problem statement}
 
 \subsubsection*{Contribution}
-
-In this paper, we present the features of Sophize Markdown, an extension of the Markdown language.
-It is convenient enough to be used for casual discussions of mathematical ideas over the web.
-It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from various sources, including formal systems.
-It thus plays an integral role in the two problems that we have mentioned above.
-
-We then elaborate on the communication interface designed to help mathematicians discuss mathematics and collaboratively discover new proofs.
-The design focuses on making the collaboration more productive and enjoyable by building the right set of technical tools that aid in effective organization and summarization of existing progress.
-
-Section 3 presents Sophize Markdown as a lightweight interface for representing math content, and Section 4 discusses its collaboration facilities. Finally, Section 5 concludes the paper.
+\todo{summarize sections. section 3 does X, section 4 does Y etc.}
 
@@
 \section{Sophize's Knowledge Organization Scheme}
-For math logical consistency is the sole criteria for truth..
-Thus, as a math library, Sophize models mathematical knowledge using logical arguments.
+For math, logical consistency is the sole criteria for truth. Thus, as a math library, Sophize models mathematical knowledge using logical arguments.
 
-The various concepts used for orgnizing knowledge logically are described below.
+The various concepts used for organizing knowledge logically are described below.
 These concepts have been modelled in JSON schema \cite{sophize_datamodel} and published for popular programming language such as Java (MVN), Javascript (npm) and Python (PyPI).
@@
 
-\paragraph{While modelling the concepts an abstract concept for ease of implementation.
-A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
 Each resource has a URI and contains fields such as search tags and citations.}
@@
 
+\subsection{Validity of arguments}
+Validity of an argument is, in principle, objectively verifiable. A formally defined logistic systems have a mechanical procedure to verify validity arguments.
+
+However, mathematics only utilizes a tiny portion formally verifiable arguments.
+Most mathematics is verified via peer review, some of this knowledge is curated by experts in books, encyclopaedias.
+The claim of validity of proofs (arguments) is judged based on the various parameters such as academic standing of the claimant, reputation of the peer reviewing journal, the history of errors of the book or encyclopedia containing them, etc.
+Clearly, this criteria is subjective and can vary to some extent for each individual.
+
+Sophize doesn't promote or endorse and such criteria.
+Instead, it allows its users to choose the criteria they believe in.
+A validity criteria is modelled as a proposition and each argument has one such validity criteria associated with it.
+
+Some sample validity criteria:
+1. Formally verified using 3 independent COQ verifiers.
+2. Peer reviewed by XYZ journal
+3. Published on Wikipedia.
+4. Claimed by someone.
+
+For easily managing validity criteria, the relationships between validity criteria are also maintained using arguments.
+Eg. published in journal with score more than 0.67 $\rightarrow$ published in Annals of Mathematics
+
+\todo{Q. Who has the time to setup belief sets? How does Sophize make it 
+convenient.}
+
 \subsection{Belief sets}
@@
 
-Of course this means that we need to start with some propositions that are assumed to be true.
-Traditionally, these are mathematical axioms and are considered to true because they are self-evident.
-However, there is no criteria to define if a propositions if self-evidently true.
+Of course, this means that we need to start with some propositions that are assumed to be true without further justification.
+Traditionally, these are mathematical axioms and are considered to self-evidently true.
+However, there is no clear criteria to claim if a propositions is self-evidently true.
 In mathematical inquiry, theorems are proven/disproven in one or more multiple theories, each with its own set of axioms.
@@
 Such a set of propositions is called a belief set.
-Thus, the truth-value of a proposition is only defined within a belief set - it doesn't have any concept of universal truth.
+Thus, the truth-value of a proposition is only defined within a belief set - there is no notion of of absolute or universal truth.
 
-The same argument may be utilized by multiple belief sets to compute truth values.
+Propositions representing argument validity criteria are also part of belief sets. All propositions that are considered to be true in a belief set without proof are called `unsupported propositions'.
 
-Computing of truth values in a belief set is thus a simple recursive graph algorithm. Sophize computes truth values for all its belief sets.
-
-\subsection{Validity of arguments}
-Validity of an argument is, in principle, objectively verifiable. A formally defined logistic systems have a mechanical procedure to verify validity arguments.
-
-However, mathematics only utilizes a tiny portion formally verifiable arguments. Most mathematics is verifies via peer review, some with curated by experts.
+Computing of truth values in a belief set is thus a simple recursive graph algorithm as explained in the section below. Sophize computes truth values for all its belief sets.
 
@@
 If a propositions and its negation is proved within a belief set is inconsistent.
-As proved by the principle of explosion, any propositions can be proved from such a contradiction.
+Due to principle of explosion, any propositions can be proved from such a contradiction.
 Thus making the claim of truth of any proposition practically worthless.
@@
 
-\section{Sophize Markdown}
+\subsection{Argument Graph}
+A proposition is considered true if it is claimed by a sound argument.
+An argument is considered sound if it is valid and its premises are true.
+Also, as explained in the section above, the validity criteria of an argument is modelled as just another premise.
+Thus, the relationship between all propositions and arguments can be represented with a simple graph.
+The following figure shows the different types of nodes and edges in such a graph
+
+1. Nodes - propositions and arguments
+2. Edges - premise to argument and argument to conclusion
+
+\subsection{Truth value computation}
+
+Using the argument graph, we can find truth values of every proposition in a belief set.
+Starting with the unsupported proposition of the belief set, computing truth values can be done using a simple recursive algorithm.
+The output of this algorithm is another graph, that we call proof graph, that has a proof for all the propositions it contains.
+For each proposition, a proof in the form of DAG of arguments (starting with unsupported propositions) can be trivially extracted from this proof graph.
+
+Note that an argument graph combines with different belief sets to generate different proof graphs. The same argument may be utilized in multiple belief sets.
+
+\todo{alternate arguments, proofs for same proposition}
+
+\subsection{Translations}
+\todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
+
+There is no good way to claim equivalency of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
+
+Eg. ZFC (informal) + ZFC (metamath) + Jensen's Inequality (metamath) + validity criteria (translation feels right to metamath group) $\rightarrow$ 
+Jensen's Inequality (informal)
+
+But, can represent translations manually using arguments.
+Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
+Again, a user can choose not to accept this criteria in which case, these translations will not be used in the generating proof graphs.
+
+Thus we can create proof graphs that have arguments from different languages.
+
+\subsection{Uses}
+Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
+
+Conjectural knowledge (Reimann hypothesis). 
+Practical utility of conjectural knowledge - eg. a lot of infromation security systems assume  P not NP)
+
+\subsubsection{Other Notes}
+\todo{How much math can be represented and Sophize's limitations. Eg. three valued logic}
+
+\section{Proof Generating Automata}
+A lot of mathematical knowledge is computed. Computations can be seen as algorithms that finding propositions based on some input.
+
+The computation 15+16 results in the value 31. We see this as
+
+\section{Other Engineering challenges}
+\todo{copyright/access management}
+\todo{efficient computation and storage of proof graphs}
+\todo{reading from disk }
+
+\section{Sophize Markdown[FROM CICM]}
 
@@
 
-\section{Sophize Collaboration}
+\section{Sophize Collaboration [From CICM]}
 

### 2021-10-22 math_library/sophize_math.tex
outline sent to Patrick

@@
 \begin{abstract}
-Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
+[FROM CICM] Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
 We present a Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
@@
 
-\section{Introduction [FROM CICM]}
+\section{Introduction}
 
@@
 
+- The goal is rational truth. Three dimensions are consistency, correspondence and values.
+
+- No hidden assumptions. Should have clear answer to every question of the form `why do you believe X'.
+
+- In its current iteration, Sophize implements consistency. Knowledge represented by manually and automated generation of arguments. Can model vast majority (almost all) of mathematics.
+
+- This gives you a way to create (consistency enforced) models.
+Next step is to see how accurately these models represent (parts of) the World.
+That involves quantifying correspondence of observations with the predictions made by the theories.
+
+- And finally, you need model individual, institutional, and societal values to claim the truth of `ought statements' like `I should wear a mask' or `Masks should be mandated'.
+
+- These starting beliefs (axioms, principles, laws, assumptions) and values are a way to model our belief systems. There are no absolutes, each belief system results in a different rational truth.
+
+\subsubsection*{Proofs in Sophize  [FROM CICM]}
 Sophize is a novel mathematics library and discussion platform.
@@
 We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
-
-\todo{- The goal is rational truth. Three dimensions are consistency, correspondence and values.}
-
-\todo{- In its current iteration, Sophize can model vast majority (almost all)  of mathematics.}
-
-\subsubsection*{Proofs in Sophize}
 
@@
 
-\subsection*{Acknowledgements}
+\subsection*{Acknowledgements [FROM CICM]}
 This publication resulted (in part) from research supported by the International Mathematical Union.
@@
 
+\subsection{Core concepts [FROM CICM]}
 The various concepts used for organizing knowledge logically are described below.
@@
 
-Sophize doesn't promote or endorse and such criteria.
+Sophize doesn't promote or endorse any criteria.
 Instead, it allows its users to choose the criteria they believe in.
@@
 1. Formally verified using 3 independent COQ verifiers.
+
 2. Peer reviewed by XYZ journal
+
 3. Published on Wikipedia.
+
 4. Claimed by someone.
 
-For easily managing validity criteria, the relationships between validity criteria are also maintained using arguments.
+For easily managing validity criteria, the relationships between validity criteria are also maintained using argument like dependency graphs.
+
 Eg. published in journal with score more than 0.67 $\rightarrow$ published in Annals of Mathematics
@@
 
-In Sophize, a proposition is claimed to be true if it is concluded by a valid argument and the premises of the argument are also true.
+In Sophize, a proposition is true if it is concluded by a valid argument and the premises of the argument are also true.
 
@@
 1. Nodes - propositions and arguments
+
 2. Edges - premise to argument and argument to conclusion
@@
 
-There is no good way to claim equivalency of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
+There is no good way to claim equivalence of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
 
@@
 \subsubsection{Other Notes}
-\todo{How much math can be represented and Sophize's limitations. Eg. three valued logic}
+\todo{What criteria are met based on the 2013 report}
 
-\section{Proof Generating Automata}
-A lot of mathematical knowledge is computed. Computations can be seen as algorithms that finding propositions based on some input.
+\todo{How much math can be represented. Eg. three valued logic}
 
-The computation 15+16 results in the value 31. We see this as
+\todo{Sophize's limitations. In "Potential Value of a
+Digital Mathematics Library" in 2013 report.
+Sophize offers no way to more easily find analogies or weaker forms of reasoning like “If A is true, then B is true.
+B is true; therefore, A becomes more plausible.” }
+
+\section{Proof Generating Automata (PGA)}
+A lot of mathematical knowledge is computed. Computation machines (calulators, algebras) can be seen as performing the following tasks: 
+1. parsing the input into a language that can represent math formulae. 
+2. Finding and outputting an equivalent form of the formula.
+
+Thus, their focus is not on finding the proof but only finding the equivalent (simplified) representation of the input formula. (Although many computer algebras do show the steps of the computation.)
+
+With Sophize, the focus instead is to generate proofs of the input propositions. However, Sophize machines can also have the capability to perform tasks 1 and 2, mentioned above.
+
+\subsection{'Active' PGA}
+As with other parts of Sophize, the output of an PGA is not taken for granted.
+Each automata specifies the premises (assumptions) that it uses to generate its proof.
+In addition, an automata may also delegate parts of proofs to another automata.
+These automata must also be specified.
+
+An automata is considered 'active' in a belief set if:
+1) all of its premises are true
+2) all the automata it delegates-to are active.
+
+As with an argument, one or more premises is used to indicate the validity of the automata (Eg.
+tested by X, verified by some committee, another program etc).
+Thus, to be considered active in a belief set, the PGA must have a verification criteria that matches the belief set's requirements.
+
+\subsection{PGA response}
+A PGA receives as a proposition as an input. The output of a PGA has the following components:
+1. Truth value of the proposition.
+2. The proof of the propositions (or its negation) as a DAG of arguments generated by the PGA.
+
+Note that unlike other propositions, arguments on Sophzie these are not stored on disk but do have a temporary URI specified in a slightly different format.
+The leaves of the DAG can have two kinds of arguments:
+1. Arguments were the premises are limited to the premises of the PGA.
+2. Special 'Arguments' that indicate that the generation of the remaining proof must be delegated to another PGA.
+
+dealing with large proofs: delegate to self after generating (say 100) arguments.
+
+- (calulator like usage) - sometimes you don't care about proof just want to find what 157+346 is.
+You can set the fetch\_proof flag to `false' and `parse\_lenient' to 'true' in the request to the PGA.
+Saves computation.
+
+\subsection{Implementing a PGA}
+It is the responsibility of the PGA to parse the input, and optionally do the computation and proof generation.
+The sophize platform merely forwards the request to the PGA and performs some sanity checks on the output.
+
+Any http server that can process the proof requests can be easily plugged in to Sophize.
+The registration is done in minutes and just requires just the specifying the address of the server to the Sophize's administrator.
+One server can implement multiple PGAs.
+
+\subsection{Materializing results}
+
+Sophize allows saving the fact that a machine has returned a valid proof for a proposition (not the actual proof which can be quite large).
+Then this proposition can be used in further proofs without the need to invoke the proof generation every time.
+The proof, of course, can be requested by the users whenever required.
 
@@
 \todo{copyright/access management}
+
 \todo{efficient computation and storage of proof graphs}
-\todo{reading from disk }
+
+\todo{ storing and reading data in disk/GitHub like repo }
 

### 2022-04-21 CEURART/sophize_md.tex
Changes as needed by the new template

--- 2021-07-25 sophize_md.tex
@@
-\documentclass[a4paper]{article}
+\documentclass[]{ceurart}
+
+%%
+%% One can fix some overfulls
+% \sloppy
+
+%%
+%% Minted listings support 
+%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
+%% \usepackage{minted}
 \usepackage{graphicx}
-\usepackage{onecolceurws}
 \usepackage{csquotes}
@@
 
-\title{Sophize Markdown and Collaboration Interface }
+%% auto break lines
+%%\setminted{breaklines=true}
 
-\author{ Abhishek Chugh }
+%prevent overflowing URLs; suggested by Franck in
+% https://tex.stackexchange.com/questions/636114/how-can-i-prevent-urls-in-an-eprint-field-from-overflowing-in-the-references-i/636172#636172
+\def\UrlBreaks{\do\/\do-}
+\hypersetup{breaklinks=true}
+\urlstyle{same}
 
-\institution{ Sophize Foundation\\ Bengaluru, India \\ abc@sophize.org }
+%%
+%% end of the preamble, start of the body of the document source.
+\begin{document}
 
-\begin{document}
-\maketitle
+\graphicspath {{../res}}
+%%
+%% Rights management information.
+%% CC-BY is default license.
+\copyrightyear{2021}
+\copyrightclause{Copyright for this paper by its authors.
+  Use permitted under Creative Commons License Attribution 4.0
+  International (CC BY 4.0).}
+
+%%
+%% This command is for the conference information
+\conference{CICM-WS}
+
+%%
+%% The "title" command
+\title{Sophize Markdown and Collaboration Interface}
+
+\author{Abhishek Chugh}[%
+orcid=0000-0001-6765-5229,
+email=abc@sophize.org,
+url=https://linkedin.com/in/abhishekchugh,
+]
+\address{Sophize Foundation, Bengaluru, India}
 
@@
 
-\vskip 32pt
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\begin{keywords}
+  sophize\sep
+  markdown \sep
+  proof graph \sep
+  polymath \sep
+  library \sep
+  semantic \sep
+  collaboration \sep
+  platform
+\end{keywords}
+
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
+\maketitle
 
@@
 
-\subsubsection*{Background: The Sophize Platform}
+\subsection*{Background: The Sophize Platform}
 
@@
 
-\subsubsection*{Proofs in Sophize}
+\subsection*{Proofs in Sophize}
 
@@
 
-\subsubsection*{Mathematics collaborations}
+\subsection*{Mathematics collaborations}
 
@@
 
-\subsubsection*{Contribution}
+\subsection*{Contribution}
 
@@
 
-\subsection*{Acknowledgements}
+\begin{acknowledgments}
 This publication resulted (in part) from research supported by the International Mathematical Union.
 The author would like to thank Patrick Ion and Michael Kohlhase for help in organizing our ideas and structuring the content of the paper.
+\end{acknowledgments}
 
@@
 \subsection{Sophize's Data Model}
-\paragraph{Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
+\paragraph{}Before we describe the Sophize Markdown language, it will be necessary to briefly describe how Sophize models mathematical entities.
 The data model is published in JSON schema \cite{sophize_datamodel} and popular package managers such as MVN, npm and PyPI.
-We describe relevant parts of the concepts used here.}
+We describe relevant parts of the concepts used here.
 
-\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
-Each resource has a URI and contains fields such as search tags and citations.}
+\paragraph{}A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+Each resource has a URI and contains fields such as search tags and citations.
 
@@
 
-\paragraph{A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
+\paragraph{}A \textbf{term} is a clearly defined entity that can be used to make up a valid proposition.
 It can be a mathematical object, operator, symbol, data structure, algorithm, or even a person.
-`Meaningless' primitives in formal theories are also categorized as terms.}
+`Meaningless' primitives in formal theories are also categorized as terms.
 
-\paragraph{A \textbf{proposition} is a grammatically valid statement that can be either true or false.
-Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.}
+\paragraph{}A \textbf{proposition} is a grammatically valid statement that can be either true or false.
+Axioms, theorems, conjectures, hypotheses, lemmas, corollaries, and converses are all classified as propositions.
 
-\paragraph{An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
+\paragraph{}An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
 In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
-A proof is seen as a directed graph of arguments and propositions.}
+A proof is seen as a directed graph of arguments and propositions.
 
@@
 
-	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_green\_tao\_theorem, 'Green–Tao Theorem'$\vert$NAV\_LINK)
+	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_green, 'Green Theorem'$\vert$NAV\_LINK)
 
@@
 
-\paragraph{\textbf{NAME} (default): This option fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.}
+\paragraph{}\textbf{NAME} (default): This option fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.
 
-\paragraph{\textbf{LOWER\_CASE (LC) or UPPER\_CASE (UC)}: These options become quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.}
+\paragraph{}\textbf{LOWER\_CASE (LC) or UPPER\_CASE (UC)}: These options become quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.
 
-\paragraph{\textbf{Custom text}: A link can also explicitly specify the link text by enclosing it in single quotes.}
+\paragraph{}\textbf{Custom text}: A link can also explicitly specify the link text by enclosing it in single quotes.
 
-The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and thus not specified in the URIs.
+\paragraph{}The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and thus not specified in the URIs.
 
@@
 
-\paragraph{The above code is rendered as:}
+\paragraph{}The above code is rendered as:
 \begin{mdframed}
@@
 
-\paragraph{\textbf{OVERLAY\_LINK} (default): By default, clicking on links opens up a modal dialog with the resource's summary.}
+\paragraph{}\textbf{OVERLAY\_LINK} (default): By default, clicking on links opens up a modal dialog with the resource's summary.
 
-\paragraph{\textbf{NAV\_LINK}: We can create a hyperlink to the resource's URL using the using NAV\_LINK option.}
+\paragraph{}\textbf{NAV\_LINK}: We can create a hyperlink to the resource's URL using the using NAV\_LINK option.
 
-\paragraph{\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element whose hover text is the URI of the resource.}
+\paragraph{}\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element whose hover text is the URI of the resource.
 
@@
 \begin{verbatim}
-# Conic section
+## Conic section
 
-A conic section (or simply conic) is a curve obtained as the intersection of the
-#(wiki/T_conical_surface, 'surface') of a #wiki/T_cone with a #wiki/T_plane. There are
-three types of conic sections.
+A conic section (or simply conic) is a curve obtained as the intersection
+of the #(wiki/T_conical_surface, 'surface') of a #wiki/T_cone with a 
+#wiki/T_plane. There are three types of conic sections.
 
@@
 
-\paragraph{The above code is rendered as:}
+\paragraph{}The above code is rendered as:
+
 \begin{mdframed}
-\section*{Conic Section}
+\subsubsection*{Conic Section}
 A conic section (or simply conic) is a curve obtained as the intersection of the \dashuline{surface} of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
 
-\subsection*{Ellipse}
+\subsubsection*{Ellipse}
 An ellipse is a regular \dashuline{oval} shape, traced by a point moving in a plane so that the sum of its distances from two other points (the foci) is constant, or resulting when a cone is cut by an oblique plane which does not intersect the base.
@@
 
-\subsection*{Parabola}
+\subsubsection*{Parabola}
+
 A parabola is a \dashuline{symmetrical} open plane curve formed by the intersection of a cone with a plane parallel to its side. The area of a parabola is unbounded.
@@
 \begin{verbatim} 
-Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of 
-happiness is what fetched $1.3 million recently. While it may not fetch many \$s, I 
-like the field equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
+Einstein's most famous equation is $E=mc^2$ but it is his
+handwritten theory of happiness is what fetched $1.3 million
+recently. While it may not fetch many \$s, I like the
+field equations more: 
+$$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
 \end{verbatim}
@@
 
-\subsection*{Sources}
+\subsection*{Online Resources}
 The Sophize Markdown parser and its Angular renderer source code are available under an MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
@@
 
-\bibliographystyle{alpha}
+\Urlmuskip=0mu plus 1mu\relax
 

### 2022-05-25 math_library/sophize_math.tex
minor
For CICM '22 submission -1/X

@@
 
-\title{Sophize Markdown and Collaboration Interface }
+\title{Sophize Mathematics Library (Work In Progress) }
 
@@
 \begin{abstract}
-[FROM CICM] Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
-We present a Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
-With this knowledge organization scheme at its core, we have engineered that platform to aggregate knowledge from sources.
+Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
+We present Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
+With this knowledge organization scheme at its core, we have engineered a platform to aggregate knowledge from multiple sources.
 The platform meaningfully combines knowledge from published research, encyclopedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
@@
 
-\subsection*{Acknowledgements [FROM CICM]}
-This publication resulted (in part) from research supported by the International Mathematical Union.
-The author would like to thank Patrick Ion and Michael Kohlhase for help in organizing our ideas and structuring the content of the paper.
+\section{Sophize's Knowledge Organization Scheme}
+At its core, Sophize's approach is to simply keep track of all arguments in favour or against any proposition.
+Use of arguments is the common factor amongst all mathematical (and scientific) knowledge.
+We use this fact to unify knowledge from multiple sources in a meaningful way as described below.
 
-\section{Sophize's Knowledge Organization Scheme}
-For math, logical consistency is the sole criteria for truth. Thus, as a math library, Sophize models mathematical knowledge using logical arguments.
+We use the set of all known arguments to track knowledge from a variety of foundational theory.
+For theoretical knowledge, i.e., knowledge that doesn't involve empirical data, the primary criteria of validity is internal (logical) consistency.
+Thus, for each foundational theory (for every belief set to be precise), we also keep track of any contradictions that arise from those foundations.
 
-\subsection{Core concepts [FROM CICM]}
+The following subsections will introduce concepts that will be
+
+\subsection{Core concepts}
 The various concepts used for organizing knowledge logically are described below.
 These concepts have been modelled in JSON schema \cite{sophize_datamodel} and published for popular programming language such as Java (MVN), Javascript (npm) and Python (PyPI).
+
+\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, arguments, and belief sets.
+Each resource has a URI and contains fields such as search tags and citations.}
+
+A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
+The dataset-id may be omitted if it can be inferred from the surrounding context.
+
+For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
+When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+
+The same URI scheme will be used in this paper to refer to various terms, propositions, arguments, etc.
 
@@
 
-\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
-Each resource has a URI and contains fields such as search tags and citations.}
+Sophize's notions of \textbf{belief sets} and \textbf{proof-generating machine} is described later in this section.
 
-A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
-The dataset-id may be omitted if it can be inferred from the surrounding context.
+\subsection{Argument Graph}
+An argument can be seen as a simple graph (see Figure \ref{argument}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
+The edge of this graph are directed and go from (a) premise nodes to argument and (b) argument node to conclusion node.
 
-For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=4cm]{argument}}
+\caption{An argument represented as a graph.}
+\label{argument}
+\end{center}
+\end{figure}
 
-The same URI scheme will be used in this paper to refer to various terms, propositions, arguments, etc.
+A set of arguments will can thus be represented as a single graph that we call an \textbf{argument graph}.
 
-There are a couple more concepts that we will describe at later in the paper.
+\begin{figure}[ht]
+\begin{center}
+\fbox{\includegraphics[height=7cm]{argument_graph}}
+\caption{A set of arguments forming an argument graph.}
+\label{argument_graph}
+\end{center}
+\end{figure}
+
+A proposition is considered true if it is claimed by a sound argument.
+An argument is considered sound if it is valid and its premises are true.
+Also, as explained in the section above, the validity criteria of an argument is modelled as just another premise.
+Thus, the relationship between all propositions and arguments can be represented with a simple graph.
+The following figure shows the different types of nodes and edges in such a graph
+
+1. Nodes - propositions and arguments
+
+2. Edges - premise to argument and argument to conclusion
+
+\subsection{Truth value computation}
+
+Using the argument graph, we can find truth values of every proposition in a belief set.
+Starting with the unsupported proposition of the belief set, computing truth values can be done using a simple recursive algorithm.
+The output of this algorithm is another graph, that we call proof graph, that has a proof for all the propositions it contains.
+For each proposition, a proof in the form of DAG of arguments (starting with unsupported propositions) can be trivially extracted from this proof graph.
+
+Note that an argument graph combines with different belief sets to generate different proof graphs. The same argument may be utilized in multiple belief sets.
+
+\todo{alternate arguments, proofs for same proposition}
 
@@
 
-\subsection{Argument Graph}
-A proposition is considered true if it is claimed by a sound argument.
-An argument is considered sound if it is valid and its premises are true.
-Also, as explained in the section above, the validity criteria of an argument is modelled as just another premise.
-Thus, the relationship between all propositions and arguments can be represented with a simple graph.
-The following figure shows the different types of nodes and edges in such a graph
-
-1. Nodes - propositions and arguments
-
-2. Edges - premise to argument and argument to conclusion
-
-\subsection{Truth value computation}
-
-Using the argument graph, we can find truth values of every proposition in a belief set.
-Starting with the unsupported proposition of the belief set, computing truth values can be done using a simple recursive algorithm.
-The output of this algorithm is another graph, that we call proof graph, that has a proof for all the propositions it contains.
-For each proposition, a proof in the form of DAG of arguments (starting with unsupported propositions) can be trivially extracted from this proof graph.
-
-Note that an argument graph combines with different belief sets to generate different proof graphs. The same argument may be utilized in multiple belief sets.
-
-\todo{alternate arguments, proofs for same proposition}
-
 \subsection{Translations}
@@
 Conjectural knowledge (Reimann hypothesis).
+
 Practical utility of conjectural knowledge - eg. a lot of infromation security systems assume  P not NP)
+
+Proof tailored to needs. Proof graph can be easily converted to prose too.
 

### 2022-05-25 math_library/sophize_math.tex
For CICM'22 submission -2/X

@@
 \begin{abstract}
-Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
-We present Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
-With this knowledge organization scheme at its core, we have engineered a platform to aggregate knowledge from multiple sources.
-The platform meaningfully combines knowledge from published research, encyclopedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
+[FROM CICM] Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
+We present a Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety of proofs.
+With this knowledge organization scheme at its core, we have engineered that platform to aggregate knowledge from several sources.
+The platform meaningfully combines knowledge from published research, encyclopedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath.
+Furthermore, it allows its users to run a federated search over them.
 To make this happen, two developments were necessary.
 First, we developed an open plugin architecture that allows proofs from computer programs to be generated as required.
-Second, we extended the Markdown language to represent the connections between between mathematical objects found across various sources of knowledge.
+Second, we extended the Markdown language to represent the connections between between mathematical objects found in various sources of knowledge.
 In addition, we also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
@@
 In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
-A proof is seen as a directed graph of arguments and propositions.}
+A proof is seen here as a directed graph of arguments and propositions.}
 
-Sophize's notions of \textbf{belief sets} and \textbf{proof-generating machine} is described later in this section.
+\paragraph{A \textbf{resource} is an abstract concept inherited by all other top-level concepts like terms, propositions, and arguments.
+Each resource has a URI and contains fields such as search tags and citations.}
 
@@
 \subsection{Validity of arguments}
-Validity of an argument is, in principle, objectively verifiable. A formally defined logistic systems have a mechanical procedure to verify validity arguments.
+Validity of an argument is, in principle, objectively verifiable. Formally defined logistic systems have a mechanical procedure to verify validity arguments.
 
-However, mathematics only utilizes a tiny portion formally verifiable arguments.
+However, mathematics only utilizes a tiny portion of formally verifiable arguments.
 Most mathematics is verified via peer review, some of this knowledge is curated by experts in books, encyclopaedias.
 The claim of validity of proofs (arguments) is judged based on the various parameters such as academic standing of the claimant, reputation of the peer reviewing journal, the history of errors of the book or encyclopedia containing them, etc.
-Clearly, this criteria is subjective and can vary to some extent for each individual.
+Clearly, these criteria are subjective and can vary to some extent for each individual.
 
@@
 Instead, it allows its users to choose the criteria they believe in.
-A validity criteria is modelled as a proposition and each argument has one such validity criteria associated with it.
+A validity criterion is modelled as a proposition and each argument has one such validity criterion associated with it.
 
 Some sample validity criteria:
+
 1. Formally verified using 3 independent COQ verifiers.
@@
 
-4. Claimed by someone.
+4. Claimed by Maryam Gauss.
 
-For easily managing validity criteria, the relationships between validity criteria are also maintained using argument like dependency graphs.
+To easily manage validity criteria, the relationships between validity criteria are also maintained using argument like dependency graphs.
 
@@
 
-In Sophize, a proposition is true if it is concluded by a valid argument and the premises of the argument are also true.
+In Sophize, a proposition is true if it is the conclusion of a valid argument and the premises of the argument are also true.
 
@@
 Traditionally, these are mathematical axioms and are considered to self-evidently true.
-However, there is no clear criteria to claim if a propositions is self-evidently true.
 In mathematical inquiry, theorems are proven/disproven in one or more multiple theories, each with its own set of axioms.
-Each theory may have its theoretical advantages and practical uses and there are no criteria to choose one theory over another when trying to assert a proposition's truth/falsity.
+Each theory may have its theoretical advantages and practical uses and there are no universal criteria to choose one theory over another when trying to assert a proposition's truth/falsity.
 
@@
 \subsection{Tracking Inconsistency}
-If a propositions and its negation is proved within a belief set is inconsistent.
+If a propositions and its negation is proved within a belief set, it is inconsistent.
 Due to principle of explosion, any propositions can be proved from such a contradiction.
@@
 
-Thus it is important to track and report contradictions in a belief set.
-Thus Sophize has a semantic notion of negation of a proposition.
-The premises or conclusion of an argument can be negation of propositions.
+Thus, it is important to track and report contradictions in a belief set.
+So, Sophize has a semantic notion of negation of a proposition.
+The premises or conclusion of an argument can be negations of propositions.
 
@@
 
-But, can represent translations manually using arguments.
+But, we can represent translations manually using arguments.
 Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
-Again, a user can choose not to accept this criteria in which case, these translations will not be used in the generating proof graphs.
+Again, a user can choose not to accept such criteria.
+In that case, these translations will not be used in the generating proof graphs.
 
@@
 
-Conjectural knowledge (Reimann hypothesis).
-
-Practical utility of conjectural knowledge - eg. a lot of infromation security systems assume  P not NP)
-
+Conjectural knowledge (Riemann hypothesis). 
+Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
 Proof tailored to needs. Proof graph can be easily converted to prose too.
@@
 \subsection{'Active' PGA}
-As with other parts of Sophize, the output of an PGA is not taken for granted.
+As with other parts of Sophize, the validity of the output of a PGA is not taken for granted.
 Each automata specifies the premises (assumptions) that it uses to generate its proof.
@@
 A PGA receives as a proposition as an input. The output of a PGA has the following components:
+
 1. Truth value of the proposition.
+
 2. The proof of the propositions (or its negation) as a DAG of arguments generated by the PGA.
 
-Note that unlike other propositions, arguments on Sophzie these are not stored on disk but do have a temporary URI specified in a slightly different format.
+Note that unlike other propositions, and arguments on Sophize these are not stored on disk but do have a temporary URI specified in a slightly different format.
 The leaves of the DAG can have two kinds of arguments:
@@
 
-- (calulator like usage) - sometimes you don't care about proof just want to find what 157+346 is.
+- (calculator like usage) - sometimes you don't care about proof just want to find what 157+346 is.
 You can set the fetch\_proof flag to `false' and `parse\_lenient' to 'true' in the request to the PGA.
@@
 It is the responsibility of the PGA to parse the input, and optionally do the computation and proof generation.
-The sophize platform merely forwards the request to the PGA and performs some sanity checks on the output.
+Sophize platform merely forwards the request to the PGA and performs some sanity checks on the output.
 

### 2022-05-27 math_library/sophize_math.tex
For CICM '22 - 3/X

--- 2022-05-25 math_library/sophize_math.tex
@@
 
-\title{Sophize Mathematics Library (Work In Progress) }
+\title{Sophize Knowledge Organization}
 
@@
 With this knowledge organization scheme at its core, we have engineered a platform to aggregate knowledge from multiple sources.
-The platform meaningfully combines knowledge from published research, encyclopedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
+The platform meaningfully combines knowledge from published research, encyclopaedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
 To make this happen, two developments were necessary.
@@
 
-\subsubsection*{Proofs in Sophize  [FROM CICM]}
+\subsubsection*{Proofs in Sophize}
 Sophize is a novel mathematics library and discussion platform.
@@
 Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopaedia, Wikipedia, and the Metamath formal system \cite{metamath}.
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \begin{center}
@@
 At its core, Sophize's approach is to simply keep track of all arguments in favour or against any proposition.
-Use of arguments is the common factor amongst all mathematical (and scientific) knowledge.
+Use of some form of arguments is the common factor amongst all mathematical (and perhaps all scientific) knowledge.
 We use this fact to unify knowledge from multiple sources in a meaningful way as described below.
 
-We use the set of all known arguments to track knowledge from a variety of foundational theory.
+We use the set of all known arguments to track knowledge from a variety of foundational theories.
 For theoretical knowledge, i.e., knowledge that doesn't involve empirical data, the primary criteria of validity is internal (logical) consistency.
-Thus, for each foundational theory (for every belief set to be precise), we also keep track of any contradictions that arise from those foundations.
-
-The following subsections will introduce concepts that will be
+Thus, for each foundational theory (`belief set' described below), we also keep track of any contradictions that arise from those foundations.
+\todo{section is crap, overview of how aggregated}
 
 \subsection{Core concepts}
-The various concepts used for organizing knowledge logically are described below.
-These concepts have been modelled in JSON schema \cite{sophize_datamodel} and published for popular programming language such as Java (MVN), Javascript (npm) and Python (PyPI).
+Sophize uses the following concepts to logically organize theoretical knowledge.
 
@@
 For example, the Pythagorean theorem (a \textbf{P}roposition) represented in the Metamath project may have the URI \emph{metamath/\textbf{P}\_pythagorean} and the definition of cone (a \textbf{T}erm) extracted from Wikipedia may have the URI \emph{wiki/\textbf{T}\_cone}.
-When used inside another resource in the `wiki' dataset, cone's definition can be referred to simply as \emph{T\_cone}.
+When used inside another resource in the same (`wiki') dataset, cone's definition can be referred to simply as \emph{T\_cone}.
 
@@
 In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
-A proof is seen as a directed graph of arguments and propositions.}
+A proof is seen here as a directed graph of arguments and propositions.}
 
-Sophize's notions of \textbf{belief sets} and \textbf{proof-generating machine} is described later in this section.
+\paragraph{A \textbf{belief set} is roughly the set of axiomatic propositions that make up the foundations of a theory. Belief sets will be described in more detail in subsection \ref{sec:bset}.}
+
+\paragraph{Loosely defined, a \textbf{proof-generating machine} (PGM) is a computer program that generates the proof for an input proposition.
+PGMs are described in more detail in section \ref{sec:pgm}.}
 
@@
 An argument can be seen as a simple graph (see Figure \ref{argument}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
-The edge of this graph are directed and go from (a) premise nodes to argument and (b) argument node to conclusion node.
+The edges of this graph are directed and go from (a) premise nodes to argument node and (b) argument node to conclusion node.
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \begin{center}
-\fbox{\includegraphics[height=4cm]{argument}}
+\fbox{\includegraphics[height=3.5cm]{argument}}
 \caption{An argument represented as a graph.}
@@
 
-A set of arguments will can thus be represented as a single graph that we call an \textbf{argument graph}.
+A set of arguments can thus be represented as a single graph that we call an \textbf{argument graph} (Figure \ref{argument_graph}).
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \begin{center}
@@
 
-A proposition is considered true if it is claimed by a sound argument.
-An argument is considered sound if it is valid and its premises are true.
-Also, as explained in the section above, the validity criteria of an argument is modelled as just another premise.
-Thus, the relationship between all propositions and arguments can be represented with a simple graph.
-The following figure shows the different types of nodes and edges in such a graph
+\subsection{Generating Proof Graphs}
+An argument graph along with a set of set of axioms results in a \textbf{proof graph}.
+Any reachability algorithm starting with the axiom nodes is sufficient to create the proof graph (See Figure \ref{proof_graph1}).
 
-1. Nodes - propositions and arguments
+\begin{figure}[htbp]
+\begin{center}
+\fbox{\includegraphics[height=7cm]{proof_graph1}}
+\caption{Proof graph from argument graph (Figure \ref{argument_graph}) using `Prop 2', `Prop 3', Prop 4' are axioms.}
+\label{proof_graph1}
+\end{center}
+\end{figure}
 
-2. Edges - premise to argument and argument to conclusion
+A proof graph is a directed acyclic graph and contains complete proofs (including all alternate proofs) for all its propositions.
 
-\subsection{Truth value computation}
+\begin{figure}[htbp]
+\begin{center}
+\fbox{\includegraphics[height=6cm]{proof_prop7}}
+\caption{Proof of `Prop 7' from proof graph in Figure \ref{proof_graph1} uses arguments `Arg 4' and `Arg 5'.}
+\label{proof_prop7}
+\end{center}
+\end{figure}
 
-Using the argument graph, we can find truth values of every proposition in a belief set.
-Starting with the unsupported proposition of the belief set, computing truth values can be done using a simple recursive algorithm.
-The output of this algorithm is another graph, that we call proof graph, that has a proof for all the propositions it contains.
-For each proposition, a proof in the form of DAG of arguments (starting with unsupported propositions) can be trivially extracted from this proof graph.
+Note that an argument graph combines with different sets of axioms to generate different proof graphs. The same argument may be utilized in multiple belief sets (Figure \ref{proof_graph2}).
 
-Note that an argument graph combines with different belief sets to generate different proof graphs. The same argument may be utilized in multiple belief sets.
-
-\todo{alternate arguments, proofs for same proposition}
+\begin{figure}[htbp]
+\begin{center}
+\fbox{\includegraphics[height=8cm]{proof_graph2}}
+\caption{Proof graph from the same argument graph (Figure \ref{argument_graph}) using `Prop 1', `Prop 2', and Prop 7' as axioms.}
+\label{proof_graph2}
+\end{center}
+\end{figure}
 
 \subsection{Validity of arguments}
-Validity of an argument is, in principle, objectively verifiable. A formally defined logistic systems have a mechanical procedure to verify validity arguments.
 
-However, mathematics only utilizes a tiny portion formally verifiable arguments.
-Most mathematics is verified via peer review, some of this knowledge is curated by experts in books, encyclopaedias.
-The claim of validity of proofs (arguments) is judged based on the various parameters such as academic standing of the claimant, reputation of the peer reviewing journal, the history of errors of the book or encyclopedia containing them, etc.
-Clearly, this criteria is subjective and can vary to some extent for each individual.
+The correctness of proofs obtained by the above process is contingent on the validity of the arguments in the argument graph.
+The validity of an argument is, in principle, independent of other arguments and objectively verifiable.
+Formally defined logistic systems indeed have a mechanical procedure to independently verify validity of arguments.
+
+However, only a small section of Mathematics is developed using formally verified arguments.
+Vast majority of mathematics is verified via peer review, some of this knowledge is curated by experts in books, encyclopaedias.
+The claim of validity of proofs (arguments) is judged based on the various parameters such as academic standing of the claimant, reputation of the peer reviewing journal, the history of errors of the book or encyclopaedia containing them, etc.
+Clearly, these criteria are subjective and each individual's criteria of accepting validity of an argument can vary to some extent.
 
@@
 Instead, it allows its users to choose the criteria they believe in.
-A validity criteria is modelled as a proposition and each argument has one such validity criteria associated with it.
+The validity criterion is modelled as a proposition and is attached to arguments as a premise.
 
-Some sample validity criteria:
-1. Formally verified using 3 independent COQ verifiers.
+\begin{figure}[htbp]
+\begin{center}
+\fbox{\includegraphics[height=5cm]{validity_criterion}}
+\caption{Validity criteria as an argument premise.}
+\label{validity_criterion}
+\end{center}
+\end{figure}
 
-2. Peer reviewed by XYZ journal
-
-3. Published on Wikipedia.
-
-4. Claimed by someone.
-
-For easily managing validity criteria, the relationships between validity criteria are also maintained using argument like dependency graphs.
-
-Eg. published in journal with score more than 0.67 $\rightarrow$ published in Annals of Mathematics
-
-\todo{Q. Who has the time to setup belief sets? How does Sophize make it 
-convenient.}
+To easily manage validity criteria, the relationships between validity criteria are also maintained in the argument graph using argument-like dependency graphs.
+Eg.
+"Published in journal with SJR score $>$ 0.67" $\rightarrow$ "Published in Annals of Mathematics".
+By maintaining relationships like above, Sophize allows its users to conveniently choose multiple sources they consider to be reliable with a single manually chosen criterion.
 
 \subsection{Belief sets}
+\label{sec:bset}
 
-In Sophize, a proposition is true if it is concluded by a valid argument and the premises of the argument are also true.
-
+A proposition is true if it is the conclusion of a valid argument and the premises of the argument are also true.
 Of course, this means that we need to start with some propositions that are assumed to be true without further justification.
 Traditionally, these are mathematical axioms and are considered to self-evidently true.
-However, there is no clear criteria to claim if a propositions is self-evidently true.
 In mathematical inquiry, theorems are proven/disproven in one or more multiple theories, each with its own set of axioms.
-Each theory may have its theoretical advantages and practical uses and there are no criteria to choose one theory over another when trying to assert a proposition's truth/falsity.
+Each theory may have its theoretical advantages and practical uses and there are no universal basis to choose one theory over another when trying to assert a proposition's truth/falsity.
 
 Thus, Sophize allows any set of propositions to be considered true without evidence.
-Such a set of propositions is called a belief set.
-Thus, the truth-value of a proposition is only defined within a belief set - there is no notion of of absolute or universal truth.
+Such a set of propositions is called a \textbf{belief set}.
+Propositions representing argument validity criteria are also part of belief sets.
+All propositions that are considered to be true in a belief set without proof are called its `unsupported propositions'.
+In addition, a belief set can also contain a number of `proof-generating machines' (e.g.
+for managing axiom-schemas) that will be discussed later.
+For ease of use, belief sets can also contain other belief sets.
 
-Propositions representing argument validity criteria are also part of belief sets. All propositions that are considered to be true in a belief set without proof are called `unsupported propositions'.
+The truth-value of a proposition is only defined within a belief set - there is no notion of of absolute or universal truth. Sophize creates proof graphs for all its belief sets.
 
-Computing of truth values in a belief set is thus a simple recursive graph algorithm as explained in the section below. Sophize computes truth values for all its belief sets.
+\subsection{Tracking Inconsistencies}
+If a proposition and its negation is proved within a belief set, it is inconsistent.
+As noted by the principle of explosion, any proposition can be proved from such a contradiction, thus making the claim of truth of any proposition practically worthless.
 
-\subsection{Tracking Inconsistency}
-If a propositions and its negation is proved within a belief set is inconsistent.
-Due to principle of explosion, any propositions can be proved from such a contradiction.
-Thus making the claim of truth of any proposition practically worthless.
+Thus, it is important to track and report contradictions in a belief set.
+To do that Sophize has a semantic notion of negation of a proposition.
+The premises or conclusion of an argument can be negations of propositions.
+When a proposition and its negation are proven, the system reports such contradictions for every belief set.
+When generating proof graphs from the argument graph, a contradicting proposition cannot be used a premise for any argument.
 
-Thus it is important to track and report contradictions in a belief set.
-Thus Sophize has a semantic notion of negation of a proposition.
-The premises or conclusion of an argument can be negation of propositions.
+\subsection{Aggregating knowledge}
 
-When a proposition and its negation are proven, the system reports such contradictions for every belief set.
+\section{Proof-Generating Machines (PGM)}
+\label{sec:pgm}
+A lot of mathematical knowledge is computed. Computation machines (e.g. calculators, algebras) can be seen as performing the following tasks
+\begin{itemize}
+\item Parsing the input into a language that can represent math formulae. 
+\item Finding and outputting an equivalent form of the formula.
+\end{itemize}
+Thus, their focus is not on finding the proof but only finding the equivalent (simplified) representation of the input formula (Although many computer algebras do show the steps of the computation.).
+With Sophize, the focus instead is to generate proofs of the input propositions.
+A \textbf{Proof-generating machine} (PGM for short) is a computer program that generates a partial proof graph against or in favour of an argument.
+PGMs can also have the capability to perform tasks 1 and 2, mentioned above.
 
-\subsection{Translations}
+PGMs take in some text as input which is parsed by the each PGM as they wish.
+Typically the text is treated either as a proposition (e.g.
+`3 + 5 = 8') or a formula (eg.
+`5+6') and in the latter case the PGM is responsible for finding an appropriate proposition (eg.
+`5 + 6 = 11') for the given input.
+The PGM then generates a proof graph for this proposition and returns back to the user.
+
+The Sophize platform itself merely forwards the request to the associated PGM and performs some checks on the output returned.
+Any http server that can process a proof request can be easily plugged in to Sophize platform using its HTTP address.
+One server can implement multiple PGMs.
+
+\subsection{`Active' PGMs}
+As with other parts of Sophize, the validity of the output of a PGM is not taken for granted.
+Each PGM must specify all the propositions (premises) that it will use in the root nodes of the proof graph it returns.
+In addition, a PGM may also delegate parts of proofs to another PGM.
+These PGMs must also be specified.
+
+A PGM is considered `active' in a belief set iff:
+\begin{enumerate}
+\item all of its premises are true in the belief set.
+\item all the PGMs it delegates-to are active.
+\end{enumerate}
+
+If the PGM returns a proof graph that utilizes As with an argument, one or more premises is used to indicate the validity of the PGM (Eg.
+tested by X, verified by some committee, another program etc).
+Thus, to be considered active in a belief set, the PGM must have a verification criteria that matches the belief set's requirements.
+The output of a PGM is not used in belief sets in which it is not active.
+
+\subsection{PGM response}
+The response of a request to any PGM has the following components:
+
+\begin{itemize}
+
+\item Truth value, i.e., whether the PGM considers the input proposition (provided or computed) true or false.
+PGM can also indicate that it doesn't understand the input or prove/disprove the proposition.
+
+\item Proof graph (or a subset of proof graph) generated by the PGM in favour or against the input proposition. This component is skipped if only computation results are requested.
+\end{itemize}
+
+Note that unlike other propositions and arguments on Sophize, these are not stored on disk.
+They have a temporary URI specified in a slightly different format.
+The leaves of the DAG can have two kinds of arguments:
+
+\begin{enumerate}
+\item Arguments whose the premises are limited to the premises of the PGM.
+\item Special `Arguments' that indicate that the generation of the remaining proof must be delegated to another PGM.
+In case of large proofs, a PGM may also delegate to itself after generating some (say 100) arguments.
+\end{enumerate}
+\subsection{Materializing results}
+
+Sophize allows saving the fact that a machine has returned a valid proof for a proposition (not the actual proof itself which can be quite large).
+Then this proposition can be used in further proofs without the need to invoke the proof generation every time.
+The proof, of course, can be requested by the users whenever required.
+
+\subsection{Connection across data sources}
 \todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
@@
 
-Conjectural knowledge (Reimann hypothesis).
-
-Practical utility of conjectural knowledge - eg. a lot of infromation security systems assume  P not NP)
-
+Conjectural knowledge (Riemann hypothesis). 
+Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
 Proof tailored to needs. Proof graph can be easily converted to prose too.
 
-\subsubsection{Other Notes}
-\todo{What criteria are met based on the 2013 report}
+\section{Sophize Markdown}
 
-\todo{How much math can be represented. Eg. three valued logic}
+In the author's view, it is crucial to maintain the proofs graphs for building trustable knowledge.
+However, the presentation of proofs as graphs to users is perhaps not very convenient.
+Traditional text based narration remains indispensable when presenting knowledge to the reader.
 
-\todo{Sophize's limitations. In "Potential Value of a
-Digital Mathematics Library" in 2013 report.
-Sophize offers no way to more easily find analogies or weaker forms of reasoning like “If A is true, then B is true.
-B is true; therefore, A becomes more plausible.” }
+We have extended the Markdown language - a lightweight markup language for creating formatted text using a plain-text editor - for building a rich narration interface.
+It allows users to quickly encode and present semantic data, to show the truth status of propositions available in prose, and to effortlessly access proof graphs.
+The detailed specification of Sophize Markdown is available here.
+Many of its features are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}.
+We highlight some of the salient features here.
 
-\section{Proof Generating Automata (PGA)}
-A lot of mathematical knowledge is computed. Computation machines (calulators, algebras) can be seen as performing the following tasks: 
-1. parsing the input into a language that can represent math formulae. 
-2. Finding and outputting an equivalent form of the formula.
+\subsection{Embedding semantic data}
 
-Thus, their focus is not on finding the proof but only finding the equivalent (simplified) representation of the input formula. (Although many computer algebras do show the steps of the computation.)
+With Sophize Markdown we can easily link resources such as terms, propositions, and arguments.
+Links can be added using the pound sign (\#) and the resource's URI.
+There are multiple resource link options that can be used for changing the behavior and text of the resource link.
+The following examples demonstrate these options.
 
-With Sophize, the focus instead is to generate proofs of the input propositions. However, Sophize machines can also have the capability to perform tasks 1 and 2, mentioned above.
-
-\subsection{'Active' PGA}
-As with other parts of Sophize, the output of an PGA is not taken for granted.
-Each automata specifies the premises (assumptions) that it uses to generate its proof.
-In addition, an automata may also delegate parts of proofs to another automata.
-These automata must also be specified.
-
-An automata is considered 'active' in a belief set if:
-1) all of its premises are true
-2) all the automata it delegates-to are active.
-
-As with an argument, one or more premises is used to indicate the validity of the automata (Eg.
-tested by X, verified by some committee, another program etc).
-Thus, to be considered active in a belief set, the PGA must have a verification criteria that matches the belief set's requirements.
-
-\subsection{PGA response}
-A PGA receives as a proposition as an input. The output of a PGA has the following components:
-1. Truth value of the proposition.
-2. The proof of the propositions (or its negation) as a DAG of arguments generated by the PGA.
-
-Note that unlike other propositions, arguments on Sophzie these are not stored on disk but do have a temporary URI specified in a slightly different format.
-The leaves of the DAG can have two kinds of arguments:
-1. Arguments were the premises are limited to the premises of the PGA.
-2. Special 'Arguments' that indicate that the generation of the remaining proof must be delegated to another PGA.
-
-dealing with large proofs: delegate to self after generating (say 100) arguments.
-
-- (calulator like usage) - sometimes you don't care about proof just want to find what 157+346 is.
-You can set the fetch\_proof flag to `false' and `parse\_lenient' to 'true' in the request to the PGA.
-Saves computation.
-
-\subsection{Implementing a PGA}
-It is the responsibility of the PGA to parse the input, and optionally do the computation and proof generation.
-The sophize platform merely forwards the request to the PGA and performs some sanity checks on the output.
-
-Any http server that can process the proof requests can be easily plugged in to Sophize.
-The registration is done in minutes and just requires just the specifying the address of the server to the Sophize's administrator.
-One server can implement multiple PGAs.
-
-\subsection{Materializing results}
-
-Sophize allows saving the fact that a machine has returned a valid proof for a proposition (not the actual proof which can be quite large).
-Then this proposition can be used in further proofs without the need to invoke the proof generation every time.
-The proof, of course, can be requested by the users whenever required.
-
-\section{Other Engineering challenges}
-\todo{copyright/access management}
-
-\todo{efficient computation and storage of proof graphs}
-
-\todo{ storing and reading data in disk/GitHub like repo }
-
-\section{Sophize Markdown[FROM CICM]}
-
-Markdown is a lightweight markup language for creating formatted text using a plain-text editor.
-Markdown is very widely adopted on the web, and it makes it quite simple to add lists, headers, bold or italic fonts, images, and more.
-One can choose from several slightly varying Markdown specifications.
-We start with the widely supported CommonMark specification and create extensions for the features that we need.
-The extensions are implemented using the `markdown-it' \cite{markdown_it} JavaScript parser.
-The parser for Sophize Markdown produces an abstract syntax tree (AST).
-A separate renderer module utilizes the AST tree to create the appropriate HTML or Single Page Application (SPA) libraries.
-Many of the features of Sophize Markdown are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}
-
-\subsection{Embedding structured data}
-
-With Sophize Markdown we can easily embed resources such as terms, propositions, and arguments. Links can be added using the resource's URI, and the following formats are supported:
-
-\begin{itemize}
-
-	\item \#URI[ $\vert$ OPTIONS ]
-
-	Examples: \#wiki/T\_cone, \#planetmath/P\_covering\_lemma$\vert$NO\_LINK$\vert$LC
-
-	\item \#(URI, \textquotesingle Custom\ Text\textquotesingle [ $\vert$ OPTIONS ])
-
-	Examples: \#(wiki/T\_cone, \textquotesingle cones\textquotesingle), \#(P\_green\_tao\_theorem, 'Green–Tao Theorem'$\vert$NAV\_LINK)
-
-\end{itemize}
-
-There are multiple resource link options to embed a resource in the Markdown.
-These are required to make it convenient for the content creators to provide a rich experience to their readers.
-Some of the commonly used options are summarized below.
-
-\subsubsection{Link Text Options}
-
-\paragraph{\textbf{NAME} (default): This option fetches the resource and sets the link text to the name of the resource. For terms, the link text is set to the phrase of the term.}
-
-\paragraph{\textbf{LOWER\_CASE (LC) or UPPER\_CASE (UC)}: These options become quite useful when adding a link in the beginning or middle of a sentence where adding the name in its default case would be grammatically incorrect.}
-
-\paragraph{\textbf{Custom text}: A link can also explicitly specify the link text by enclosing it in single quotes.}
-
-The following example shows the above options in use. Note that we assume that the dataset-id of URIs is available from the context and thus not specified in the URIs.
-
+\subsubsection*{Example 1}
 \begin{verbatim}
-#P_cosine_law|UC is a generalization of the #P_pythagorean for all kinds of
-#(T_triangle, 'triangles').
+#P_cosine_law|UC generalizes the #P_pythagorean for all kinds of #(T_triangle, 'triangles').
 \end{verbatim}
@@
 \begin{mdframed}
-\dashuline{Law of cosines} is a generalization of the \dashuline{Pythagorean theorem} for all kinds of \dashuline{triangles}.
+\dashuline{Law of cosines} generalizes the \dashuline{Pythagorean theorem} for all kinds of \dashuline{triangles}.
 \end{mdframed}
 
-\subsubsection{Link Type Options}
+The link options 'UC/LC' makes the link text upper-cased or lower-cased.
 
-\paragraph{\textbf{OVERLAY\_LINK} (default): By default, clicking on links opens up a modal dialog with the resource's summary.}
-
-\paragraph{\textbf{NAV\_LINK}: We can create a hyperlink to the resource's URL using the using NAV\_LINK option.}
-
-\paragraph{\textbf{NO\_LINK}: NO\_LINK creates a non-clickable element whose hover text is the URI of the resource.}
-
-For example, the following Markdown code has all three link types:
+\subsubsection*{Example 2}
 \begin{verbatim}
-#T_matrix_multiplication|NO_LINK is a #(T_commutative_property, 
-'non-commutative'|NAV_LINK) #T_binary_operation.
+#T_matrix_multiplication|NO_LINK is a #(T_commutative_property, 'non-commutative'|NAV_LINK)
+#T_binary_operation.
 \end{verbatim}
@@
 \end{mdframed}
-The first element shows `\#wiki/T\_matrix\_multiplication' on mouse-hover. The second link navigates the page to a different URL. Clicking on the third link pops up a modal dialog box like so:
+This example shows the various link behaviours.
+The first element shows `\#wiki/T\_matrix\_multiplication' on mouse-hover.
+The second link navigates the page to a different URL.
+Clicking on the third link pops up a modal dialog box like so:
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \begin{center}
@@
 
-\subsubsection{Resource Expansion}
-
-Instead of creating a link, this option expands the resource in place.
-For terms and propositions, the definition and the statement are added in place, respectively.
-For arguments, its premises, conclusion, and the argument text is added.
-
-The following is a sample article where we re-use concepts and theorems already extracted from multiple sources (say, Wikipedia and the Oxford dictionary):
+\subsubsection*{Example 3}
 
@@
 A conic section (or simply conic) is a curve obtained as the intersection of the
-#(wiki/T_conical_surface, 'surface') of a #wiki/T_cone with a #wiki/T_plane. There are
-three types of conic sections.
+surface of a #wiki/T_cone with a #wiki/T_plane. There are three types of conic sections.
 
@@
 ## Parabola
-#oxford/T_parabola|EXPAND The area of a parabola is unbounded.
 ...
@@
 \section*{Conic Section}
-A conic section (or simply conic) is a curve obtained as the intersection of the \dashuline{surface} of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
+A conic section (or simply conic) is a curve obtained as the intersection of the surface of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
 
 \subsection*{Ellipse}
-An ellipse is a regular \dashuline{oval} shape, traced by a point moving in a plane so that the sum of its distances from two other points (the foci) is constant, or resulting when a cone is cut by an oblique plane which does not intersect the base.
+An ellipse is a regular \dashuline{oval} shape, traced by a point moving in a plane so that the sum of its distances from two other points is constant.
 The area $A_{ellipse}$ enclosed by an ellipse is $$A_{ellipse} = \pi a b$$where $a$ and $b$ are the lengths of the \dashuline{semi-major} and \dashuline{semi-minor} axes, respectively.
@@
 \subsection*{Parabola}
-A parabola is a \dashuline{symmetrical} open plane curve formed by the intersection of a cone with a plane parallel to its side. The area of a parabola is unbounded.
-
 ...
@@
 
-\subsubsection{Status Indicators}
+In the above example, the `EXPAND' option expanded the definition of the term, and statement of the proposition in place.
+Thus we were able to easily re-use concepts and theorems already extracted from other sources (say, Wikipedia and the Oxford dictionary in this case).
 
-For propositions, a Truth Value Icon indicating whether or not there is a proof is added next to the link.
+\subsection{Status Indicators}
+
+For propositions, a truth-value icon indicating whether or not there is a proof is added next to the link.
 Clicking on the icon brings up the proof graph as shown in Figure \ref{proof_tree}.
-Similarly, an icon is added next to an argument which indicates whether the argument is valid or not.
+Similarly, an icon is added next to a proof generating machine which indicates whether the PGM is active or not.
 These options can be turned on or off depending on the input and the context.
-Further details require an in-depth understanding of the Sophize knowledge organization scheme which is not our focus here.
 
@@
 
-While multiple applications extend Markdown to support TeX, there is no standardized syntax specification.
-However, Pandoc is the most widely used tool for converting \LaTeX\space to Markdown, and its specification is well documented and tested.
-Thus, we use their specification for our extension \cite{pandoc}:
-
-\blockquote{Anything between two \$ characters will be treated as TeX math.
-The opening \$ must have a non-space character immediately to its right, while the closing \$ must have a non-space character immediately to its left, and must not be followed immediately by a digit.
-Thus, \$20,000 and \$30,000 won’t parse as math.
-If for some reason you need to enclose text in literal \$ characters, backslash-escape them and they won’t be treated as math delimiters.
-
-For display math, use \$\$ delimiters.
-(In this case, the delimiters may be separated from the formula by whitespace.
-However, there can be no blank lines between the opening and closing \$\$ delimiters.)}
+With Sophize Markdown, we can add \LaTeX\space by enclosing it between two \$ signs (or \$\$ for display math).
 
@@
 
-\section{Sophize Collaboration [From CICM]}
-
-Sophize's communication interface is designed to allow multiple researchers to collaboratively solve a problem.
-In such open online collaborations, a lot of different ideas and approaches get introduced rapidly.
-Going through all these comments and making sense of the rapidly evolving ideas becomes a daunting task that can dissuade even the experts and the highly motivated.
-We believe that we have created a novel interface that can significantly mitigate this problem.
-The work is primarily influenced by recommendations made by Timothy Gowers and Terence Tao after organizing several Polymath projects \cite{polymath_blog}.
-We believe that the interface can aid many collaboration types - with few or many participants.
-We demonstrate the various features of this interface by incorporating actual data from a Polymath project at: \url{https://youtu.be/d3gaalJ7UQM}.
-
-\begin{figure}[ht]
-\begin{center}
-\fbox{\includegraphics[height=14cm]{collab}}
-\caption{Some elements of the Sophize Collaboration Interface.}
-\label{collab}
-\end{center}
-\end{figure}
-
-\subsubsection*{Requirements}
-
-Helping users make sense of the conversation and allowing them to get up to speed with existing progress as quickly as possible is perhaps the most important requirement for managing online collaborations.
-To solve this problem, we need to organize the ideas in an intuitive way and to summarize the progress.
-A reader should be able to quickly grasp the current state, and project moderators need a way to manage the direction of various threads to avoid the big picture from being obscured.
-
-Other technical requirements were discussed by some project participants and summarized by Tao on his blog \cite{whats_new_2009} (lightly edited):
-
-\begin{itemize}
-
-  \item \LaTeX\space support
-
-  \item Group moderation
-
-  \item Comment editing and preview
-
-  \item Comment numbering and/or threading
-
-  \item Wiki-like features, i.e., group-editable, publicly-viewable documents with version control
-
-  \item Some way to view all recent comments or developments in a project
-
-  \item Easy registration process
-
-  \item Easy commenting process (i.e., no technical knowledge required)
-
-  \item Permanent URLs for posts and comments (for link-back purposes)
-
-\end{itemize}
-
-We note that Sophize provides all the above features except that it doesn't yet allow users to look at the previous versions of documents. We summarize innovative features of the platform below:
-
-\subsection{Hierarchical Page Organization}
-
-As noted by Gowers, to make sense of the numerous ideas discussed, they need to be organized in a natural hierarchical way.
-The `proof discovery tree', as described by Gowers \cite{gowers_weblog_2009}, would have a precise approach to the main problem, and each of the subproblems that come up would have its own trees.
-The leaves of the tree would thus be sub-problems that get solved without division into sub-problems.
-
-Sophize brings the `Proof-discovery tree' to life by organizing the project using neatly organized wiki-like pages.
-Pages have a parent-child relationship allowing them to be organized like a tree.
-Discussion comments can be posted on any page, and moderators can rearrange them the way they think is best for the project.
-Moderators are also encouraged to add an overview on each page that quickly informs readers of the significant ideas that they should be familiar with before they start contributing.
-
-\subsection{Comment Summaries}
-
-Even after the hierarchical division of comments, some pages can still have a large number of comments, which make them difficult to follow.
-To overcome this problem, we allow project moderators to create summaries of discussions that have taken place so far.
-Comment summaries get embedded in the comment tree as a parent for comments they summarise.
-For example, they can club together multiple comment chains that are dead ends so that each reader doesn't waste time on them.
-Or they could summarize a sub-proof that was arrived at after dozens of comments.
-
 \subsection{Sophize Markdown benefits}
 
-Project collaborators get all the benefits of Sophize Markdown, such as easy linking of existing math content, \LaTeX\space support, and live preview of pages and comments being written or edited.
+With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
 
-Comments in Sophize are numbered serially (starting with 1 for each collaboration), each comment can be referenced with the hashtag notation (e.g., `\#3' for the 3rd comment).
-Comments in an external project can be referenced by providing the project's URI (\#URI/COMMENT\_NUMBER).
+\section{Other Engineering challenges}
+\todo{copyright/access management}
 
-Also, we make it extremely easy to extract terms, propositions and proofs from comments. These resources not only help in better understanding of the project, it also helps build Sophize's library.
+\todo{efficient computation and storage of proof graphs}
 
-\subsection{Reducing noise}
+\todo{ storing and reading data in disk/GitHub like repo }
+\subsubsection{Other Notes}
+\todo{What criteria are met based on the 2013 report}
 
-Sophize gives project moderators the usual tools like spam removal and fine-grained access control to manage participants.
-We also add a new feature where certain comments can be marked hidden.
-Often, threads of dozens of comments can be just noise because they were based on confused concepts or mistaken assumptions.
-Such comments should not be marked as spam.
-By marking such threads as `hidden', moderators can ensure that these are not shown by default.
-But any user can view them when required.
+\todo{How much math can be represented. Eg. three valued logic}
 
-\section{Conclusion and Future Work}
-
-We have presented Sophize Markdown, a lightweight language for representing mathematical knowledge on the web.
-Using this language, we can easily embed mathematical entities like definitions, theorems, and proofs, making it very convenient to find and browse relevant content.
-Sophize Markdown plays a central role in organizing proofs from various data sources on the Sophize platform.
-While there are other ways to represent semantic knowledge, such as content MathML and OpenMath, their scope is somewhat limited to specifying the meaning of the mathematical formula.
-The sTeX system \cite{Kohlhase2008} is perhaps most similar to Sophize Markdown but it needs creation of \LaTeX\space documents and use of \LaTeX ML systems.
-This makes its use in real-time web workflows impractical.
-
-We utilized the Sophize Markdown language to create an innovative mathematics communication interface.
-It is specially designed to aid online mathematics collaborations and can help actualize their vast latent potential.
-We believe that it can not only aid large-scale collaborations like the Polymath projects but will also be useful for private collaborations and workshops like those organized by AiM.
-
-In the future, we want to make a substantial portion of math literature embedded with structured data available at a much greater scale.
-Thus, we will improve Sophize Markdown's support for \LaTeX\space features like equation numbering, tables, and references.
-In addition, we are developing an online tool to easily extract content like definitions, theorems, proofs from math literature by automating some of the tedious tasks.
-This process will be aided by the recent supervised learning techniques \cite{ginev2019scientific} that classify scientific statements in literature.
-
-\subsection*{Sources}
-The Sophize Markdown parser and its Angular renderer source code are available under an MIT license at \url{https://github.com/Sophize/sophize-md-parser} and \url{https://github.com/Sophize/ngx-sophize-md-renderer}, respectively.
-The NPM packages for these projects are named `sophize-md-parser' and `ngx-sophize-md-renderer'.
+\todo{Sophize's limitations. In "Potential Value of a
+Digital Mathematics Library" in 2013 report.
+Sophize offers no way to more easily find analogies or weaker forms of reasoning like “If A is true, then B is true.
+B is true; therefore, A becomes more plausible.” }
 

### 2022-05-27 math_library/sophize_math.tex
For CICM'22 submission 4/X

@@
 
-\subsection{Core concepts}
+\subsection{Core Concepts}
 Sophize uses the following concepts to logically organize theoretical knowledge.
@@
 
-\subsection{Validity of arguments}
+\subsection{Validity of Arguments}
 
@@
 
-\subsection{Belief sets}
+\subsection{Belief Sets}
 \label{sec:bset}
@@
 
-\subsection{Aggregating knowledge}
+\subsection{Aggregating Knowledge}
 
@@
 
-\subsection{PGM response}
+\subsection{PGM Response}
 The response of a request to any PGM has the following components:
@@
 
-\subsection{Connection across data sources}
-\todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
-
-There is no good way to claim equivalence of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
-
-Eg. ZFC (informal) + ZFC (metamath) + Jensen's Inequality (metamath) + validity criteria (translation feels right to metamath group) $\rightarrow$ 
-Jensen's Inequality (informal)
-
-But, we can represent translations manually using arguments.
-Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
-Again, a user can choose not to accept such criteria.
-In that case, these translations will not be used in the generating proof graphs.
-
-Thus we can create proof graphs that have arguments from different languages.
-
-\subsection{Uses}
-Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
-
-Conjectural knowledge (Riemann hypothesis). 
-Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
-Proof tailored to needs. Proof graph can be easily converted to prose too.
-
 \section{Sophize Markdown}
@@
 It allows users to quickly encode and present semantic data, to show the truth status of propositions available in prose, and to effortlessly access proof graphs.
+
+With Sophize Markdown, we can easily add \LaTeX\space by enclosing it between two \$ signs (or \$\$ for display math).
 The detailed specification of Sophize Markdown is available here.
 Many of its features are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}.
-We highlight some of the salient features here.
+We highlight the prominent features here.
 
@@
 
-\subsection{Status Indicators}
+\subsection{Truth Status}
 
-For propositions, a truth-value icon indicating whether or not there is a proof is added next to the link.
+Sophize markdown adds an icon next to each proposition link.
+This icon indicates whether the proposition has been proven or dis-proven (or both) in the currently selected belief set using a check-mark or a cross.
 Clicking on the icon brings up the proof graph as shown in Figure \ref{proof_tree}.
+If the users switches from one belief set to another, the icon is updated based on the truth values in the new belief set but other parts of the article are unchanged.
+
 Similarly, an icon is added next to a proof generating machine which indicates whether the PGM is active or not.
-These options can be turned on or off depending on the input and the context.
 
@@
 
-In formal languages, definitions of terms, statements of propositions, and supporting argument text may be parseable by an external parser.
+In formal languages, definitions of terms, statements of propositions, and supporting argument text may be parse-able by an external parser.
 We can convert the externally parsed output into Markdown in such a case, where each term is automatically linked to the appropriate resource.
@@
 
-\subsection{\LaTeX\space Support}
+\section{Building a Modern Mathematics Library}
+The argument and proof graphs in help us build a network of information that spans across a wide variety of sources (including live results from PGMs).
+Using different belief sets, users can view mathematical knowledge arising from different theoretical foundations and choose what they consider to be reliable.
+With Sophize Markdown, users can easily embed semantic information, thus making it convenient to explore the network of knowledge that is being built.
+However, a few more practical issues need to be overcome to build a modern scalable library with reliable information.
 
-With Sophize Markdown, we can add \LaTeX\space by enclosing it between two \$ signs (or \$\$ for display math).
+\subsection{Semantic Data Extraction}
+Utilizing the full range of features offered by the Sophize platform requires the availability of semantic information.
+However, extracting semantic information from unstructured or semi-structured literature is a difficult problem.
+This problem can be seen as composed of several sub-problems:
+\begin{itemize}
+\item Finding definitions and propositions in prose.
+\item Associating the appropriate entity with a term used in prose for quick lookup.
+\item Identifying arguments and along with premises and conclusion.
+\item \label{prob:dup} Identifying duplicate definitions and propositions used in different sources.
+\end{itemize}
 
-The following example summarizes the specification:
-\begin{quote}
-\begin{verbatim} 
-Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of 
-happiness is what fetched $1.3 million recently. While it may not fetch many \$s, I 
-like the field equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
-\end{verbatim}
-\end{quote}
+Solving these problems would need manual effort (e.g.
+crowd-sourcing) combined with automated extraction tools.
+Recent progress in machine learning and natural language processing techniques does make this problem seem tractable.
 
-The above Markdown code is rendered as:
-\begin{mdframed}
-Einstein's most famous equation is $E=mc^2$ but it is his handwritten theory of happiness is
-what fetched \$1.3 million recently. While it may not fetch many \$s, I like the field
-equations more: $$G_{\mu \nu }+\Lambda g_{\mu \nu }=\kappa T_{\mu \nu }$$
-\end{mdframed}
+\subsubsection{}
 
-\subsection{Sophize Markdown benefits}
+\subsubsection{Connecting Across Datasets}
+The sub-problem 4 mentioned above is crucial to help make connections across datasets.
+For example, once we have identified that the `Jensen's Inequaility' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is made available to the reader of the published paper.
 
-With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
+\subsection{Search Interface}
 
-\section{Other Engineering challenges}
+\subsection{Data Management}
+Sophize organizes
+
+\subsection{Collaboration}
+
 \todo{copyright/access management}
@@
 \todo{ storing and reading data in disk/GitHub like repo }
+
+With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
+
+\subsection{Connection across data sources}
+\todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
+
+There is no good way to claim equivalence of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
+
+Eg. ZFC (informal) + ZFC (metamath) + Jensen's Inequality (metamath) + validity criteria (translation feels right to metamath group) $\rightarrow$ 
+Jensen's Inequality (informal)
+
+But, we can represent translations manually using arguments.
+Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
+Again, a user can choose not to accept such criteria.
+In that case, these translations will not be used in the generating proof graphs.
+
+Thus we can create proof graphs that have arguments from different languages.
+
+\subsection{Uses}
+Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
+
+Conjectural knowledge (Riemann hypothesis). 
+Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
+Proof tailored to needs. Proof graph can be easily converted to prose too.
+
 \subsubsection{Other Notes}

### 2022-05-27 math_library/sophize_math.tex
Latex package for CICM '22 submission

@@
-\documentclass[a4paper]{article}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.21 of 2022/01/12
+%
+\documentclass[runningheads]{llncs}
+%
+\usepackage[T1]{fontenc}
+% T1 fonts will be used to generate the final print and online PDFs,
+% so please use T1 fonts in your manuscript whenever possible.
+% Other font encondings may result in incorrect characters.
+%
 \usepackage{graphicx}
-\usepackage{onecolceurws}
-\usepackage{csquotes}
+\usepackage{mdframed}
+\usepackage[normalem]{ulem}
 \usepackage{hyperref}
-\usepackage{framed}
-\usepackage{mdframed}
-\usepackage{upquote}
-\usepackage{lmodern}
-\usepackage[normalem]{ulem}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following two lines
+% to display URLs in blue roman font according to Springer's eBook style:
+%\usepackage{color}
+\renewcommand\UrlFont{\color{blue}\rmfamily}
+%
 
 \newcommand\todo[1]{\textcolor{red}{TODO: #1}}
+\graphicspath {{../res}}
+\begin{document}
+%
+\title{Sophize Mathematics Library}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Abhishek Chugh\inst{1}\orcidID{0000-0001-6765-5229}}
+%
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Sophize Foundation, Bengaluru - 560066, India 
+\email{abc@sophize.org}
+}
+%
+\maketitle              % typeset the header of the contribution
+%
+\begin{abstract}
+Sophize is a novel mathematics library and discussion platform with a mission to help our
+users find and organize mathematical proofs. We present Sophize's novel yet familiar
+knowledge organization scheme that is used to represent a wide variety of proofs. With this
+scheme at its core, we have engineered a platform to logically aggregate knowledge from
+multiple sources. The platform curates knowledge from published research, encyclopaedias
+such as PlanetMath and Wikipedia, informal computer programs, and formal systems such as
+Metamath; and allows its users to run a federated search over them. To make this happen, two
+developments were necessary. First, we came up with the concept of 'proof-generating
+machines' and developed an open plugin architecture that allows proofs from computer
+programs to be generated as required. Second, we extended the Markdown language to represent
+the connections between mathematical objects found across various sources of knowledge. In
+addition, we also utilized this new language to create a novel communication system built
+specifically to aid mathematicians in solving problems collaboratively.
 
-\title{Sophize Knowledge Organization}
-
-\author{ Abhishek Chugh }
-
-\graphicspath {{../res}}
-
-\institution{ Sophize Foundation\\ Bengaluru, India \\ abc@sophize.org }
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-Sophize is a novel mathematics library and discussion platform with a mission to help our users find and organize mathematical proofs.
-We present Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
-With this knowledge organization scheme at its core, we have engineered a platform to aggregate knowledge from multiple sources.
-The platform meaningfully combines knowledge from published research, encyclopaedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
-To make this happen, two developments were necessary.
-First, we developed an open plugin architecture that allows proofs from computer programs to be generated as required.
-Second, we extended the Markdown language to represent the connections between between mathematical objects found across various sources of knowledge.
-In addition, we also utilized this new language to create a novel communication system built specifically to aid mathematicians in solving problems collaboratively.
-
+\keywords{Sophize \and
+knowledge organization \and
+proof-generating machine \and
+belief set \and
+metamath \and
+markdown \and
+argument graph \and
+proof graph \and
+semantic data}
 \end{abstract}
-
-\vskip 32pt
 
@@
 
-\subsubsection*{Background: The Sophize Platform}
+\subsection*{The Sophize Platform}
 
-- The goal is rational truth. Three dimensions are consistency, correspondence and values.
-
-- No hidden assumptions. Should have clear answer to every question of the form `why do you believe X'.
-
-- In its current iteration, Sophize implements consistency. Knowledge represented by manually and automated generation of arguments. Can model vast majority (almost all) of mathematics.
-
-- This gives you a way to create (consistency enforced) models.
-Next step is to see how accurately these models represent (parts of) the World.
-That involves quantifying correspondence of observations with the predictions made by the theories.
-
-- And finally, you need model individual, institutional, and societal values to claim the truth of `ought statements' like `I should wear a mask' or `Masks should be mandated'.
-
-- These starting beliefs (axioms, principles, laws, assumptions) and values are a way to model our belief systems. There are no absolutes, each belief system results in a different rational truth.
-
-\subsubsection*{Proofs in Sophize}
 Sophize is a novel mathematics library and discussion platform.
@@
 Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopaedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+
+\subsection*{Motivation}
+
+In the past couple of decades, the Internet has revolutionized our life by giving us access to seemingly unlimited information.
+Information from a wide variety of topics ranging from human medicine to rocket science is now just a few keystrokes away.
+However, even with this information we seem to having trouble understanding the complex world around us.
+In fact, dealing with the vast amounts of information thrown at us seems to be one of the primary problems of our generation.
+While we have access to a wide range of opinions on almost every topic imaginable, it has becoming increasingly difficult to decide which one to trust.
+It seems that you can find "proofs" for anything and everything we would like to believe.
+
+Thus the author's primary motivation for this project is to create a library that not just lays out all the information of the World but organizes in a way that help us make better sense of it.
+A library that helps us access justifications from a variety of viewpoints and help us collaboratively and objectively evaluate issues in the justifications or the viewpoints they arise from.
+Clearly, this is challenging goal.
+
+We begin our journey with a focus on pure Mathematics, where knowledge is objectively less complex as compared to other fields.
+In mathematics, only logically sound arguments are acceptable as justifications.
+These arguments develop from different foundational theories and logical consistency is the primary criteria of correctness for them.
+Thus, as a Mathematics library, Sophize's goal is to help our users access to mathematical proofs (chains of arguments) from a variety of foundational theories (extended to `belief sets' as described in Section \ref{sec:bset}) and help us collaboratively and objectively evaluate issues in the argument or the belief sets they arise from.
+
+With our current scheme we can incorporate almost all mathematics.
+A natural extension would be model observational data and develop criteria to quantify empirical correspondence in order to have the ability to incorporate scientific knowledge.
+But, for now we are focused on building a state-of-the-art Mathematics library that is valuable to our community.
+
+\subsection*{Proofs in Sophize}
+
+\begin{figure}[!ht]
+\begin{center}
+\fbox{\includegraphics[width=\textwidth]{proof_tree}}
+\caption{A proof displayed as a graph (tree) of arguments and propositions on the Sophize platform.}
+\label{proof_tree}
+\end{center}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\fbox{\includegraphics[height=12cm]{proof_tree}}
-\caption{A proof displayed as a graph (tree) of arguments and propositions on the Sophize platform.}
-\label{proof_tree}
-\end{center}
-\end{figure}
-
 This work can also be seen as a step towards formalizing the network of information that exists in the connections of mathematical objects.
@@
 And thus, one of the main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
-\todo{Explain and summarize the problem statement}
 
-\subsubsection*{Contribution}
-\todo{summarize sections. section 3 does X, section 4 does Y etc.}
+\subsection*{Contribution}
+In this paper, we present the novel concepts and features of Sophize Mathematics Library.
+First, we expound Sophize's scheme to build a trust-focused logical network of mathematical knowledge.
+In section \ref{sec:pgm}, we describe Sophize's proof-generating machines which are computer programs that generate proofs that integrate with Sophize's knowledge graphs.
+
+We then present some features of Sophize Markdown, an extension of the Markdown language that helps present Sophize's knowledge graphs to its users.
+It is convenient enough to be used for casual discussions of mathematical ideas over the web.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from various sources, including formal systems.
+It thus plays an integral role in the two problems that we have mentioned above.
+
+Section \ref{sec:lib} discusses some other challenges and contributions made towards making Sophize a modern mathematics library. Finally, Section \ref{sec:summary} concludes the paper.
 
@@
 Thus, for each foundational theory (`belief set' described below), we also keep track of any contradictions that arise from those foundations.
-\todo{section is crap, overview of how aggregated}
 
@@
 \subsection{Argument Graph}
-An argument can be seen as a simple graph (see Figure \ref{argument}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
+An argument can be seen as a simple graph (see Fig.~\ref{argument}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
 The edges of this graph are directed and go from (a) premise nodes to argument node and (b) argument node to conclusion node.
 
-\begin{figure}[htbp]
+\begin{figure}[!ht]
 \begin{center}
-\fbox{\includegraphics[height=3.5cm]{argument}}
+\fbox{\includegraphics[height=3cm]{argument}}
 \caption{An argument represented as a graph.}
@@
 
-A set of arguments can thus be represented as a single graph that we call an \textbf{argument graph} (Figure \ref{argument_graph}).
+A set of arguments can thus be represented as a single graph that we call an \textbf{argument graph} (Fig.~\ref{argument_graph}).
 
-\begin{figure}[htbp]
+\begin{figure}[!ht]
 \begin{center}
-\fbox{\includegraphics[height=7cm]{argument_graph}}
+\fbox{\includegraphics[height=5.5cm]{argument_graph}}
 \caption{A set of arguments forming an argument graph.}
@@
 An argument graph along with a set of set of axioms results in a \textbf{proof graph}.
-Any reachability algorithm starting with the axiom nodes is sufficient to create the proof graph (See Figure \ref{proof_graph1}).
+Any reachability algorithm starting with the axiom nodes is sufficient to create the proof graph (See Fig.~\ref{proof_graph1}).
 
-\begin{figure}[htbp]
+\begin{figure}[!ht] 
 \begin{center}
-\fbox{\includegraphics[height=7cm]{proof_graph1}}
-\caption{Proof graph from argument graph (Figure \ref{argument_graph}) using `Prop 2', `Prop 3', Prop 4' are axioms.}
+\fbox{\includegraphics[height=5.5cm]{proof_graph1}}
+\caption{Proof graph from argument graph (Fig.~\ref{argument_graph}) using `Prop 2', `Prop 3', Prop 4' are axioms.}
 \label{proof_graph1}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!ht]
 \begin{center}
-\fbox{\includegraphics[height=6cm]{proof_prop7}}
-\caption{Proof of `Prop 7' from proof graph in Figure \ref{proof_graph1} uses arguments `Arg 4' and `Arg 5'.}
+\fbox{\includegraphics[height=4cm]{proof_prop7}}
+\caption{Proof of `Prop 7' from proof graph in Fig.~\ref{proof_graph1} uses arguments `Arg 4' and `Arg 5'.}
 \label{proof_prop7}
@@
 
-Note that an argument graph combines with different sets of axioms to generate different proof graphs. The same argument may be utilized in multiple belief sets (Figure \ref{proof_graph2}).
+Note that an argument graph combines with different sets of axioms to generate different proof graphs. The same argument may be utilized in multiple belief sets (Fig.~\ref{proof_graph2}).
 
-\begin{figure}[htbp]
+\begin{figure}[!ht]
 \begin{center}
-\fbox{\includegraphics[height=8cm]{proof_graph2}}
-\caption{Proof graph from the same argument graph (Figure \ref{argument_graph}) using `Prop 1', `Prop 2', and Prop 7' as axioms.}
+\fbox{\includegraphics[height=5.5cm]{proof_graph2}}
+\caption{Proof graph from the same argument graph (Fig.~\ref{argument_graph}) using `Prop 1', `Prop 2', and Prop 7' as axioms.}
 \label{proof_graph2}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!ht]
 \begin{center}
-\fbox{\includegraphics[height=5cm]{validity_criterion}}
+\fbox{\includegraphics[height=4cm]{validity_criterion}}
 \caption{Validity criteria as an argument premise.}
@@
 
-\subsection{Aggregating Knowledge}
+\subsection{Advantages and Limitations}
+
+Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
+
+Conjectural knowledge (Riemann hypothesis). 
+Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
+Proof tailored to needs. Proof graph can be easily converted to prose too.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \begin{center}
-\fbox{\includegraphics[height=5cm]{modal}}
+\fbox{\includegraphics[width=\textwidth]{modal}}
 \caption{Modal dialog box for the term binary operation. These boxes can also have content that uses all three types of links. }
@@
 This icon indicates whether the proposition has been proven or dis-proven (or both) in the currently selected belief set using a check-mark or a cross.
-Clicking on the icon brings up the proof graph as shown in Figure \ref{proof_tree}.
+Clicking on the icon brings up the proof graph as shown in Fig.~\ref{proof_tree}.
 If the users switches from one belief set to another, the icon is updated based on the truth values in the new belief set but other parts of the article are unchanged.
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \begin{center}
-\fbox{\includegraphics[height=3cm]{formal}}
+\fbox{\includegraphics[height=2.25cm]{formal}}
 \caption{The prime number theorem written in Metamath language and rendered as Markdown in real time.}
@@
 \section{Building a Modern Mathematics Library}
+\label{sec:lib}
 The argument and proof graphs in help us build a network of information that spans across a wide variety of sources (including live results from PGMs).
@@
 
-\subsubsection{}
+\subsubsection{Connecting Across Datasets}
+The last sub-problem mentioned above is crucial to help make connections across datasets.
+For example, once we have identified that the `Jensen's Inequality' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is automatically made available to the reader of the published paper.
 
-\subsubsection{Connecting Across Datasets}
-The sub-problem 4 mentioned above is crucial to help make connections across datasets.
-For example, once we have identified that the `Jensen's Inequaility' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is made available to the reader of the published paper.
+However, figuring out if two sources are referring to the same proposition or a different version of the same proposition is often unclear.
+When working with formal systems using different languages, another related problem arises.
+There is no general way to claim equivalence of propositions across different formal systems.
+There are some projects, like Formal Harmony and theory morphisms, that are trying to understand in what sense these propositions are same and how we can translate one to another.
+But these projects are still in early stages and do not provide a general solution.
+
+However, we can utilize curated translations, such as those available from Logipedia, by representing them using arguments.
+The conclusion of such an argument is the proposition in target language and the premise would be the proposition in source language.
+For bi-directional translations two such arguments will be required.
+Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
+A user can choose not to accept such criteria.
+In that case, these translations will not be used in the generating proof graphs.
+Thus we can create proof graphs that have arguments from different languages.
+
+There are some cases where translations occur on firmer grounds, e.g., use of theory morphisms or translations of HOL-light proofs to Metamath.
+The author has not studied these cases in detail but expects that it to be possible to formulate such cross-language translations using the argument graphs.
+
+\subsection{Data Management}
+
+Sophize divides its data into groups called datasets for copyright management and data access rules.
+For example, the 'wiki' dataset that extracts knowledge from Wikipedia mathematics glossaries releases its data under `CC-BY-SA' license, whereas the `metamath' dataset is public (`CC0').
+Our signed-in users are free to create their own datasets and we allow them to choose who can read, write or comment in these datasets.
+Another interesting access control is the restriction of use of resources (especially argument-validity criteria) outside an otherwise open-to-read dataset.
+
+Information can be added to Sophize platform using intuitive web forms.
+However, it is infeasible to extract information from large repositories in this manner.
+Sophize publishes its data schema and helper libraries (explained in Section \ref{sec:core}) in multiple languages.
+The extracted information is can thus be stored as text (JSON) files in a repository.
+Sophize provides dataset owners the ability to sync knowledge such repositories to the central Sophize database.
 
 \subsection{Search Interface}
+Sophize allows its users to run a run a federated search over its resources using an Elasticsearch server.
+We allow users to search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer (See section \ref{sources} for sources) that removes spaces and lower cases the encoding.
 
-\subsection{Data Management}
-Sophize organizes
+For example the, latex formula \verb+$E = mc^2$+ is converted to \textit{Ej9rjmc9v2mMm}. 
+Note that the encoder converts spaces and new-lines into the character `j' or `J' which are removed by our Elasticsearch analyzer at the time of searching the documents.
 
@@
 
-\todo{copyright/access management}
-
-\todo{efficient computation and storage of proof graphs}
-
-\todo{ storing and reading data in disk/GitHub like repo }
-
+The Sophize platform includes an innovative mathematics communication interface designed to help
+mathematicians discuss mathematics and collaboratively discover new proofs. The design focuses on
+making the collaboration more productive and enjoyable by building the right set of technical
+tools that aid in effective organization and summarization of existing progress.
 With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
 
-\subsection{Connection across data sources}
-\todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
-
-There is no good way to claim equivalence of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
-
-Eg. ZFC (informal) + ZFC (metamath) + Jensen's Inequality (metamath) + validity criteria (translation feels right to metamath group) $\rightarrow$ 
-Jensen's Inequality (informal)
-
-But, we can represent translations manually using arguments.
-Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
-Again, a user can choose not to accept such criteria.
-In that case, these translations will not be used in the generating proof graphs.
-
-Thus we can create proof graphs that have arguments from different languages.
-
-\subsection{Uses}
-Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
-
-Conjectural knowledge (Riemann hypothesis). 
-Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
-Proof tailored to needs. Proof graph can be easily converted to prose too.
-
-\subsubsection{Other Notes}
+\section{Conclusion}
+\label{sec:conclusion}
 \todo{What criteria are met based on the 2013 report}
@@
 
-\bibliographystyle{alpha}
+\subsubsection{Acknowledgements} 
+A part of the research presented here was supported by the International Mathematical Union.
 
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
 \bibliography{mybib}
-
 \end{document}

### 2022-05-27 math_library/sophize_math.tex
For CICM '22 submission - 5/X

--- 2022-05-27 math_library/sophize_math.tex
@@
 
-\title{Sophize Knowledge Organization}
+\title{Sophize Mathematics Library}
 
@@
 
-\subsubsection*{Background: The Sophize Platform}
+\subsubsection*{The Sophize Platform}
+
+Sophize is a novel mathematics library and discussion platform.
+The author has developed the platform over the course of the last two years at \url{https://sophize.org}.
+Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
+We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+
+\subsubsection*{Motivation}
+
+In the past couple of decades, the Internet has revolutionized our life by giving us access to seemingly unlimited information.
+Information from a wide variety of topics ranging from human medicine to rocket science is now just a few keystrokes away.
+However, even with this information we seem to having trouble understanding the complex world around us.
+In fact, dealing with the vast amounts of information thrown at us seems to be one of the primary problems of our generation.
+While we have access to a wide range of opinions on almost every topic imaginable, it has becoming increasingly difficult to decide which one to trust.
+It seems that you can find "proofs" for anything and everything we would like to believe.
+
+Thus the author's primary motivation for this project is to create a library that not just lays out all the information of the World but organizes in a way that help us make better sense of it.
+A library that helps us access justifications from a variety of viewpoints and help us collaboratively and objectively evaluate issues in the justifications or the viewpoints they arise from.
+Clearly, this is challenging goal.
+
+We begin our journey with a focus on pure Mathematics, where knowledge is objectively less complex as compared to other fields.
+In mathematics, only logically sound arguments are acceptable as justifications.
+These arguments develop from different foundational theories and logical contradictions are the primary .
+Thus, as a Mathematics library Sophize's goal is to help our users access to mathematical proofs (chains of arguments) from a variety of foundational theories (extended to 'belief sets' as described in Section \ref{sec:bset}) and help us collaboratively and objectively evaluate issues in the argument or the belief sets they arise from.
 
@@
 \subsubsection*{Contribution}
-\todo{summarize sections. section 3 does X, section 4 does Y etc.}
+In this paper, we present the features\todo{x} of Sophize Mathematics Library.
+First, we expound \todo{x} Sophize's scheme to build a trust-focused logical network of mathematical knowledge.
+In section \ref{sec:pgm}, we describe Sophize's proof-generating machines which are computer programs that generate proofs that integrate with Sophize's knowledge graphs.
+
+We then present some features of Sophize Markdown, an extension of the Markdown language that is helps present Sophize's knowledge graphs to its users.
+It is convenient enough to be used for casual discussions of mathematical ideas over the web.
+It is also powerful enough to embed mathematical entities such as definitions, theorems, and proofs from various sources, including formal systems.
+It thus plays an integral role in the two problems that we have mentioned above.
+
+Section \ref{sec:lib} discusses some other challenges and contributions made towards making Sophize a modern mathematics library. Finally, Section \ref{sec:summary} concludes the paper.
+
+\subsection*{Acknowledgements}
+A part of the research presented here was supported by the International Mathematical Union.
 
@@
 
-\subsubsection{}
-
 \subsubsection{Connecting Across Datasets}
 The sub-problem 4 mentioned above is crucial to help make connections across datasets.
-For example, once we have identified that the `Jensen's Inequaility' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is made available to the reader of the published paper.
+For example, once we have identified that the `Jensen's Inequality' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is automatically made available to the reader of the published paper.
+
+However, figuring out if two sources are referring to the same proposition or a different version of the same proposition is often unclear.
+When working with formal systems using different languages, another related problem arises.
+There is no general way to claim equivalence of propositions across different formal systems.
+There are some projects, like Formal Harmony and theory morphisms, that are trying to understand in what sense these propositions are same and how we can translate one to another.
+But these projects are still in early stages and do not provide a general solution.
+
+However, we can utilize curated translations, such as those available from Logipedia, by representing them using arguments.
+The conclusion of such an argument is the proposition in target language and the premise would be the proposition in source language.
+For bi-directional translations two such arguments will be required.
+Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
+A user can choose not to accept such criteria.
+In that case, these translations will not be used in the generating proof graphs.
+Thus we can create proof graphs that have arguments from different languages.
+
+There are some cases where translations occur on firmer grounds, e.g., use of theory morphisms or translations of HOL-light proofs to Metamath.
+The author has not studied these cases in detail but expects that it to be possible to formulate such cross-language translations using the argument graphs.
+
+\subsection{Data Management}
+
+Sophize divides its data into groups called datasets for copyright management and data access rules.
+For example, the 'wiki' dataset that extracts knowledge from Wikipedia mathematics glossaries releases its data under `CC-BY-SA' license, whereas the `metamath' dataset is public (`CC0').
+Our signed-in users are free to create their own datasets and we allow them to choose who can read, write or comment in these datasets.
+
+Information can be added to Sophize platform using intuitive web forms.
+However, it is infeasible to extract information from large repositories in this manner.
+Sophize publishes its data schema and helper libraries (explained in Section \ref{sec:core}) in multiple languages.
+The extracted information is can thus be stored as text (JSON) files in a repository.
+Sophize provides dataset owners the ability to sync knowledge such repositories to the central Sophize database.
 
 \subsection{Search Interface}
+Sophize allows its users to run a run a federated search over its resources using an Elasticsearch server.
+We allow users to search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer (See section \ref{sources} for sources) that removes spaces and lower cases the encoding.
 
-\subsection{Data Management}
-Sophize organizes
+For example the, latex formula \verb+$E = mc^2$+ is converted to \textit{Ej9rjmc9v2mMm}. 
+Note that the encoder converts spaces and new-lines into the character `j' or `J' which are removed by our Elasticsearch analyzer at the time of searching the documents.
 
@@
 
-\todo{copyright/access management}
-
-\todo{efficient computation and storage of proof graphs}
-
-\todo{ storing and reading data in disk/GitHub like repo }
-
+The Sophize platform includes an innovative mathematics communication interface designed to help
+mathematicians discuss mathematics and collaboratively discover new proofs. The design focuses on
+making the collaboration more productive and enjoyable by building the right set of technical
+tools that aid in effective organization and summarization of existing progress.
 With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
-
-\subsection{Connection across data sources}
-\todo{What are Translations? (informal to formal, formal to other formal), Why do we need translations?}
-
-There is no good way to claim equivalence of propositions across different formal systems. [Formal Harmony still in infancy, theory morphisms aren't yet practical].
-
-Eg. ZFC (informal) + ZFC (metamath) + Jensen's Inequality (metamath) + validity criteria (translation feels right to metamath group) $\rightarrow$ 
-Jensen's Inequality (informal)
-
-But, we can represent translations manually using arguments.
-Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
-Again, a user can choose not to accept such criteria.
-In that case, these translations will not be used in the generating proof graphs.
-
-Thus we can create proof graphs that have arguments from different languages.
-
-\subsection{Uses}
-Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
-
-Conjectural knowledge (Riemann hypothesis). 
-Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
-Proof tailored to needs. Proof graph can be easily converted to prose too.
 

### 2022-05-27 math_library/sophize_math.tex
Minor fixes

@@
 We present Sophize's novel yet familiar knowledge organization scheme that is used to represent a wide variety proofs.
-With this knowledge organization scheme at its core, we have engineered a platform to aggregate knowledge from multiple sources.
-The platform meaningfully combines knowledge from published research, encyclopaedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
+With this scheme at its core, we have engineered a platform to logically aggregate knowledge from multiple sources.
+The platform curates knowledge from published research, encyclopaedias such as PlanetMath and Wikipedia, informal computer programs and formal systems such as Metamath; and allows its users to run a federated search over them.
 To make this happen, two developments were necessary.
-First, we developed an open plugin architecture that allows proofs from computer programs to be generated as required.
+First, we came up with concept of 'proof-generating machines' and developed an open plugin architecture that allows proofs from computer programs to be generated as required.
 Second, we extended the Markdown language to represent the connections between between mathematical objects found across various sources of knowledge.
@@
 In mathematics, only logically sound arguments are acceptable as justifications.
-These arguments develop from different foundational theories and logical contradictions are the primary .
-Thus, as a Mathematics library Sophize's goal is to help our users access to mathematical proofs (chains of arguments) from a variety of foundational theories (extended to 'belief sets' as described in Section \ref{sec:bset}) and help us collaboratively and objectively evaluate issues in the argument or the belief sets they arise from.
+These arguments develop from different foundational theories and logical consistency is the primary criteria of correctness for them.
+Thus, as a Mathematics library, Sophize's goal is to help our users access to mathematical proofs (chains of arguments) from a variety of foundational theories (extended to `belief sets' as described in Section \ref{sec:bset}) and help us collaboratively and objectively evaluate issues in the argument or the belief sets they arise from.
 
-- The goal is rational truth. Three dimensions are consistency, correspondence and values.
-
-- No hidden assumptions. Should have clear answer to every question of the form `why do you believe X'.
-
-- In its current iteration, Sophize implements consistency. Knowledge represented by manually and automated generation of arguments. Can model vast majority (almost all) of mathematics.
-
-- This gives you a way to create (consistency enforced) models.
-Next step is to see how accurately these models represent (parts of) the World.
-That involves quantifying correspondence of observations with the predictions made by the theories.
-
-- And finally, you need model individual, institutional, and societal values to claim the truth of `ought statements' like `I should wear a mask' or `Masks should be mandated'.
-
-- These starting beliefs (axioms, principles, laws, assumptions) and values are a way to model our belief systems. There are no absolutes, each belief system results in a different rational truth.
+With our current scheme we can incorporate almost all mathematics.
+A natural extension would be model observational data and develop criteria to quantify empirical correspondence in order to have the ability to incorporate scientific knowledge.
+But, for now we are focused on building a state-of-the-art Mathematics library that is valuable to our community.
 
 \subsubsection*{Proofs in Sophize}
-Sophize is a novel mathematics library and discussion platform.
-The author has developed the platform over the course of the last two years at \url{https://sophize.org}.
-Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopaedia, Wikipedia, and the Metamath formal system \cite{metamath}.
-
 Mathematical proofs are based on a variety of foundations such as ZFC, intuitionistic logic, and type theory.
@@
 And thus, one of the main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
-\todo{Explain and summarize the problem statement}
 
 \subsubsection*{Contribution}
-In this paper, we present the features\todo{x} of Sophize Mathematics Library.
-First, we expound \todo{x} Sophize's scheme to build a trust-focused logical network of mathematical knowledge.
+In this paper, we present the novel concepts and features of Sophize Mathematics Library.
+First, we expound Sophize's scheme to build a trust-focused logical network of mathematical knowledge.
 In section \ref{sec:pgm}, we describe Sophize's proof-generating machines which are computer programs that generate proofs that integrate with Sophize's knowledge graphs.
 
-We then present some features of Sophize Markdown, an extension of the Markdown language that is helps present Sophize's knowledge graphs to its users.
+We then present some features of Sophize Markdown, an extension of the Markdown language that helps present Sophize's knowledge graphs to its users.
 It is convenient enough to be used for casual discussions of mathematical ideas over the web.
@@
 Our signed-in users are free to create their own datasets and we allow them to choose who can read, write or comment in these datasets.
+Another interesting access control is the restriction of use of resources (especially argument-validity criteria) outside an otherwise open-to-read dataset.
 
@@
 
-\subsubsection{Other Notes}
+\section{Conclusion}
+\label{sec:conclusion}
 \todo{What criteria are met based on the 2013 report}

### 2022-05-27 math_library/sophize_math.tex
CICM '22 1st submitted version

--- 2022-05-27 math_library/sophize_math.tex
@@
 
-\subsection*{The Sophize Platform}
+\subsection{The Sophize Platform}
 
-Sophize is a novel mathematics library and discussion platform.
-The author has developed the platform over the course of the last two years at \url{https://sophize.org}.
-Sophize's primary mission is to help users find existing proofs of mathematical statements, to discover new proofs, and to utilize this knowledge in their work.
-We combine knowledge from multiple resources and have accumulated thousands of definitions, theorems, and proofs from a wide variety of sources, including some published research, the PlanetMath encyclopedia, Wikipedia, and the Metamath formal system \cite{metamath}.
+Sophize is a novel mathematics library and discussion platform. The author has developed the
+platform over the course of the last few years at \url{https://sophize.org}. Sophize's
+primary mission is to help users find existing proofs of mathematical statements, to
+discover new proofs, and to utilize this knowledge in their work. We combine knowledge from
+multiple resources and have accumulated thousands of definitions, theorems, and proofs from
+a wide variety of sources, including some published research, the PlanetMath encyclopedia,
+Wikipedia, and the Metamath formal system \cite{metamath}.
 
-\subsection*{Motivation}
+\subsection{Motivation}
 
-In the past couple of decades, the Internet has revolutionized our life by giving us access to seemingly unlimited information.
-Information from a wide variety of topics ranging from human medicine to rocket science is now just a few keystrokes away.
-However, even with this information we seem to having trouble understanding the complex world around us.
-In fact, dealing with the vast amounts of information thrown at us seems to be one of the primary problems of our generation.
-While we have access to a wide range of opinions on almost every topic imaginable, it has becoming increasingly difficult to decide which one to trust.
-It seems that you can find "proofs" for anything and everything we would like to believe.
+In the past couple of decades, the Internet has revolutionized our life by giving us access
+to seemingly unlimited information. Information from a wide variety of topics ranging from
+human medicine to rocket science is now just a few keystrokes away. However, it seems
+that we are having even more trouble making sense of the World around us.
+In fact, dealing with the vast amounts of information thrown at us seems to be one of the most important problems of our generation.
+While we have access to a wide range of opinions on almost every topic imaginable, it has become increasingly difficult to decide which one to trust.
+It
+seems that we can find "proofs" for anything and everything we would like to believe.
 
-Thus the author's primary motivation for this project is to create a library that not just lays out all the information of the World but organizes in a way that help us make better sense of it.
-A library that helps us access justifications from a variety of viewpoints and help us collaboratively and objectively evaluate issues in the justifications or the viewpoints they arise from.
-Clearly, this is challenging goal.
+Thus the author's primary motivation for this project is to create a library that not just
+lays out all the information about the World but organizes it in a way that helps us make
+better sense of it. A library that helps us access justifications from a variety of
+viewpoints and allows us to collaboratively and objectively evaluate issues in the
+justifications or the viewpoints they arise from. Clearly, this is a challenging goal.
 
-We begin our journey with a focus on pure Mathematics, where knowledge is objectively less complex as compared to other fields.
-In mathematics, only logically sound arguments are acceptable as justifications.
-These arguments develop from different foundational theories and logical consistency is the primary criteria of correctness for them.
-Thus, as a Mathematics library, Sophize's goal is to help our users access to mathematical proofs (chains of arguments) from a variety of foundational theories (extended to `belief sets' as described in Section \ref{sec:bset}) and help us collaboratively and objectively evaluate issues in the argument or the belief sets they arise from.
+We begin our journey with a focus on pure Mathematics, where knowledge is objectively less
+complex as compared to other fields. In mathematics, only logically sound arguments are
+acceptable as justifications. These arguments develop in different foundational theories;
+and logical consistency is the primary criterion of correctness. Thus, as a
+Mathematics library, Sophize's goal is to help our users access mathematical proofs (arguments) from a variety of belief sets (roughly - foundational theories along with indicators of trust in knowledge sources) and allow our users to collaboratively and objectively evaluate issues in the arguments or the belief sets they developed in.
 
-With our current scheme we can incorporate almost all mathematics.
-A natural extension would be model observational data and develop criteria to quantify empirical correspondence in order to have the ability to incorporate scientific knowledge.
-But, for now we are focused on building a state-of-the-art Mathematics library that is valuable to our community.
+With our current scheme, we can incorporate nearly all mathematics. A natural extension
+would be to model observational data and develop criteria to quantify empirical
+correspondence in order to have the ability to incorporate scientific knowledge. But, for
+now, we are focused on developing a state-of-the-art library for the Mathematics community.
 
-\subsection*{Proofs in Sophize}
+\subsection{Proofs in Sophize}
+\label{sec:sophize_proofs}
 
@@
 \begin{center}
-\fbox{\includegraphics[width=\textwidth]{proof_tree}}
+\fbox{\includegraphics[height=8.25cm]{proof_tree}}
 \caption{A proof displayed as a graph (tree) of arguments and propositions on the Sophize platform.}
@@
 The committee on planning a global library of the mathematical sciences recognized that this network is largely unexplored, and formalizing it has tremendous potential to accelerate math research \cite{sciences2014developing}.
+Hence, we required novel techniques to connect mathematical entities from such a wide range of formal and informal knowledge sources.
 
-Hence, we required novel knowledge organization techniques to connect mathematical entities from such a wide range of formal and informal knowledge sources.
-And thus, one of the main challenges towards building the Sophize platform was to create a simple way to embed mathematical entities on the web.
-
-\subsection*{Contribution}
+\subsection{Contribution}
 In this paper, we present the novel concepts and features of Sophize Mathematics Library.
@@
 
-Section \ref{sec:lib} discusses some other challenges and contributions made towards making Sophize a modern mathematics library. Finally, Section \ref{sec:summary} concludes the paper.
+Section \ref{sec:lib} discusses some other challenges and contributions made towards making Sophize a modern mathematics library. Finally, Section \ref{sec:conclusion} concludes the paper.
 
@@
 At its core, Sophize's approach is to simply keep track of all arguments in favour or against any proposition.
-Use of some form of arguments is the common factor amongst all mathematical (and perhaps all scientific) knowledge.
+The use of some form of arguments is the common factor amongst all mathematical (and perhaps most scientific) knowledge.
 We use this fact to unify knowledge from multiple sources in a meaningful way as described below.
@@
 We use the set of all known arguments to track knowledge from a variety of foundational theories.
-For theoretical knowledge, i.e., knowledge that doesn't involve empirical data, the primary criteria of validity is internal (logical) consistency.
+For theoretical knowledge, i.e., the knowledge that doesn't involve empirical data, the primary criterion of validity is internal (logical) consistency.
 Thus, for each foundational theory (`belief set' described below), we also keep track of any contradictions that arise from those foundations.
@@
 \subsection{Core Concepts}
-Sophize uses the following concepts to logically organize theoretical knowledge.
+\label{sec:core}
+Sophize uses the following concepts to logically organize theoretical knowledge. The datamodel for these concepts is published in JSON schema \cite{sophize_datamodel}.
 
@@
 Each resource has a URI and contains fields such as search tags and citations.}
-
+\paragraph{}
 A \textbf{URI} consists of two parts: a namespace-like identifier called its dataset-id, which indicates the data source, and a resource-id that specifies the resource type and its unique name in the data source.
@@
 \paragraph{An \textbf{argument} is a set of propositions called premises along with a concluding proposition that is claimed to follow from the premises.
-In addition, most arguments include supporting text that explains how the conclusion follows from the premises.
-A proof is seen here as a directed graph of arguments and propositions.}
+In addition, most arguments include supporting text that explains how the conclusion follows from the premises.}
 
-\paragraph{A \textbf{belief set} is roughly the set of axiomatic propositions that make up the foundations of a theory. Belief sets will be described in more detail in subsection \ref{sec:bset}.}
+\paragraph{A \textbf{belief set} is roughly the set of axiomatic propositions that make up the foundations of a theory. Belief sets will be described in subsection \ref{sec:bset}.}
 
-\paragraph{Loosely defined, a \textbf{proof-generating machine} (PGM) is a computer program that generates the proof for an input proposition.
-PGMs are described in more detail in section \ref{sec:pgm}.}
+\paragraph{Loosely defined, a \textbf{proof-generating machine} (PGM) is a computer program that generates proofs for an input proposition on-the-fly.
+PGMs are described in detail in section \ref{sec:pgm}.}
 
 \subsection{Argument Graph}
-An argument can be seen as a simple graph (see Fig.~\ref{argument}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
+An argument can be seen as a simple graph (see Fig.~\ref{argument_graph}) with two types of nodes - (a) a single node representing the argument itself and (b) a set of proposition nodes representing the argument's conclusion and premises.
 The edges of this graph are directed and go from (a) premise nodes to argument node and (b) argument node to conclusion node.
+A set of arguments can thus be represented as a single graph that we call an \textbf{argument graph}.
 
@@
 \begin{center}
-\fbox{\includegraphics[height=3cm]{argument}}
-\caption{An argument represented as a graph.}
-\label{argument}
-\end{center}
-\end{figure}
-
-A set of arguments can thus be represented as a single graph that we call an \textbf{argument graph} (Fig.~\ref{argument_graph}).
-
-\begin{figure}[!ht]
-\begin{center}
-\fbox{\includegraphics[height=5.5cm]{argument_graph}}
-\caption{A set of arguments forming an argument graph.}
+\fbox{\includegraphics[width=\textwidth]{argument_graph}}
+\caption{An argument represented as a graph (left). A set of arguments forming an argument graph (right).}
 \label{argument_graph}
@@
 \subsection{Generating Proof Graphs}
-An argument graph along with a set of set of axioms results in a \textbf{proof graph}.
-Any reachability algorithm starting with the axiom nodes is sufficient to create the proof graph (See Fig.~\ref{proof_graph1}).
+A \textbf{proof graph} is a directed acyclic graph and contains complete proofs (including all alternate proofs) for all its propositions.
+A proof graph can be generated from an argument graph by starting with the axiom nodes and finding all nodes that can be reached from them (See Fig.~\ref{proof_graph1}).
 
@@
 \begin{center}
-\fbox{\includegraphics[height=5.5cm]{proof_graph1}}
-\caption{Proof graph from argument graph (Fig.~\ref{argument_graph}) using `Prop 2', `Prop 3', Prop 4' are axioms.}
+\fbox{\includegraphics[height=5cm]{proof_graph1}}
+\caption{Proof graph from argument graph (Fig.~\ref{argument_graph}) using `Prop 2', `Prop 3', Prop 4' as axioms.}
 \label{proof_graph1}
@@
 
-A proof graph is a directed acyclic graph and contains complete proofs (including all alternate proofs) for all its propositions.
-
 \begin{figure}[!ht]
@@
 \fbox{\includegraphics[height=4cm]{proof_prop7}}
-\caption{Proof of `Prop 7' from proof graph in Fig.~\ref{proof_graph1} uses arguments `Arg 4' and `Arg 5'.}
+\caption{Proof of `Prop 7' from proof graph in Fig.~\ref{proof_graph1} uses `Arg 4' and `Arg 5'.}
 \label{proof_prop7}
@@
 
-Note that an argument graph combines with different sets of axioms to generate different proof graphs. The same argument may be utilized in multiple belief sets (Fig.~\ref{proof_graph2}).
+Note that an argument graph combines with different sets of axioms to generate different proof graphs. The same argument may be utilized in multiple proof graphs (Fig.~\ref{proof_graph2}).
 
@@
 \begin{center}
-\fbox{\includegraphics[height=5.5cm]{proof_graph2}}
+\fbox{\includegraphics[height=5cm]{proof_graph2}}
 \caption{Proof graph from the same argument graph (Fig.~\ref{argument_graph}) using `Prop 1', `Prop 2', and Prop 7' as axioms.}
@@
 The validity of an argument is, in principle, independent of other arguments and objectively verifiable.
-Formally defined logistic systems indeed have a mechanical procedure to independently verify validity of arguments.
+Formally defined logistic systems indeed have a mechanical procedure to independently verify the validity of arguments.
 
 However, only a small section of Mathematics is developed using formally verified arguments.
-Vast majority of mathematics is verified via peer review, some of this knowledge is curated by experts in books, encyclopaedias.
-The claim of validity of proofs (arguments) is judged based on the various parameters such as academic standing of the claimant, reputation of the peer reviewing journal, the history of errors of the book or encyclopaedia containing them, etc.
-Clearly, these criteria are subjective and each individual's criteria of accepting validity of an argument can vary to some extent.
+The vast majority of mathematics is verified via peer review, and some of this knowledge is curated by experts in books, encyclopaedias.
+The claim of validity of proofs (arguments) is judged based on various parameters such as the academic standing of the claimant, the reputation of the peer reviewing journal, the history of errors in the book or encyclopaedia containing them, etc.
+Clearly, these criteria are subjective and each individual's criteria for accepting the validity of an argument can vary to some extent.
 
@@
 \begin{center}
-\fbox{\includegraphics[height=4cm]{validity_criterion}}
+\fbox{\includegraphics[height=3cm]{validity_criterion}}
 \caption{Validity criteria as an argument premise.}
@@
 
-To easily manage validity criteria, the relationships between validity criteria are also maintained in the argument graph using argument-like dependency graphs.
-Eg.
-"Published in journal with SJR score $>$ 0.67" $\rightarrow$ "Published in Annals of Mathematics".
-By maintaining relationships like above, Sophize allows its users to conveniently choose multiple sources they consider to be reliable with a single manually chosen criterion.
+To easily manage validity criteria, the relationships between validity criteria are also maintained in the argument graph using arguments such as "Published in journal with SJR score $>$ 0.67" $\rightarrow$ "Published in Annals of Mathematics" (validation criterion should be provided for such arguments too).
+By maintaining such relationships, Sophize allows its users to conveniently choose multiple sources they consider to be reliable with a single manually chosen criterion.
 
@@
 Of course, this means that we need to start with some propositions that are assumed to be true without further justification.
-Traditionally, these are mathematical axioms and are considered to self-evidently true.
-In mathematical inquiry, theorems are proven/disproven in one or more multiple theories, each with its own set of axioms.
-Each theory may have its theoretical advantages and practical uses and there are no universal basis to choose one theory over another when trying to assert a proposition's truth/falsity.
+Traditionally, these are mathematical axioms and are considered to be self-evidently true.
+In mathematical inquiry, theorems are proven/disproven in one or more theories, each with its own set of axioms.
+Each theory may have its theoretical advantages and practical uses and there is no universal basis to choose one theory over another when trying to assert a proposition's truth/falsity.
 
-Thus, Sophize allows any set of propositions to be considered true without evidence.
+Sophize allows any set of propositions to be considered true without evidence.
 Such a set of propositions is called a \textbf{belief set}.
@@
 
-The truth-value of a proposition is only defined within a belief set - there is no notion of of absolute or universal truth. Sophize creates proof graphs for all its belief sets.
+The truth-value of a proposition is only defined within a belief set - there is no notion of absolute or universal truth on the Sophize platform.
+Sophize maintains proof graphs for all its belief sets.
 
@@
 
-\subsection{Advantages and Limitations}
+\subsection{Potential Advantages}
 
-Efficiently modelling different axiomatic systems that have a large overlap of arguments(eg. euclidean/parabolic/hyperbolic geometry, ZF/ZFC etc)
+Logical organization of mathematics can lead to many advantages. We list some interesting ones below.
 
-Conjectural knowledge (Riemann hypothesis). 
-Practical utility of conjectural knowledge - eg. a lot of information security systems assume "P is not NP"
-Proof tailored to needs. Proof graph can be easily converted to prose too.
+This knowledge organization scheme facilitates the re-use of propositions, and arguments across different theories.
+For example, to organize knowledge of different constant-curve geometries, we would create 4 belief sets - one each for absolute, Euclidean, hyperbolic and elliptic geometries.
+The latter three belief sets would comprise the absolute geometry belief set and the appropriate version of the parallel postulate needed for them.
+In such a scheme all the arguments (proofs) added to the argument graph for absolute geometry would automatically be shared by the other three geometries.
+The other three geometries need to only add the arguments that utilize their version of the parallel postulate.
+
+Another use case would be to understand the consequences of important conjectures like the Reimann hypothesis by creating two belief sets - one where the conjecture is true and one where it is false.
+The proof graphs would systematically store such conjectural knowledge which often gets lost especially when results from multiple conjectures are involved.
+Complexity theory is one such field where this need is quite apparent.
+On a more practical note, several information security systems build on the conjectural developed with the assumption $P \neq NP$.
+
+Proof graphs are currently organized as trees as seen in Fig \ref{proof_tree}.
+Users can keep exploring the proof till they reach a point where the propositions are already familiar to them.
+A future application of proof graphs would be to generate narrative proofs based on tailored to the reader's current understanding.
+This could be achieved in a classroom setting where the current level of mathematical understanding of students is known or assumed.
+It may also be possible to infer this from the user's activity on the platform.
+
+\subsection{Limitations}
+The scheme described in this section has a semantic notion of negation of a proposition to track contradictions.
+Thus it is incapable of organizing knowledge that depends on more complex calculi such as many-valued logics.
 
@@
 With Sophize, the focus instead is to generate proofs of the input propositions.
-A \textbf{Proof-generating machine} (PGM for short) is a computer program that generates a partial proof graph against or in favour of an argument.
+A \textbf{proof-generating machine} (PGM) is a computer program that generates a partial proof graph against or in favour of an argument.
 PGMs can also have the capability to perform tasks 1 and 2, mentioned above.
@@
 One server can implement multiple PGMs.
+An overview of PGMs generating Metamath proofs is here: \url{https://youtu.be/hJtEIo3ioLM}
 
@@
 These PGMs must also be specified.
+Similar to argument validation criterion, each PGM should also have premise indicating PGM's correctness criteria (e.g.
+tested by X, verified by some committee, another program etc.)
 
@@
 \item all of its premises are true in the belief set.
-\item all the PGMs it delegates-to are active.
+\item all the PGMs it delegates-to are active in the belief set.
 \end{enumerate}
 
-If the PGM returns a proof graph that utilizes As with an argument, one or more premises is used to indicate the validity of the PGM (Eg.
-tested by X, verified by some committee, another program etc).
-Thus, to be considered active in a belief set, the PGM must have a verification criteria that matches the belief set's requirements.
 The output of a PGM is not used in belief sets in which it is not active.
@@
 \item Truth value, i.e., whether the PGM considers the input proposition (provided or computed) true or false.
-PGM can also indicate that it doesn't understand the input or prove/disprove the proposition.
+PGM can also indicate that it doesn't understand the input or can't prove/disprove the proposition.
 
@@
 \item Arguments whose the premises are limited to the premises of the PGM.
-\item Special `Arguments' that indicate that the generation of the remaining proof must be delegated to another PGM.
-In case of large proofs, a PGM may also delegate to itself after generating some (say 100) arguments.
+\item Special `Arguments' that indicate that the generation of the proof of this argument's conclusion must be delegated to another PGM.
+To paginate large proofs, a PGM may also delegate to itself after generating some (say 100) arguments.
 \end{enumerate}
@@
 However, the presentation of proofs as graphs to users is perhaps not very convenient.
-Traditional text based narration remains indispensable when presenting knowledge to the reader.
+Traditional text-based narration remains indispensable when presenting knowledge to the reader.
 
@@
 With Sophize Markdown, we can easily add \LaTeX\space by enclosing it between two \$ signs (or \$\$ for display math).
-The detailed specification of Sophize Markdown is available here.
-Many of its features are demonstrated at: \url{https://youtu.be/5UYOpQwcjCk}.
-We highlight the prominent features here.
+A detailed specification of Sophize Markdown is available \cite{EasyChair6207} and many of its features are demonstrated at \url{https://youtu.be/5UYOpQwcjCk}.
+We highlight relevant features here:
 
-\subsection{Embedding semantic data}
+\subsection{Embedding Semantic Data}
 
@@
 Links can be added using the pound sign (\#) and the resource's URI.
-There are multiple resource link options that can be used for changing the behavior and text of the resource link.
-The following examples demonstrate these options.
+There are multiple resource link options that can be used for changing the behaviour and text of the resource link.
+The following example utilizes some of the options.
 
-\subsubsection*{Example 1}
-\begin{verbatim}
-#P_cosine_law|UC generalizes the #P_pythagorean for all kinds of #(T_triangle, 'triangles').
-\end{verbatim}
-
-\paragraph{The above code is rendered as:}
-\begin{mdframed}
-\dashuline{Law of cosines} generalizes the \dashuline{Pythagorean theorem} for all kinds of \dashuline{triangles}.
-\end{mdframed}
-
-The link options 'UC/LC' makes the link text upper-cased or lower-cased.
-
-\subsubsection*{Example 2}
-\begin{verbatim}
-#T_matrix_multiplication|NO_LINK is a #(T_commutative_property, 'non-commutative'|NAV_LINK)
-#T_binary_operation.
-\end{verbatim}
-
-\paragraph{The above code is rendered as:}
-\begin{mdframed}
-Matrix multiplication is a \underline{non-commutative} \dashuline{binary operation.}
-\end{mdframed}
-This example shows the various link behaviours.
-The first element shows `\#wiki/T\_matrix\_multiplication' on mouse-hover.
-The second link navigates the page to a different URL.
-Clicking on the third link pops up a modal dialog box like so:
-
-\begin{figure}
-\begin{center}
-\fbox{\includegraphics[width=\textwidth]{modal}}
-\caption{Modal dialog box for the term binary operation. These boxes can also have content that uses all three types of links. }
-\label{modal}
-\end{center}
-\end{figure}
-
-\subsubsection*{Example 3}
+\subsubsection*{Sample Markdown Code}
 
@@
 
-A conic section (or simply conic) is a curve obtained as the intersection of the
-surface of a #wiki/T_cone with a #wiki/T_plane. There are three types of conic sections.
+A conic section is a curve obtained as the intersection of the 
+#(wiki/T_conical_surface, 'surface') of a #wiki/T_cone with a 
+#wiki/T_plane. There are three types of conic sections.
 
@@
 \section*{Conic Section}
-A conic section (or simply conic) is a curve obtained as the intersection of the surface of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
+A conic section is a curve obtained as the intersection of the surface of a \dashuline{cone} with a \dashuline{plane}. There are three types of conic sections.
 
@@
 Thus we were able to easily re-use concepts and theorems already extracted from other sources (say, Wikipedia and the Oxford dictionary in this case).
+Clicking on the underlined concepts, pops-up a modal dialog with the definition of the term clicked.
 
@@
 
-Sophize markdown adds an icon next to each proposition link.
-This icon indicates whether the proposition has been proven or dis-proven (or both) in the currently selected belief set using a check-mark or a cross.
+When a belief set is chosen, Sophize markdown adds an icon next to each proposition link.
+This icon indicates whether the proposition has been proven or dis-proven (or both) in the currently selected belief set using an appropriate symbol such as a check-mark or a cross.
 Clicking on the icon brings up the proof graph as shown in Fig.~\ref{proof_tree}.
 If the users switches from one belief set to another, the icon is updated based on the truth values in the new belief set but other parts of the article are unchanged.
-
+This functionality is demonstrated in the demo in subsection \ref{sec:sophize_proofs}.
 Similarly, an icon is added next to a proof generating machine which indicates whether the PGM is active or not.
@@
 \subsection{Formal Language Support}
-
-In formal languages, definitions of terms, statements of propositions, and supporting argument text may be parse-able by an external parser.
-We can convert the externally parsed output into Markdown in such a case, where each term is automatically linked to the appropriate resource.
+In the case of formal languages, when propositions can be fully parsed, Sophize can automatically attach links to appropriate resources.
 This provides a convenient interface, where the user types in the native language, and the final output automatically allows users to explore all concepts that make up the input statement in depth.
@@
 
-\begin{figure}
-\begin{center}
-\fbox{\includegraphics[height=2.25cm]{formal}}
-\caption{The prime number theorem written in Metamath language and rendered as Markdown in real time.}
-\label{formal}
-\end{center}
-\end{figure}
-
 \section{Building a Modern Mathematics Library}
 \label{sec:lib}
-The argument and proof graphs in help us build a network of information that spans across a wide variety of sources (including live results from PGMs).
-Using different belief sets, users can view mathematical knowledge arising from different theoretical foundations and choose what they consider to be reliable.
-With Sophize Markdown, users can easily embed semantic information, thus making it convenient to explore the network of knowledge that is being built.
-However, a few more practical issues need to be overcome to build a modern scalable library with reliable information.
+This sections discusses a some practical issues need to be overcome to build a modern scalable library with reliable information.
 
@@
 \item Associating the appropriate entity with a term used in prose for quick lookup.
-\item Identifying arguments and along with premises and conclusion.
+\item Identifying arguments along with premises and conclusion.
 \item \label{prob:dup} Identifying duplicate definitions and propositions used in different sources.
@@
 
-Solving these problems would need manual effort (e.g.
+Solving these problems would require manual effort (e.g.
 crowd-sourcing) combined with automated extraction tools.
-Recent progress in machine learning and natural language processing techniques does make this problem seem tractable.
-
-\subsubsection{Connecting Across Datasets}
-The last sub-problem mentioned above is crucial to help make connections across datasets.
-For example, once we have identified that the `Jensen's Inequality' in a published paper is same as the Planetmath proposition with the same name, Planetmath's proof is automatically made available to the reader of the published paper.
-
-However, figuring out if two sources are referring to the same proposition or a different version of the same proposition is often unclear.
-When working with formal systems using different languages, another related problem arises.
-There is no general way to claim equivalence of propositions across different formal systems.
-There are some projects, like Formal Harmony and theory morphisms, that are trying to understand in what sense these propositions are same and how we can translate one to another.
-But these projects are still in early stages and do not provide a general solution.
-
-However, we can utilize curated translations, such as those available from Logipedia, by representing them using arguments.
-The conclusion of such an argument is the proposition in target language and the premise would be the proposition in source language.
-For bi-directional translations two such arguments will be required.
-Such translations do not stand on a very firm foundation and that should be indicated in the validation criteria of the argument.
-A user can choose not to accept such criteria.
-In that case, these translations will not be used in the generating proof graphs.
-Thus we can create proof graphs that have arguments from different languages.
-
-There are some cases where translations occur on firmer grounds, e.g., use of theory morphisms or translations of HOL-light proofs to Metamath.
-The author has not studied these cases in detail but expects that it to be possible to formulate such cross-language translations using the argument graphs.
+Recent progress in machine learning and natural language processing techniques \cite{ginev2019scientific} does make this problem seem tractable.
 
@@
 
-Sophize divides its data into groups called datasets for copyright management and data access rules.
+Sophize divides its data into groups called datasets for copyright and data access management.
 For example, the 'wiki' dataset that extracts knowledge from Wikipedia mathematics glossaries releases its data under `CC-BY-SA' license, whereas the `metamath' dataset is public (`CC0').
 Our signed-in users are free to create their own datasets and we allow them to choose who can read, write or comment in these datasets.
-Another interesting access control is the restriction of use of resources (especially argument-validity criteria) outside an otherwise open-to-read dataset.
+Another interesting access control is the restriction of use of resources (especially argument-validity criteria) from an otherwise open-to-read dataset.
 
@@
 However, it is infeasible to extract information from large repositories in this manner.
-Sophize publishes its data schema and helper libraries (explained in Section \ref{sec:core}) in multiple languages.
+Sophize publishes its data schema (explained in Section \ref{sec:core}) and helper libraries in multiple languages.
 The extracted information is can thus be stored as text (JSON) files in a repository.
@@
 \subsection{Search Interface}
+\label{sec:search}
 Sophize allows its users to run a run a federated search over its resources using an Elasticsearch server.
-We allow users to search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer (See section \ref{sources} for sources) that removes spaces and lower cases the encoding.
-
-For example the, latex formula \verb+$E = mc^2$+ is converted to \textit{Ej9rjmc9v2mMm}. 
-Note that the encoder converts spaces and new-lines into the character `j' or `J' which are removed by our Elasticsearch analyzer at the time of searching the documents.
+We even allow users to \LaTeX to their search queries.
+The server runs search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer that removes spaces and lower cases the encoding.
+(See section \ref{sec:sources} for sources)
 
@@
 
-The Sophize platform includes an innovative mathematics communication interface designed to help
-mathematicians discuss mathematics and collaboratively discover new proofs. The design focuses on
-making the collaboration more productive and enjoyable by building the right set of technical
-tools that aid in effective organization and summarization of existing progress.
-With Sophize Markdown at its core, Sophize's collaboration interface\cite{todo}  (\underline{\href{https://youtu.be/d3gaalJ7UQM}{demo}}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview comment drafts.
+The Sophize platform includes an innovative mathematics communication interface designed to help our users discuss mathematics and collaboratively discover new proofs.
+The design focuses on making the collaboration more productive and enjoyable by building the right set of technical tools that aid in effective organization and summarization of existing progress.
+With Sophize Markdown at its core, Sophize's collaboration interface\cite{EasyChair6207}  (demo: \url{https://youtu.be/d3gaalJ7UQM}) is able to provide key features such as easy linking of existing math content, \LaTeX\space support, and live preview of comment drafts.
 
-\section{Conclusion}
+\section{Conclusion And Future Work}
 \label{sec:conclusion}
-\todo{What criteria are met based on the 2013 report}
 
-\todo{How much math can be represented. Eg. three valued logic}
+We have presented the Sophize platform, a modern open mathematics library focused on providing reliable and detailed knowledge to its users.
+We extract and aggregate logical arguments from a wide variety of sources including published research, encyclopedias, formal theorem provers, and formal/informal programs.
+While there exist other systems that work with disparate data sources, we are aware of no other systems that attempt to logically aggregate knowledge across these data sources.
+Using this organization scheme we can maintain proofs of results from different theoretical foundations and tailor them to a user's knowledge reliability criterion.
 
-\todo{Sophize's limitations. In "Potential Value of a
-Digital Mathematics Library" in 2013 report.
-Sophize offers no way to more easily find analogies or weaker forms of reasoning like “If A is true, then B is true.
-B is true; therefore, A becomes more plausible.” }
+We show how PGMs can be used to compute proofs in real-time and embed them in our knowledge graphs.
+We utilize the proof-graphs using Sophize Markdown to allow users to effortlessly browse proofs and lookup math entities in math literature.
+While there are other ways to represent semantic knowledge, such as content MathML and OpenMath, their scope is somewhat limited to specifying the meaning of the mathematical formula.
+The sTeX system \cite{Kohlhase2008} is perhaps most similar to Sophize Markdown but it needs creation of \LaTeX\space documents and use of \LaTeX ML systems.
+This makes its use in real-time web workflows impractical.
+
+In its current state, Sophize has limited information to share with its users.
+Thus, we would first like to develop automated or semi-automated techniques to extract semantic knowledge from literature and expand the knowledge base that we share with our community.
+Using the proof-graphs and the semantic information collected we would like to make it easier for users to find relevant content with better search results.
+
+\subsection*{Sources}
+\label{sec:sources}
+The source code for several aspects of the Sophize platform (include Sophize Markdown) is  at available at \url{https://github.com/Sophize}.
+The math encoder and Elasticsearch analyzer mentioned in section \ref{sec:search} are available at \url{https://gist.github.com/abc-sophize}.
 
@@
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
 \bibliographystyle{splncs04}

### 2022-05-30 math_library/sophize_math.tex
CICM'22 2nd submission

@@
 Metamath; and allows its users to run a federated search over them. To make this happen, two
-developments were necessary. First, we came up with the concept of 'proof-generating
+developments were necessary. First, we came up with the concept of `proof-generating
 machines' and developed an open plugin architecture that allows proofs from computer
@@
 In fact, dealing with the vast amounts of information thrown at us seems to be one of the most important problems of our generation.
-While we have access to a wide range of opinions on almost every topic imaginable, it has become increasingly difficult to decide which one to trust.
-It
-seems that we can find "proofs" for anything and everything we would like to believe.
+While we have access to a wide range of opinions on almost every topic imaginable, it has become increasingly difficult to decide which ones to trust.
+It seems that the Internet can find us "proofs" for anything we would like to believe.
 
-Thus the author's primary motivation for this project is to create a library that not just
-lays out all the information about the World but organizes it in a way that helps us make
-better sense of it. A library that helps us access justifications from a variety of
+Thus, the author's primary motivation for this project is to create a library that not just lays out all the information about the World but organizes it in a way that helps us make better sense of it.
+A library that helps us access justifications from a variety of
 viewpoints and allows us to collaboratively and objectively evaluate issues in the
@@
 
-Logical organization of mathematics can lead to many advantages. We list some interesting ones below.
+Apart from organizing knowledge focused on trust and aggregating disparate data sources, logical organization of mathematics can lead to many other advantages. We list some interesting ones below.
 
@@
 Complexity theory is one such field where this need is quite apparent.
-On a more practical note, several information security systems build on the conjectural developed with the assumption $P \neq NP$.
+Such conjectural knowledge knowledge can have practical applications too.
+For example, a lot of our information security systems utilize the knowledge developed with the conjectures $P \neq NP$.
 
@@
 Users can keep exploring the proof till they reach a point where the propositions are already familiar to them.
-A future application of proof graphs would be to generate narrative proofs based on tailored to the reader's current understanding.
+A future application of proof graphs would be to generate narrative proofs tailored to the reader's current understanding.
 This could be achieved in a classroom setting where the current level of mathematical understanding of students is known or assumed.
@@
 \label{sec:pgm}
-A lot of mathematical knowledge is computed. Computation machines (e.g. calculators, algebras) can be seen as performing the following tasks
+A lot of mathematical knowledge is computed. Most computation machines (e.g. calculators, algebras) can be seen as performing the following tasks
 \begin{itemize}
@@
 \end{itemize}
-Thus, their focus is not on finding the proof but only finding the equivalent (simplified) representation of the input formula (Although many computer algebras do show the steps of the computation.).
+Thus, their focus is not on finding the proof but only finding the equivalent simplified representation of the input formula (Although many computer algebras do show the steps of the computation).
 With Sophize, the focus instead is to generate proofs of the input propositions.
@@
 `3 + 5 = 8') or a formula (eg.
-`5+6') and in the latter case the PGM is responsible for finding an appropriate proposition (eg.
+`5 + 6') and in the latter case the PGM is responsible for finding an appropriate proposition (eg.
 `5 + 6 = 11') for the given input.
@@
 \item Special `Arguments' that indicate that the generation of the proof of this argument's conclusion must be delegated to another PGM.
+Seeing such arguments, the Sophize platform requests the remainder of the proof from the indicated PGMs as needed to allow users to browse the proof uninterrupted.
 To paginate large proofs, a PGM may also delegate to itself after generating some (say 100) arguments.
 \end{enumerate}
+
 \subsection{Materializing results}
@@
 Thus we were able to easily re-use concepts and theorems already extracted from other sources (say, Wikipedia and the Oxford dictionary in this case).
-Clicking on the underlined concepts, pops-up a modal dialog with the definition of the term clicked.
+Clicking on the underlined concepts pops-up a modal dialog with the definition of the term clicked.
 
@@
 Sophize divides its data into groups called datasets for copyright and data access management.
-For example, the 'wiki' dataset that extracts knowledge from Wikipedia mathematics glossaries releases its data under `CC-BY-SA' license, whereas the `metamath' dataset is public (`CC0').
+For example, the `wiki' dataset that extracts knowledge from Wikipedia mathematics glossaries releases its data under `CC-BY-SA' license, whereas the `metamath' dataset is public (`CC0').
 Our signed-in users are free to create their own datasets and we allow them to choose who can read, write or comment in these datasets.
@@
 Sophize provides dataset owners the ability to sync knowledge such repositories to the central Sophize database.
+The datasets `wiki' and `planetmath' use this scheme for keeping the script-generated data synced with Sophize's central database.
 
@@
 We even allow users to \LaTeX to their search queries.
-The server runs search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer that removes spaces and lower cases the encoding.
+The server runs search a space-insensitive and case-insensitive search over \LaTeX\space formulae by encoding \LaTeX\space formulae as lexemes and an Elasticsearch analyzer processes them appropriately.
 (See section \ref{sec:sources} for sources)
@@
 
-We show how PGMs can be used to compute proofs in real-time and embed them in our knowledge graphs.
-We utilize the proof-graphs using Sophize Markdown to allow users to effortlessly browse proofs and lookup math entities in math literature.
+We show how proof-generating machines can be used to instantaneously compute proofs that embed into previously computed graphs.
+We showcase how Sophize Markdown allow users to effortlessly browse proof-graphs and lookup entities in math literature.
 While there are other ways to represent semantic knowledge, such as content MathML and OpenMath, their scope is somewhat limited to specifying the meaning of the mathematical formula.

### 2022-08-08 math_library/sophize_math.tex
Submission (with sources) to CICM

@@
 
-Another use case would be to understand the consequences of important conjectures like the Reimann hypothesis by creating two belief sets - one where the conjecture is true and one where it is false.
+Another use case would be to understand the consequences of important conjectures like the Riemann hypothesis by creating two belief sets - one where the conjecture is true and one where it is false.
 The proof graphs would systematically store such conjectural knowledge which often gets lost especially when results from multiple conjectures are involved.
